---
title: "Variable Creation 2009-2014"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, cache.lazy = FALSE)
```

# Packages

```{r}
library(data.table)
library(tidyverse)
library(ggthemr)
library(here)
library(vroom)
library(janitor)
library(readxl)
library(ggalluvial)
library(tidylog)
library(arrow)
library(tidylog)
```

# Useful functions

```{r}
source(here("src","code_lib","useful_functions.R"))
```

# Params

```{r}
# figures
fig_height = 6
fig_width = (16/9)*fig_height
ggthemr("pale")

# no scientific notation
options(scipen=999)

# data folder
data_path <- "../data/"
```

# -----

# Import data

## 2009-2014 cohort

```{r}
# Cohort data containing one line per student and the relevant variables
cohort_09_14 <- fread(here("out/data/cohort_09_14.csv"))
cohort_09_14[, .N, by = student_id] %>% count(N)
ids_cohort_09_14 <- cohort_09_14 |> pull(student_id) |> unique()
```

## Enrollment 2008-2023

```{r}
all_enrol_08_23_clean <- open_dataset(here("out/data/all_enrol_parquet/")) |> 
  filter(year_sise %in% 2008:2023)

# replace all empty by missing values
all_enrol_08_23_clean <- all_enrol_08_23_clean %>%
  mutate(across(where(is.character), ~ifelse(.=="", NA, .)))
gc()

# some minor cleaning across different underlying data sources
all_enrol_08_23_clean <- all_enrol_08_23_clean |> 
  mutate(diplom = ifelse(source_sise == "bpbac", dipl_det, diplom),
         diplom_lab = ifelse(source_sise == "bpbac", dipl_det_lab, diplom_lab),
         etabli = ifelse(source_sise == "bpbac", etab, etabli),
         compos = ifelse(source_sise == "bpbac", etab, compos))
```

## Graduation 2009-2023

```{r}
all_result_09_23_clean <- open_dataset(here("out/data/all_result_parquet/")) |> 
  filter(year %in% 2009:2023)
# replace all empty by missing values
all_result_09_23_clean <- all_result_09_23_clean %>%
  mutate(across(where(is.character), ~ifelse(.=="", NA, .)))
gc()
```

## Bac 2006-2020

```{r}
bac_06_20 <- open_dataset(paste0(data_path, "modified_data/anonym/ocean/parquet/"))

# keep only most recent bac grade for each student
bac_06_20_unique <- bac_06_20 |> 
  filter(student_id != "" & !is.na(moy1)) |> 
  select(student_id, year_bac, moy1) |> 
  collect()
setDT(bac_06_20_unique)

# how many observations per student?
bac_06_20_unique[, .N, by = student_id] |> count(N)

bac_06_20_unique[, most_recent_year := max(year_bac), by = student_id]
bac_06_20_unique <- bac_06_20_unique[year_bac == most_recent_year]
bac_06_20_unique[, .N, by = student_id] |> count(N)

# for remaining few duplicates keep highest grade
bac_06_20_unique[, n_obs := .N, by = student_id]
bac_06_20_unique[n_obs > 1, highest_grade := max(moy1, na.rm = T), by = student_id]
bac_06_20_unique <- bind_rows(bac_06_20_unique[n_obs == 1],
                              bac_06_20_unique[n_obs > 1 & moy1 == highest_grade])
bac_06_20_unique[, .N, by = student_id] |> count(N)

bac_06_20_unique$n_obs <- NULL
bac_06_20_unique[, n_obs := .N, by = student_id]
bac_06_20_unique |> count(n_obs)
bac_06_20_unique <- bac_06_20_unique[n_obs == 1]
bac_06_20_unique[, .N, by = student_id] |> count(N)

bac_06_20_unique <- bac_06_20_unique |> select(student_id, year_bac, moy1)
```


# -----

# Echelon crit

```{r}
years <- 2009:2016
echelon_crit <- data.frame()
for (i in years) {
  print(i)
  echelon_crit <- bind_rows(echelon_crit, read_excel(paste0(data_path, "original_data/other/parent_inc_pt_tot_echelon.xlsx"), sheet = paste0(i)) %>%
  clean_names() %>%
  pivot_longer(cols = -points_de_charge,
               names_to = "echelon",
               names_prefix = "echelon_",
               values_to = "parent_inc") %>%
  mutate(parent_inc = str_replace_all(parent_inc, "\\p{WHITE_SPACE}", ""),
         parent_inc = as.numeric(parent_inc),
         year_aglae = i))
}
echelon_crit <- echelon_crit %>%
  as_tibble() %>% 
  mutate(echelon = ifelse(echelon == "0_bis", "0bis", echelon)) %>% 
  group_by(year_aglae, points_de_charge) %>% 
  arrange(year_aglae, points_de_charge) %>% 
  mutate(parent_inc_min = lead(parent_inc)) %>% 
  rename(parent_inc_max = parent_inc) %>% 
  mutate(parent_inc_min = ifelse(is.na(parent_inc_min), -Inf, parent_inc_min)) %>%
  rename(echelon_theory = echelon,
         pt_tot_new = points_de_charge)
# fwrite(echelon_crit, here("out/data/echelon_crit_09_16.csv"))
```

# -----

# Enrollment data preliminary cleaning

## Cohort sample + principal enrollment

```{r}
# keep only students in cohort i'm analysing
ids_students <- cohort_09_14 |> pull(student_id) |> unique()
all_enrol_cohort <- all_enrol_08_23_clean |> 
  filter(student_id %in% ids_students) |> 
  collect()
setDT(all_enrol_cohort)
gc()

# obtain bac year
all_enrol_cohort <- all_enrol_cohort |> 
  left_join(cohort_09_14 |> select(student_id, year_bac))

# keep only principal enrollment
all_enrol_cohort <- all_enrol_cohort |> 
  filter(inspr == "O" | is.na(inspr))
```

## Enrollment year (degetu)

```{r}
# obtain year of study for bpbac
# all the missing degetu come from bpbac
all_enrol_cohort |> count(degetu)
all_enrol_cohort |> 
  filter(is.na(degetu)) |> count(source_sise)

# replace missing degetu by its equivalent in bpbac ("niveau")
all_enrol_cohort <- all_enrol_cohort |> 
  mutate(degetu_new = ifelse(source_sise == "bpbac", niveau, degetu),
         degetu_new = as.numeric(degetu_new))
all_enrol_cohort |> count(degetu_new, sort = T) |> count_to_pct()

# # replace to missing non-post-secondary enrollments
# all_enrol_cohort |>
#   filter(source_sise == "bpbac" & substring(typ_dipl, 1, 1) < 3) |> 
#   count(typ_dipl_lab)
# all_enrol_cohort <- all_enrol_cohort |> 
#   mutate(degetu_new = ifelse(source_sise == "bpbac" & substring(typ_dipl, 1, 1) < 3, NA, degetu_new))
# all_enrol_08_23_clean |> 
#   count(source_sise, degetu_new) |> arrange(degetu_new)

# recode some niveau variables
all_enrol_cohort |> filter(source_sise == "bpbac")  %>%
  count(typ_dipl_det, typ_dipl_det_lab, degetu_new)

all_enrol_cohort <- all_enrol_cohort |> 
  mutate(degetu_new = case_when(typ_dipl_det == "3242" ~ 0, # CLASSE DE MISE A NIVEAU POUR BTS
                                typ_dipl_det == "3281" ~ 4, # DIP.SUPERIEUR ARTS APPLIQUES :1ERE ANNEE
                                typ_dipl_det == "3282" ~ 5, # DIP.SUPERIEUR ARTS APPLIQUES :2EME ANNEE
                                typ_dipl == "329" ~ 3, # DIPLOME NATIONAL DE TECHNO SPECIALISE
                                typ_dipl_det == "4331"~ 3, # FORMATION COMPLEMENTAIRE POST BTS
                                typ_dipl_det == "32B1" ~ 4, # DIP SUP COMPTA ET GESTION 1E AN.- DESCF
                                typ_dipl_det == "32B2" ~ 5, # DIP SUP COMPTA ET GESTION 2E ANNEE
                                TRUE ~ degetu_new))

all_enrol_cohort %>% count(degetu_new)

all_enrol_cohort |>
  filter(is.na(degetu_new)) %>% count(typ_dipl_lab)

all_enrol_cohort %>%
  filter(degetu_new > 6) %>% count(typ_dipl_lab, diplom_lab, sort = T)

# replace > 6 by 6
all_enrol_cohort <- all_enrol_cohort |> 
  mutate(degetu_new = ifelse(degetu_new > 6, 6, degetu_new))

# obtain campus name for manual checks just in case
# missing for 10% of observations
uai_all <- fread("~/projects/data/modified_data/other/uai_all.csv") |> 
  clean_names()
etab_sup <- fread("~/projects/data/original_data/other/fr-esr-principaux-etablissements-enseignement-superieur.csv") |> 
  clean_names()
uai_all <- bind_rows(uai_all |> 
                       select(compos = etabli,
                              compos_lab = etabli_lab),
                     etab_sup |> 
                       select(compos = uai_identifiant,
                              compos_lab = libelle))
setDT(uai_all)
uai_all[, id := 1:.N, by = compos]
uai_all <- uai_all[id == 1]
uai_all[, .N, by = compos] |> count(N)

all_enrol_cohort <- all_enrol_cohort |> 
  left_join(uai_all |> select(compos, compos_lab))
all_enrol_cohort |> 
  count(is.na(compos_lab)) |> count_to_pct()
all_enrol_cohort |> 
  filter(is.na(compos_lab)) |> count(source_sise)
all_enrol_cohort |> 
  filter(is.na(compos_lab)) |> count(etabli_lab, etabli, compos)
```

### Alluvial plot for verification of variable consistency

```{r, eval=FALSE}

# alluvial graph to check consistency of degetu_new
# very few unexpected jumps from year to year reassuringly ----
all_enrol_08_23_clean_agg <- all_enrol_cohort %>%
  select(student_id, year_sise, degetu_new) %>%
  arrange(student_id) %>%
  head(n = 100000) %>%
  group_by(year_sise, student_id) %>%
  collect() |>
  slice_max(order_by = degetu_new)
setDT(all_enrol_08_23_clean_agg)
all_enrol_08_23_clean_agg[, .N, by = list(year_sise, student_id)] %>% count(N)
# pick random enrolment for students with multiple max degetu
all_enrol_08_23_clean_agg[, id := 1:.N, by = list(year_sise, student_id)]
all_enrol_08_23_clean_agg <- all_enrol_08_23_clean_agg[id == 1]
all_enrol_08_23_clean_agg <- all_enrol_08_23_clean_agg %>%
  group_by(student_id) %>%
  arrange(year_sise) %>%
  mutate(enrol_num = 1:n()) %>%
  ungroup()

all_enrol_08_23_clean_agg <- all_enrol_08_23_clean_agg %>%
  pivot_wider(id_cols = student_id,
              names_from = enrol_num,
              values_from = degetu_new) %>%
  mutate(across(matches("[[:digit:]]"), ~ ., .names = "year_enrol_{.col}")) %>%
  select(student_id, contains("year_enrol"))
grouping_cols = lapply(all_enrol_08_23_clean_agg %>% select(contains("year_enrol")) %>% names, as.symbol)
all_enrol_08_23_clean_agg <- all_enrol_08_23_clean_agg %>%
  group_by(.dots = grouping_cols) %>%
  summarise(freq = n()) %>%
  ungroup() %>%
  mutate(id = 1:n()) %>%
  pivot_longer(cols = contains("year_enrol"),
               names_to = "year_enrol",
               values_to = "degetu_new") %>%
  mutate(year_enrol = str_remove(year_enrol, "year_enrol_"))

all_enrol_08_23_clean_agg %>%
  mutate(degetu_new = fct_explicit_na(as.character(degetu_new), "Not in data"),
         degetu_new= factor(degetu_new, levels = c(as.character(1:13), "Not in data"))) %>%
  ggplot(aes(x = factor(year_enrol, levels = as.character(1:13)), y = freq, fill = degetu_new, stratum = degetu_new, alluvium = id, label = degetu_new)) +
  geom_flow() +
  geom_stratum(alpha = .5) +
  geom_text(stat = "stratum", size = 3) +
  scale_fill_viridis_d() +
  # scale_y_continuous(expand = c(0,0), breaks = seq(0, 20000, 2000), lim = c(0, 20000)) +
  scale_x_discrete(expand = c(.01, .01)) +
  theme(panel.grid.major.x = element_blank()) +
  labs(x = "Enrollment #",
       y = "Frequency",
       fill = "Year of study")

rm(all_enrol_08_23_clean_agg, grouping_cols)
# ----
```

## Degree duration (niveau_f)

This variable could be useful to check on-time degree completion / assess persistence conditional on initial degree length

```{r}
# quickly double check to make sure everything makes sense
all_enrol_cohort |> 
  distinct(typ_dipl, diplom, niveau_f) |>
  count(niveau_f) |> count_to_pct()

## equivalent to bac
all_enrol_cohort |> 
  filter(niveau_f == 0) |> 
  count(typ_dipl_lab, sort = T)

all_enrol_cohort |> 
  filter(niveau_f == 0) |> 
  count(diplom, diplom_lab, sort = T)

## equivalent to bac + 1
all_enrol_cohort |> 
  filter(niveau_f == 1) |> 
  count(typ_dipl, typ_dipl_lab, degetu_new)

## equivalent to bac + 2
all_enrol_cohort |> 
  filter(niveau_f == 2) |> 
  count(typ_dipl, typ_dipl_lab, degetu_new)

## equivalent to bac + 3
all_enrol_cohort |> 
  filter(niveau_f == 3) |> 
  count(typ_dipl, typ_dipl_lab, degetu_new) |> view()

## equivalent to bac + 4
all_enrol_cohort |> 
  filter(niveau_f == 4) |> 
  count(typ_dipl, typ_dipl_lab, degetu_new) |> view()

## equivalent to bac + 5
all_enrol_cohort |> 
  filter(niveau_f == 5) |> 
  count(typ_dipl, typ_dipl_lab, degetu_new) |> view()

## equivalent to bac > 5
all_enrol_cohort |> 
  filter(niveau_f > 5) |> 
  count(typ_dipl, typ_dipl_lab, degetu_new) |> view()

# recode degree duration
all_enrol_cohort <- all_enrol_cohort |> 
  mutate(niveau_f_num = as.numeric(niveau_f))

all_enrol_cohort |> 
  filter(is.na(niveau_f_num)) |> 
  count(niveau_f, typ_dipl, typ_dipl_lab)

all_enrol_cohort <- all_enrol_cohort |> 
  mutate(niveau_f_new = case_when(typ_dipl %in% c("CY", "FH", "FJ", "IB") ~ 6, # 1ERE ANNEE COMMUNE AUX ETUDES DE SANTE, DE DOCTEUR EN PHARMACIE, DE DOCTEUR EN CHIRURGIE DENTAIRE, DE DOCTEUR EN MEDECINE
                                  typ_dipl == "UW" ~ 3, # DIPLOME PARIS-DAUPHINE GRADE LICENCE
                                  typ_dipl == "RA" ~ 5, # DIPLOME VISE NIVEAU BAC+5 GRADE MASTER (some of these are incorrect)
                                  typ_dipl == "FI" ~ 5, # FORMATION D'INGENIEUR CLASSIQUE (some of these are put as 6)
                                  typ_dipl == "YB" ~ 6, # DOCTORAT D'UNIVERSITE (GENERIQUE)
                                  typ_dipl == "311" ~ 2, # CPGE
                                  typ_dipl == "324" ~ 0, # DPECF ET CLASSES DE MISE A NIVEAU
                                  typ_dipl == "325" ~ 1, # DIP.METIERS D'ARTS EN 1 AN
                                  typ_dipl == "326" ~ 2, # DIP.METIERS D'ARTS EN 2 ANS
                                  typ_dipl == "328" ~ 5, # DIP.SUPERIEUR ARTS APPLIQUES
                                  typ_dipl == "329" ~ 3, # DIPLOME NATIONAL DE TECHNO SPECIALISE
                                  typ_dipl == "32A" ~ 3, # DIP DE COMPTA GESTION
                                  typ_dipl == "32B" ~ 5, # DIP SUP COMPTA ET GESTION
                                  typ_dipl == "433" ~ 3, # FORMATION COMPLEMENTAIRE POST BTS
                                  typ_dipl == "521" ~ 3, # PREPA.DIVERSE POST-BAC
                                  TRUE ~ niveau_f_num))

all_enrol_cohort |> 
  count(niveau_f_new, degetu_new)

all_enrol_cohort |> 
  filter(niveau_f_new < degetu_new) |> 
  count(typ_dipl, typ_dipl_lab, degetu_new, niveau_f_new, sort = T)
```

# -----

# Main enrolment

## Preliminary checks

```{r}
# 4.93% of students have multiple enrollments in their Bac year
all_enrol_cohort[year_bac == year_sise, .N, by = list(student_id, year_sise)] |>
  count(N > 1) |> count_to_pct()

# what degree types are delivered in the HEIs in SISE Inscrits?
all_enrol_cohort |>
  filter(source_sise == "inscrits" & year_bac == year_sise) |>
  count(nature, sort = T) |> count_to_pct()

# identify potential engineering schools in the SISE Inscrits data
all_enrol_cohort |>
  filter(source_sise == "inscrits") |>
  mutate(at_least_one_inge = sum(nature == "6", na.rm = T) > 0,
         share_inge = mean(nature == "6", na.rm = T),
         n_students = n(), .by = c(etabli_lab, compos, compos_lab)) |>
  filter(at_least_one_inge == T) |>
  count(etabli_lab, compos, compos_lab, share_inge, sort = T) |> view()

# identify potential business schools in the SISE Inscrits data
all_enrol_cohort |>
  filter(source_sise == "inscrits") |>
  mutate(at_least_one_busi = sum(nature == "7", na.rm = T) > 0,
         share_busi = mean(nature == "7", na.rm = T),
         n_students = n(), .by = c(etabli_lab, compos, compos_lab)) |>
  filter(at_least_one_busi == T) |>
  count(etabli_lab, compos, compos_lab, share_busi, sort = T) |> view()

# Other schools in SISE Inscrits/ENS
all_enrol_cohort |>
  filter(source_sise %in% c("inscrits", "ens") &
           !str_detect(etabli_lab, "UNIV|Universte|Université")) |>
  count(etabli, etabli_lab, compos, compos_lab, sort = T) |> view()

# almost all engeering degrees in SISE INGE
all_enrol_cohort |>
  filter(source_sise == "inge" & year_bac == year_sise) |>
  count(nature, sort = T) |> count_to_pct()

# almost all business degrees in SISE INGE
all_enrol_cohort |>
  filter(source_sise == "mana" & year_bac == year_sise) |>
  count(nature, sort = T) |> count_to_pct()

# SISE ENS: a mix of different types of schools
all_enrol_cohort |>
  filter(source_sise == "ens" & year_bac == year_sise) |>
  count(nature, sort = T) |> count_to_pct()

all_enrol_cohort |> 
  filter(source_sise == "ens") |> count(etabli, etabli_lab, compos, compos_lab) |> view()

# SISE PRIV: Instituts catholiques
all_enrol_cohort |>
  filter(source_sise == "priv" & year_bac == year_sise) |>
  count(nature, sort = T) |> count_to_pct()

all_enrol_cohort |> 
  filter(source_sise == "priv") |> count(etabli, etabli_lab, compos, compos_lab) |> view()
```

## HEI id groups

```{r}
# engineering schools in SISE inscrits/ENS - etabli ----
not_inge_inge_etabli <- c("0101060Y", # Universite Technologie Troyes
                          "0381912X", # Institut Polytechnique Grenoble
                          "0311381H", # INP Toulouse
                          "0900424X", # Universite Technologie Montbeliard
                          "0601223D", # Universite Technologie Compiegne
                          "0912341A", # CentraleSupélec
                          "0753465J", # AgroParisTech
                          "0753493P", # Ecole nationale superieure des Mines de Paris
                          "0932019P", # ESIEE Paris
                          "0410981U", # Ecole nationale superieure de la nature et du paysage (interne a l'INSA Centre Val de Loire)
                          "0753429V", # ESPCI
                          "0541564G", # INP Lorraine
                          "0753375L", # Ecole nationale superieure de Chimie de Paris
                          "0597131F", # INSA Hauts-de-France de Valenciennes
                          "0951623Y", # EISTI
                          "0910725U", # Institut d'optique Supoptique
                          "0750043P", # EIVP
                          "0632033T", # SIGMA Clermont
                          "0772496V", # Ecole nationale des sciences geographiques
                          "0350095N", # Ecle des hautes etudes en sante publique
                          "0690193K", # Institut national enseignement superieur et recherche en alimentation, sante animale, sciences agronomiques et environnement
                          c("0912381U", "0921682D") # ENSAE
                          )
# ----

all_enrol_cohort |>
  filter(source_sise == "inscrits" & etabli %in% not_inge_inge_etabli) |>
  summarise(pct_inge = mean(nature == "6"), .by = c(etabli, etabli_lab)) |>
  arrange(desc(pct_inge))

# engineering schools in SISE inscrits/ENS - compos ----
not_inge_inge_compos <- c("0596610P", # Ecole polytechnique universitaire de l'université Lille
                          "0134014T", # Polytech Marseille
                          "0062019M", # Ecole polytechnique universitaire de l'universite Cote d'Azur
                          c("0451638L", "0281168T"), # Ecole polytechnique universitaire de l'universite d'Orleans
                          "0371610Z", # Ecole polytechnique universitaire de l'universite de Tours
                          "0341143H", # Ecole polytechnique universitaire de Montpellier
                          c("0442409E", "0442410F"), # Ecole polytechnique universitaire de l'université de Nantes
                          "0595338G", # ENSIAME (predecesseur de l'INSA HAuts-de-France)
                          "0540130Y", # École polytechnique universitaire de l'Université de Lorraine - Polytech Nancy
                          "0540128W", # Ecole nationale supérieure des Mines de Nancy
                          "0911986P", # Polytech Paris-Saclay Orsay
                          "0540109A", # Ecole nationale supérieure d'agronomie et des industries alimentaires
                          "0693550J", # École polytechnique universitaire de l'Université Lyon-I
                          "0580766T", # Institut supérieur de l'automobile et des transports
                          "0754400A", # Ecole polytechnique universitaire de Sorbonne Université
                          "0772625K", # Ecole supérieure d'ingénieurs de Paris-Est Marne-la-Vallée
                          "0492226D", # Ecole polytechnique universitaire de l'université d'Angers
                          "0595868H", # Ecole nationale supérieure Mines-Télécom Lille Douai - site de Lille
                          c("0731386K", "0741510P"), # Polytech Annecy-Chambery
                          "0680099N", # Ecole nationale supérieure d'ingénieurs Sud Alsace
                          "0382881A", # Ecole polytechnique universitaire Grenoble INP-UGA
                          "0763096C", # Institut supérieur d'études logistiques
                          "0672380Y", # Télécom Physique Strasbourg
                          "0540121N", # Ecole nationale supérieure d'électricité et de mécanique
                          "0540113E", # École Nationale Supérieure des Industries Chimiques
                          "0570140T", # Ecole nationale d'ingenieurs de Metz
                          "0422026Z", # Télécom Saint-Etienne
                          "0861041P", # École nationale supérieure d'ingénieurs de Poitiers
                          "0631383L", # Ecole Polytechnique universitaire de l'Université Clermont Auvergne
                          "0341143H", # Ecole polytechnique universitaire de Montpellier
                          "0542236M", # Telecom Nancy
                          "0871022N", # Ecole nationale superieure d'ingenieurs de Limoges
                          "0875082B", # ENSIL-ENSCI Limoges
                          "0881586W", # Ecole nationale supérieure des technologies et industries du bois
                          "0540123R", # Ecole nationale supérieure de géologie
                          "0672792W", # Ecole européenne de chimie polymères et matériaux
                          "0831443T", # Ecole d'ingeneieurs de l'universite de Toulou
                          "0221809X", # Ecole nationale supérieure des sciences appliquées et de technologie
                          "0542259M", # École européenne d'ingénieurs en génie des matériaux
                          "0212108C", # École supérieure d'ingénieurs en matériaux et informatique - électronique
                          c("0631383L", "0031105K"), # Ecole Polytechnique universitaire de l'Université Clermont Auvergne
                          "0680097L", # Ecole nationale supérieure de chimie de Mulhouse
                          "0782104N", # Institut des sciences et techniques des Yvelines
                          "0352786N", # Ecole supérieure d'ingénieurs de Rennes
                          "0542307P", # Ecole nationale supérieure en génie des systèmes et de l'innovation
                          "0511933Z", # Ecole Nationale Supérieure d'Ingénieurs de Reims
                          c("0501991T", "0142374E", "0501999B"), # Ecole d'ingenieurs de l'Universite Caen Normandie (ESIX Normandie)
                          "0641846J", # École nationale supérieure en génie des technologies industrielles
                          "0721553X", # Ecole nationale supérieure d'ingénieurs du Mans
                          "0631883E", # Institut d'informatique d'Auvergne-Institut supérieur d'informatique de modélisation et de leurs applications
                          c("0561890A", "0561891B"), # Ecole Nationale Supérieure d'Ingénieurs de Bretagne Sud
                          "0251900E", # Institut supérieur d'ingénieurs de Franche-Comté
                          "0642090Z", # Institut superieur aquitain du batiment et des travaux publics de l'universite de Pau
                          "0672504H", # Ecole supérieure de biotechnologie de Strasbourg
                          "0542391F", # Cycle preparatoire Polytechnique de l'universite de Lorraine
                          "0292136P", # Ecole supérieure d'ingénieurs en agroalimentaire de Bretagne Atlantique - site de Quimper
                          "0891207D", # Institut des Techniques d'Ingénieur de l'Industrie de Bourgogne
                          c("0623921A", "0624429C"), # Ecole d'ingenieurs du Littoral Cote d'Opale de l'universite du Littoral
                          "0942389L", # Ecole publique d'ingenieurs de la sante et du numerique de l'universite Paris XII
                          "0755632P", # Ecole d'ingénieurs Denis Diderot Paris
                          "0763460Y", # Ecole supérieure d'ingénieurs en technologies innovantes
                          "7200737N", # Ecole d'ingenieurs Paoli Tech de l'universite de Corse
                          "0772625K", # Ecole supérieure d'ingénieurs de Paris-Est Marne-la-Vallée
                          "0811358L", # Ecole d'ingénieur informatique et systèmes d'information pour la santé
                          "0081149F", # Ecole d'ingénieurs en sciences industrielles et numérique de l'université de Reims
                          "0595967R", # INSA Hauts-de-France
                          c("0952264V", "0642140D"), # Antenne de Cergy et de Pau de CY Tech
                          "0134317X", # Antenne Ecole Polytechnique Marseille
                          "0512181U", # Ecole d'ingenieurs en sciences industrielles et numerique Reims
                          c("9741394X", "9741567K")) # ESIROI-IDAI - La Reunion
# ----

all_enrol_cohort |>
  filter(source_sise == "inscrits" & compos %in% not_inge_inge_compos) |>
  summarise(pct_inge = mean(nature == "6"), .by = c(compos, compos_lab)) |>
  arrange(desc(pct_inge))

# business schools in SISE inscrits - compos ----
inscrits_busi_compos <- c("0673015N") # Ecole de management de Strasbourg
# ----

all_enrol_cohort |>
  filter(source_sise == "inscrits" & compos %in% inscrits_busi_compos) |>
  summarise(pct_busi = mean(nature == "7"), .by = c(compos, compos_lab)) |>
  arrange(desc(pct_busi))

# IEP HEI etabli and/or compos ----
iep <- c("0753431X", # Sciences Po Paris (etabli et compos)
         "0310133B", # Sciences Po Toulouse (compos)
         "0330192E", # Sciences Po Bordeaux (compos)
         "0690173N", # Sciences Po Lyon (etabli et compos)
         "0595876S", # Sciences Po Lille (etabli et compos)
         "0130221V", # Sciences Po Aix (compos)
         "0380134P", # Sciences Po Grenoble (compos)
         "0670178E", # Sciences Po Strasbourg (compos)
         "0352317D", # Sciences Po Rennes (etabli et compos)
         "0783640H") # Sciences Po Saint-Germain-en-Laye (compos)
# ----

all_enrol_cohort |>
  filter(compos %in% iep) |>
  count(compos_lab)

# ENS ----
ens_etabli <- c("0352440M", # ENS de Rennes
                "0694123G", # ENS de Lyon
                "0753455Y") # ENS Ulm

ens_compos <- c("0352440M", # ENS de Rennes
                "0940607Z", # ENS Cachan
                "0912423P") # ENS Paris-Saclay
# ----

all_enrol_cohort |>
  filter(etabli %in% ens_etabli | compos %in% ens_compos) |>
  count(etabli_lab, compos_lab)

# Other schools ----
other_etabli <- c("0753488J", # INALCO
                  "0851415B", # Institut Catholique de Vendee
                  c("0753742K", "0755700N"), # EHESS
                  c("0310153Y", "0441916U"), # Ecole nationale veterinaire de Nantes
                  "0753486G", # Ecole pratique des hautes etudes
                  "0753494R", # Museum nationale d'histoire naturelle
                  "0753478Y", # Ecole nationale des Chartes
                  "0782019W", # Ecole nationale superieur du paysage Versailles
                  "0380141X", # Ecole d'architecture Grenoble
                  "0772551E", # Ecole d'architecture Marne la Vallee
                  "0782019W", # Ecole nationale superieur du paysage Marseille
                  "0951982N", # Ecole pratique de service social
                  "0753469N", # Conservatoire nationale superieure art dramatique
                  "0061804D", # Ecole regionale d'acteurs de Cannes
                  "0951809A", # ILEPS - Ecole des metiers du sport et de l'enseignement
                  "0593655C", # Ecole superieure d'art Ville de Cambrai
                  "0060836B", # Ecole nationale superieure d'art de la Villa d'Arson
                  "0593654B", # Ecole des Beaux Arts Ville de Vallenciennes
                  "0692459Y", # ENSSIB
                  "0940608A") # Ecole nationale vétérinaire d'Alfort
# ----
```

## Function

I follow the IPP report on Grandes Ecoles.

Order: (1) école d'ingé, (2) école de commerce, (3) IEP/Dauphine, (4) CPGE, (5) DUT, (6) BTS, (7) école privée/autres, (8) medecine, (9) licence/master

```{r}
main_enrol_fct <- function(dt = all_enrol_cohort |> 
                             select(year_sise, year_bac, student_id, etabli, etabli_lab, compos, compos_lab, diplom_lab, degetu_new, typ_dipl, typ_dipl_lab, nature, source_sise)) {
  
  # ONE ENROLLMENT ----
  
  # create variable containing number of enrollment by student
  dt$nb <- NULL
  # 96% of students have only 1 enrollment
  dt[, .N, by = list(student_id, year_sise)] |> count(N > 1) |> count_to_pct()
  dt[, nb := .N, by = list(year_sise, student_id)]
  dt %>% count(nb) %>% count_to_pct()
  dt %>% count(nb > 1) %>% count_to_pct()
  
  # create variable containing student's main enrollment
  dt$ins_princip <- NULL
  dt$ins_princip_lab <- NULL
  
  # for students with only one enrollment, set ins_princip to TRUE
  dt[nb == 1, ins_princip := T]
  print(dt %>% count(ins_princip) %>% count_to_pct())
  dt[ins_princip == T, .N, by = list(year_sise, student_id)] %>% count(N)
  
  # label main enrollment of students with only one enrollment
  dt[nb == 1, ins_princip_lab := case_when(source_sise %in% c("inge", "mana") ~ source_sise,
                                           
                                           etabli %in% not_inge_inge_etabli | compos %in% not_inge_inge_compos ~ "inge",
                                           compos %in% inscrits_busi_compos ~ "mana",
                                           compos %in% iep | etabli_lab == "UNIVERSITE PARIS-DAUPHINE" ~ "iep/dauphine",
                                           typ_dipl == 311 ~ "cpge",
                                           nature == "U" ~ "dut",
                                           typ_dipl %in% 321:323 ~ "bts",
                                           diplom_lab %in% c("PREMIERE ANNEE COMMUNE AUX ETUDES DE SANTE (PACES)", "DE DOCTEUR EN MEDECINE", "DE DOCTEUR EN PHARMACIE") ~ "medecine",
                                           etabli %in% c(ens_etabli, other_etabli) | compos %in% ens_compos | source_sise == "priv" | typ_dipl %in% c("324", "326", "328", "329", "32A", "32B", "433", "521") ~ "other",
                                           TRUE ~ "licence/master")]
  dt[nb == 1] %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
  # ----
  
  # MULTIPLE ENROLLMENTS ----

  ## école d'ingé ----
  # identify every student with at least one enrollment in an engineering school
  dt[nb > 1, ins_inge := (sum(source_sise == "inge" | etabli %in% not_inge_inge_etabli | compos %in% not_inge_inge_compos, na.rm = T) > 0), by = list(year_sise, student_id)]
  dt[ins_inge == T & source_sise != "inge"] %>% count(source_sise, sort = T)
  
  # assign main enrollment and label
  dt[nb > 1 & (source_sise == "inge" | etabli %in% not_inge_inge_etabli | compos %in% not_inge_inge_compos), ins_princip := T]
  dt[nb > 1 & (source_sise == "inge" | etabli %in% not_inge_inge_etabli | compos %in% not_inge_inge_compos), ins_princip_lab := "inge"]
  
  # drop secondary enrollments
  dt <- dt |> 
    filter(!(nb > 1 & ins_inge == T & is.na(ins_princip)))
  
  # how many multiple enrollments left? 3.36%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # some of these are for students with two enrollments in an engineering track
  dt[ins_inge == T, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # keep one at random
  dt[ins_inge == T, id := 1:.N, by = list(year_sise, student_id)]
  dt <- bind_rows(dt[ins_inge == T & id == 1],
                  dt[ins_inge == F | is.na(ins_inge)])
  # how many multiple enrollments left? 3.26%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  
  dt$nb <- NULL
  dt[, nb := .N, by = list(student_id, year_sise)]
  
  # count main enrollment labels
  dt[ins_inge == T] %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
  dt |> count(ins_princip_lab)
  dt |> summarise(n_distinct(year_sise, student_id))
  # ----
  
  ## école de commerce ----
  # identify every student with at least one enrollment in a business school
  dt[nb > 1, ins_mana:= (sum(source_sise == "mana" | compos %in% inscrits_busi_compos, na.rm = T) > 0), by = list(year_sise, student_id)]
  dt[ins_mana == T & source_sise != "mana"] %>% count(source_sise, sort = T)
  
  # assign main enrollment and label
  dt[nb > 1 & (source_sise == "mana" | compos %in% inscrits_busi_compos), ins_princip := T]
  dt[nb > 1 & (source_sise == "mana" | compos %in% inscrits_busi_compos), ins_princip_lab := "mana"]
  
  # drop secondary enrollments
  dt <- dt |> 
    filter(!(nb > 1 & ins_mana == T & is.na(ins_princip)))
  
  # how many multiple enrollments left? 3.03%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # a handful of these are for students with two enrollments in a business track
  dt[ins_mana == T, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # keep one at random
  dt[ins_mana == T, id := 1:.N, by = list(year_sise, student_id)]
  dt <- bind_rows(dt[ins_mana == T & id == 1],
                  dt[ins_mana == F | is.na(ins_mana)])
  # how many multiple enrollments left? 3.02%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  
  dt$nb <- NULL
  dt[, nb := .N, by = list(student_id, year_sise)]
  
  # count main enrollment labels
  dt[ins_mana == T] %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
  dt |> count(ins_princip_lab)
  dt |> summarise(n_distinct(year_sise, student_id))
  # ----
  
  ## IEP/Dauphine ----
  # identify every student with at least one enrollment in an IEP or Dauphine
  dt[nb > 1, ins_iep := (sum(compos %in% iep | etabli_lab == "UNIVERSITE PARIS-DAUPHINE", na.rm = T) > 0), by = list(year_sise, student_id)]
  dt[ins_iep == T] %>% count(source_sise, sort = T)
  
  # assign main enrollment and label
  dt[nb > 1 & (compos %in% iep | etabli_lab == "UNIVERSITE PARIS-DAUPHINE"), ins_princip := T]
  dt[nb > 1 & (compos %in% iep | etabli_lab == "UNIVERSITE PARIS-DAUPHINE"), ins_princip_lab := "iep/dauphine"]
  
  # drop secondary enrollments
  dt <- dt |> 
    filter(!(nb > 1 & ins_iep == T & is.na(ins_princip)))
  
  # how many multiple enrollments left? 2.91%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # a handful of these are for students with two enrollments in a business track
  dt[ins_iep == T, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # keep one at random
  dt[ins_iep == T, id := 1:.N, by = list(year_sise, student_id)]
  dt <- bind_rows(dt[ins_iep == T & id == 1],
                  dt[ins_iep == F | is.na(ins_iep)])
  # how many multiple enrollments left? 2.90%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  
  dt$nb <- NULL
  dt[, nb := .N, by = list(student_id, year_sise)]
  
  # count main enrollment labels
  dt[ins_iep == T] %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
  dt |> count(ins_princip_lab)
  dt |> summarise(n_distinct(year_sise, student_id))
  # ----

  ## CPGE ----
  # identify every student with at least one enrollment in a CPGE
  dt[nb > 1, ins_cpge := (sum(source_sise == "bpbac" & typ_dipl == 311, na.rm = T) > 0), by = list(year_sise, student_id)]
  dt[ins_cpge == T] %>% count(source_sise, sort = T)
  
  # assign main enrollment and label
  dt[nb > 1 & (source_sise == "bpbac" & typ_dipl == 311), ins_princip := T]
  dt[nb > 1 & (source_sise == "bpbac" & typ_dipl == 311), ins_princip_lab := "cpge"]
  
  # drop secondary enrollments
  dt <- dt |> 
    filter(!(nb > 1 & ins_cpge == T & is.na(ins_princip)))
  
  # how many multiple enrollments left? 1.56%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # a handful of these are for students with two enrollments in a business track
  dt[ins_cpge == T, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # keep one at random
  dt[ins_cpge == T, id := 1:.N, by = list(year_sise, student_id)]
  dt <- bind_rows(dt[ins_cpge == T & id == 1],
                  dt[ins_cpge == F | is.na(ins_cpge)])
  # how many multiple enrollments left? 1.56%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  
  dt$nb <- NULL
  dt[, nb := .N, by = list(student_id, year_sise)]
  
  # count main enrollment labels
  dt[ins_cpge == T] %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
  dt |> count(ins_princip_lab)
  dt |> summarise(n_distinct(year_sise, student_id))
  # ----
  
  ## DUT ----
  # identify every student with at least one enrollment in a CPGE
  dt[nb > 1, ins_dut := (sum(nature == "U", na.rm = T) > 0), by = list(year_sise, student_id)]
  dt[ins_dut == T] %>% count(source_sise, sort = T)
  
  # assign main enrollment and label
  dt[nb > 1 & nature == "U", ins_princip := T]
  dt[nb > 1 & nature == "U", ins_princip_lab := "dut"]
  
  # drop secondary enrollments
  dt <- dt |> 
    filter(!(nb > 1 & ins_dut == T & is.na(ins_princip)))
  
  # how many multiple enrollments left? 1.53%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # a handful of these are for students with two enrollments in a business track
  dt[ins_dut == T, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # keep one at random
  dt[ins_dut == T, id := 1:.N, by = list(year_sise, student_id)]
  dt <- bind_rows(dt[ins_dut == T & id == 1],
                  dt[ins_dut == F | is.na(ins_dut)])
  # how many multiple enrollments left? 1.53%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  
  dt$nb <- NULL
  dt[, nb := .N, by = list(student_id, year_sise)]
  
  # count main enrollment labels
  dt[ins_dut == T] %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
  dt |> count(ins_princip_lab)
  dt |> summarise(n_distinct(year_sise, student_id))
  # ----
  
  ## BTS ----
  # identify every student with at least one enrollment in a BTS
  dt[nb > 1, ins_bts := (sum(typ_dipl %in% 321:323, na.rm = T) > 0), by = list(year_sise, student_id)]
  dt[ins_bts == T] %>% count(source_sise, sort = T)
  
  # assign main enrollment and label
  dt[nb > 1 & typ_dipl %in% 321:323, ins_princip := T]
  dt[nb > 1 & typ_dipl %in% 321:323, ins_princip_lab := "bts"]
  
  # drop secondary enrollments
  dt <- dt |> 
    filter(!(nb > 1 & ins_bts == T & is.na(ins_princip)))
  
  # how many multiple enrollments left? 1.46%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # a handful of these are for students with two enrollments in a business track
  dt[ins_bts == T, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # keep one at random
  dt[ins_bts == T, id := 1:.N, by = list(year_sise, student_id)]
  dt <- bind_rows(dt[ins_bts == T & id == 1],
                  dt[ins_bts == F | is.na(ins_bts)])
  # how many multiple enrollments left? 1.45%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  
  dt$nb <- NULL
  dt[, nb := .N, by = list(student_id, year_sise)]
  
  # count main enrollment labels
  dt[ins_bts == T] %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
  dt |> count(ins_princip_lab)
  dt |> summarise(n_distinct(year_sise, student_id))
  # ----
  
  ## Other schools (private, ENS, specialised schools) ----
  # identify every student with at least one enrollment in an "other" school
  dt[nb > 1, ins_other := (sum(etabli %in% c(ens_etabli, other_etabli) | compos %in% ens_compos | source_sise == "priv" | typ_dipl %in% c("324", "326", "328", "329", "32A", "32B", "433", "521"), na.rm = T) > 0), by = list(year_sise, student_id)]
  dt[ins_other == T] %>% count(source_sise, sort = T)
  
  # assign main enrollment and label
  dt[nb > 1 & (etabli %in% c(ens_etabli, other_etabli) | compos %in% ens_compos | source_sise == "priv" | typ_dipl %in% c("324", "326", "328", "329", "32A", "32B", "433", "521")), ins_princip := T]
  dt[nb > 1 & (etabli %in% c(ens_etabli, other_etabli) | compos %in% ens_compos | source_sise == "priv" | typ_dipl %in% c("324", "326", "328", "329", "32A", "32B", "433", "521")), ins_princip_lab := "other"]
  
  # drop secondary enrollments
  dt <- dt |> 
    filter(!(nb > 1 & ins_other == T & is.na(ins_princip)))
  
  # how many multiple enrollments left? 0.55%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # a handful of these are for students with two enrollments in a business track
  dt[ins_other == T, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # keep one at random
  dt[ins_other == T, id := 1:.N, by = list(year_sise, student_id)]
  dt <- bind_rows(dt[ins_other == T & id == 1],
                  dt[ins_other == F | is.na(ins_other)])
  # how many multiple enrollments left? 0.55%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  
  dt$nb <- NULL
  dt[, nb := .N, by = list(student_id, year_sise)]
  
  # count main enrollment labels
  dt[ins_other == T] %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
  dt |> count(ins_princip_lab)
  dt |> summarise(n_distinct(year_sise, student_id))
  # ----
  
  ## Medical degree ----
  # identify every student with at least one enrollment in a medical degree
  dt[nb > 1, ins_medecine := (sum(diplom_lab %in% c("PREMIERE ANNEE COMMUNE AUX ETUDES DE SANTE (PACES)", "DE DOCTEUR EN MEDECINE", "DE DOCTEUR EN PHARMACIE"), na.rm = T) > 0), by = list(year_sise, student_id)]
  dt[ins_medecine == T] %>% count(source_sise, sort = T)
  
  # assign main enrollment and label
  dt[nb > 1 & (diplom_lab %in% c("PREMIERE ANNEE COMMUNE AUX ETUDES DE SANTE (PACES)", "DE DOCTEUR EN MEDECINE", "DE DOCTEUR EN PHARMACIE")), ins_princip := T]
  dt[nb > 1 & (diplom_lab %in% c("PREMIERE ANNEE COMMUNE AUX ETUDES DE SANTE (PACES)", "DE DOCTEUR EN MEDECINE", "DE DOCTEUR EN PHARMACIE")), ins_princip_lab := "medecine"]
  
  # drop secondary enrollments
  dt <- dt |> 
    filter(!(nb > 1 & ins_medecine == T & is.na(ins_princip)))
  
  # how many multiple enrollments left? 0.57%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # a handful of these are for students with two enrollments in a business track
  dt[ins_medecine == T, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  # keep one at random
  dt[ins_medecine == T, id := 1:.N, by = list(year_sise, student_id)]
  dt <- bind_rows(dt[ins_medecine == T & id == 1],
                  dt[ins_medecine == F | is.na(ins_medecine)])
  # how many multiple enrollments left? 0.57%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  
  dt$nb <- NULL
  dt[, nb := .N, by = list(student_id, year_sise)]
  
  # count main enrollment labels
  dt[ins_medecine == T] %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
  dt |> count(ins_princip_lab)
  dt |> summarise(n_distinct(year_sise, student_id))
  # ----
  
  ## Licence/master ----
  # randomly pick one of the enrollments
  dt$id <- NULL
  dt[nb > 1 & is.na(ins_princip), id := 1:.N, by = list(year_sise, student_id)]
  dt %>% count(id)
  
  # assign main enrollment and label
  dt[id == 1, ins_princip := T]
  dt[id == 1, ins_princip_lab := "licence/master"]
  
  # drop secondary enrollments
  dt <- dt |> 
    filter(!(nb > 1 & id > 1 & is.na(ins_princip)))
  
  # how many multiple enrollments left? 0%
  dt[, .N, by = list(year_sise, student_id)] |> count(N > 1) |> count_to_pct()
  
  # count main enrollment labels
  dt %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
  dt |> summarise(n_distinct(year_sise, student_id))
  # ----
  
  # ----
  
  # how many rows per student?
  # how many multiple enrollments left? 0%
  dt[, .N, by = list(year_sise, student_id)] |> count(N)
  print(dt %>% count(ins_princip_lab, sort = T) %>% count_to_pct())
  
  # return dt_princip
  return(dt)
}
```

## In Bac year

### Keep only enrollment in Bac year and obtain main enrollment

```{r}
if (!file.exists(here("out", "data", "all_enrol_08_23_clean_bacyear_princip.csv"))) {
  all_enrol_cohort_bacyear <- all_enrol_cohort |> 
    filter(year_sise == year_bac)
  gc()
  
  all_enrol_08_23_clean_bacyear_princip <- main_enrol_fct(all_enrol_cohort_bacyear)
  
  fwrite(all_enrol_08_23_clean_bacyear_princip,
         here("out", "data", "all_enrol_08_23_clean_bacyear_princip.csv"))
  
  rm(all_enrol_cohort_bacyear)
  gc()
}
```

### Merge main enrolment variable in Bac year in cohort_09_14

```{r}
all_enrol_08_23_clean_bacyear_princip <- fread(here("out", "data", "all_enrol_08_23_clean_bacyear_princip.csv"))

cohort_09_14 <- cohort_09_14 %>% 
  left_join(all_enrol_08_23_clean_bacyear_princip %>%
              select(student_id,
                     etabli, compos, typ_dipl_lab, diplom, diplom_lab, niveau_f_new,
                     ins_princip, ins_princip_lab, source_sise))

cohort_09_14 %>% count(ins_princip_lab, sort = T) %>% count_to_pct()
```

## In Bac year + 1

### Keep only enrollment in Bac year and obtain main enrollment

```{r}
if (!file.exists(here("out", "data", "all_enrol_08_23_clean_bacyear_plus1_princip.csv"))) {
  all_enrol_08_23_clean_bacyear_plus1 <- all_enrol_cohort |>
    filter(year_sise == year_bac + 1) |> collect() |> setDT()
  gc()
  
  all_enrol_08_23_clean_bacyear_plus1_princip <- main_enrol_fct(all_enrol_08_23_clean_bacyear_plus1)
  
  fwrite(all_enrol_08_23_clean_bacyear_plus1_princip,
         here("out", "data", "all_enrol_08_23_clean_bacyear_plus1_princip.csv"))
  
  rm(all_enrol_08_23_clean_bacyear_plus1)
  gc()
}
```

### Merge main enrolment variable in Bac year in cohort_09_14

```{r}
all_enrol_08_23_clean_bacyear_plus1_princip <- fread(here("out", "data", "all_enrol_08_23_clean_bacyear_plus1_princip.csv"))

cohort_09_14 <- cohort_09_14 %>% 
  left_join(all_enrol_08_23_clean_bacyear_plus1_princip %>%
              select(student_id,
                     etabli_bacyear_plus1 = etabli,
                     compos_bacyear_plus1 = compos,
                     diplom_bacyear_plus1 = diplom,
                     niveau_f_new_bacyear_plus1 = niveau_f_new,
                     ins_princip_bacyear_plus1 = ins_princip,
                     ins_princip_lab_bacyear_plus1 = ins_princip_lab,
                     source_sise_bacyear_plus1 = source_sise))

cohort_09_14 %>% count(ins_princip_lab_bacyear_plus1) %>% count_to_pct()
```

## In Bac year + 2

### Keep only enrollment in Bac year and obtain main enrollment

```{r}
if (!file.exists(here("out", "data", "all_enrol_08_23_clean_bacyear_plus2_princip.csv"))) {
  all_enrol_08_23_clean_bacyear_plus2 <- all_enrol_cohort |>
    filter(year_sise == year_bac + 2) |> collect() |> setDT()
  gc()
  
  all_enrol_08_23_clean_bacyear_plus2_princip <- main_enrol_fct(all_enrol_08_23_clean_bacyear_plus2)
  
  fwrite(all_enrol_08_23_clean_bacyear_plus2_princip, here("out", "data", "all_enrol_08_23_clean_bacyear_plus2_princip.csv"))
  
  rm(all_enrol_08_23_clean_bacyear_plus2)
  gc()
}
```

### Merge main enrolment variable in Bac year in cohort_09_14

```{r}
all_enrol_08_23_clean_bacyear_plus2_princip <- fread(here("out", "data", "all_enrol_08_23_clean_bacyear_plus2_princip.csv"))

cohort_09_14 <- cohort_09_14 %>% 
  left_join(all_enrol_08_23_clean_bacyear_plus2_princip %>%
              select(student_id,
                     etabli_bacyear_plus2 = etabli,
                     compos_bacyear_plus2 = compos,
                     diplom_bacyear_plus2 = diplom,
                     niveau_f_new_bacyear_plus2 = niveau_f_new,
                     ins_princip_bacyear_plus2 = ins_princip,
                     ins_princip_lab_bacyear_plus2 = ins_princip_lab,
                     source_sise_bacyear_plus2 = source_sise))

cohort_09_14 %>% count(ins_princip_lab_bacyear_plus2) %>% count_to_pct()
```


# -----

# Enrolled in Bac year

```{r}
# obtain student IDs who have at least one enrollment in all post-secondary enrollment datasets
ids_enrol_year_bac_all <- all_enrol_cohort %>%
  filter(year_sise == year_bac) %>%
  pull(student_id) %>%
  unique()
ids_enrol_year_bac_all %>% length

# create dummy identifying students enrolled in any post-secondary HEI
cohort_09_14[, enrol_year_bac_all_0914 := (student_id %in% ids_enrol_year_bac_all)]
cohort_09_14 %>% count(enrol_year_bac_all_0914) %>% count_to_pct()
cohort_09_14 %>% count(year_bac, enrol_year_bac_all_0914) %>% count_to_pct()

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(enrol_year_bac_all_0914))
# ----
```

# At least one enrollment at any point in time

```{r}
# obtain student IDs who have at least one enrollment at any point in time
ids_enrol_anytime_all <- all_enrol_cohort %>%
  pull(student_id) %>%
  unique()
ids_enrol_anytime_all %>% length

# create dummy identifying students enrolled at any point in time
cohort_09_14[, enrol_anytime_all_0914 := (student_id %in% ids_enrol_anytime_all)]
cohort_09_14 %>% count(enrol_anytime_all_0914) %>% count_to_pct()
cohort_09_14 %>% count(year_bac, enrol_anytime_all_0914) %>% count_to_pct()

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(enrol_anytime_all_0914))
# ----
```

# -----

# Enrolment in 2nd year 2 years after Bac

```{r}
# obtain student IDs who have at least one enrollment in 2nd year 2 years after Bac
ids_enrol_2_ontime_all <- all_enrol_cohort %>%
  filter(year_sise == year_bac + 1 & degetu_new == 2) %>%
  pull(student_id) %>%
  unique()
ids_enrol_2_ontime_all %>% length

# create dummy identifying students enrolled in 2nd year 2 years after Bac
cohort_09_14[, enrol_2_ontime_all_0914 := (student_id %in% ids_enrol_2_ontime_all)]
cohort_09_14 %>% count(enrol_2_ontime_all_0914) %>% count_to_pct()
cohort_09_14 %>% count(year_bac, enrol_2_ontime_all_0914) %>% count_to_pct()

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(enrol_2_ontime_all_0914))
# ----
```

# Enroled in 2nd year at any point in time

```{r}
# obtain student IDs who have at least one enrollment in 2nd year at any point in time
ids_enrol_2_anytime_all <- all_enrol_cohort %>%
  filter(degetu_new == 2) %>%
  pull(student_id) %>%
  unique()
ids_enrol_2_anytime_all %>% length

# create dummy identifying students enrolled in 2nd year at any point in time
cohort_09_14[, enrol_2_anytime_all_0914 := (student_id %in% ids_enrol_2_anytime_all)]
cohort_09_14 %>% count(enrol_2_anytime_all_0914) %>% count_to_pct()
cohort_09_14 %>% count(year_bac, enrol_2_anytime_all_0914) %>% count_to_pct()

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(enrol_2_anytime_all_0914))
# ----
```

# -----

# Enrolled in 3rd year 3 years after Bac

```{r}
# obtain student IDs who have at least one enrollment in 3rd year
ids_enrol_3_ontime_all <- all_enrol_cohort %>%
  filter(year_sise == year_bac + 2 & degetu_new == 3) %>%
  pull(student_id) %>%
  unique()
ids_enrol_3_ontime_all %>% length

# create dummy identifying students enrolled in 3rd year 3 years after Bac
cohort_09_14[, enrol_3_ontime_all_0914 := (student_id %in% ids_enrol_3_ontime_all)]
cohort_09_14 %>% count(enrol_3_ontime_all_0914) %>% count_to_pct()
cohort_09_14 %>% count(year_bac, enrol_3_ontime_all_0914) %>% count_to_pct()

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(enrol_3_ontime_all_0914, na.rm = T))
# ----
```

# Enrolled in 3rd year at any point in time

```{r}
# obtain student IDs who have at least one enrollment in 3rd year
ids_enrol_3_anytime_all <- all_enrol_cohort %>%
  filter(degetu_new == 3) %>%
  pull(student_id) %>%
  unique()
ids_enrol_3_anytime_all %>% length

# create dummy identifying students enrolled in 3rd year 3 years after Bac
cohort_09_14[, enrol_3_anytime_all_0914 := (student_id %in% ids_enrol_3_anytime_all)]
cohort_09_14 %>% count(enrol_3_anytime_all_0914) %>% count_to_pct()
cohort_09_14 %>% count(year_bac, enrol_3_anytime_all_0914) %>% count_to_pct()

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(enrol_3_anytime_all_0914))
# ----
```

# -----

# Degree "quality" in Bac year, Bac year + 1, and Bac year + 2

Proxy degree quality by median Bac grade of students enrolled in degree at the HEI in same year. The reason why I don't take median Bac grade of students enrolled in degree at the HEI in t-1 is because in 2014 many universities merged together and thus quality is missing for 41% of students from the 2014 Bac cohort. Moreover students in new degrees can't be assigned a quality in that case, and students in STS and CPGE in the 2009 cohort would be missing quality as well because 2008 BPBAC data is missing student identifiers.

```{r}
all_enrol_08_23_clean |> count(is.na(compos)) |> collect()
all_enrol_08_23_clean |> count(is.na(diplom)) |> collect()

# compute degree (compos-diplom) "quality" as median Bac grade of enrolled students in each year
degree_quality <- all_enrol_08_23_clean |>
  filter(!is.na(diplom) & !is.na(compos)) |> 
  left_join(bac_06_20_unique) |> 
  group_by(year_sise, compos, diplom, diplom_lab) |> 
  summarise(quality = median(moy1, na.rm = T),
            n_students = n()) |> 
  ungroup() |> collect()
degree_quality |> head()

# degree quality missing for 23.2% (26.8% before) of degrees, mostly at the beginning of the period so this is probably masters degrees since I only observe bac grade from 2006 onwards
degree_quality |> count(is.na(quality)) |> count_to_pct()
degree_quality |> summarise(mean(is.na(quality)), .by = year_sise) |> 
  arrange(year_sise)

# 22.9% (22.8% before) of degrees have less than 10 students
degree_quality |> count(n_students <= 10) |> count_to_pct()
degree_quality |> filter(n_students <= 10) |> count(diplom_lab, sort = T)

# evolution of degree quality over time
degree_quality |>
  filter(!is.na(quality)) |>
  group_by(year_sise) |>
  reframe(across(quality, list(min, mean, median, max)))
degree_quality |> pull(quality) |> summary()

# merge with cohort_09_14
cohort_09_14 <- cohort_09_14 |> 
  left_join(degree_quality |>
              mutate(year_bac = year_sise) |>
              select(year_bac, compos, diplom, quality, n_students)) |> 
  left_join(degree_quality |>
              mutate(year_bac = year_sise - 1) |>
              select(year_bac, compos_bacyear_plus1 = compos, diplom_bacyear_plus1 = diplom, quality_bacyear_plus1 = quality, n_students_bacyear_plus1 = n_students)) |>
  left_join(degree_quality |>
              mutate(year_bac = year_sise - 2) |>
              select(year_bac, compos_bacyear_plus2 = compos, diplom_bacyear_plus2 = diplom, quality_bacyear_plus2 = quality, n_students_bacyear_plus2 = n_students))

# no missing
cohort_09_14 |>
  filter(enrol_year_bac_all_0914 == T) |> count(is.na(quality)) |> count_to_pct()

# no missing
cohort_09_14 |>
  filter(enrol_2_ontime_all_0914 == T) |> count(is.na(quality_bacyear_plus1)) |> count_to_pct()

# missing 7 degrees, no big deal
cohort_09_14 |>
  filter(enrol_3_ontime_all_0914 == T) |> count(is.na(quality_bacyear_plus2)) |> count_to_pct()
```

# -----

# Total number of years in higher education

```{r}
# compute the number of years enrolled for each student (excluding 2008)
ids_tot_enrol_yrs <- all_enrol_08_23_clean |>
  filter(year_sise != 2008) |> 
  group_by(student_id) |> 
  summarise(tot_enrol_yrs = n_distinct(year_sise)) |> 
  ungroup() |> collect() |> setDT()
ids_tot_enrol_yrs[, .N, by = student_id] %>%  count(N)
cohort_09_14[, .N, by = student_id] %>%  count(N)

# merge with cohort_09_14
cohort_09_14 <- cohort_09_14 %>% 
  left_join(ids_tot_enrol_yrs)

cohort_09_14 %>% count(year_bac, tot_enrol_yrs) %>% count_to_pct()

# replace missing by 0
cohort_09_14 <- cohort_09_14 %>% 
  mutate(tot_enrol_yrs = ifelse(is.na(tot_enrol_yrs), 0, tot_enrol_yrs))

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(tot_enrol_yrs))
```

# Highest year of study attained

```{r}
# compute the number of years enrolled for each student (excluding 2008)
all_enrol_cohort %>% count(degetu_new)  |> collect() |>  count_to_pct()

# 127 missing degetu_new, no big deal

ids_max_enrol_degetu <- all_enrol_cohort |> 
  filter(year_sise != 2008) |> 
  group_by(student_id) |>
  summarise(max_enrol_degetu = max(degetu_new, na.rm = T)) |>
  ungroup() |> 
  collect() |> setDT()

ids_max_enrol_degetu %>% count(max_enrol_degetu) %>% count_to_pct()
# replace -Inf by 0 (1 obs.)
ids_max_enrol_degetu <- ids_max_enrol_degetu %>% 
  mutate(max_enrol_degetu = ifelse(max_enrol_degetu < 0, 0, max_enrol_degetu))
ids_max_enrol_degetu %>% count(max_enrol_degetu) %>% count_to_pct()

# merge with cohort_09_14
cohort_09_14 <- cohort_09_14 %>% 
  left_join(ids_max_enrol_degetu)

cohort_09_14 |> filter(enrol_anytime_all_0914 == T) |> count(max_enrol_degetu)
cohort_09_14 %>% count(year_bac, max_enrol_degetu) %>% count_to_pct()

# replace missing by 0
cohort_09_14 <- cohort_09_14 %>% 
  mutate(max_enrol_degetu = ifelse(is.na(max_enrol_degetu), 0, max_enrol_degetu))
cohort_09_14 %>% count(year_bac, max_enrol_degetu) %>% count_to_pct()

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(max_enrol_degetu))
# ----
```

# -----

# Degree completion anytime after Bac

```{r}
# obtain student IDs who 
ids_grad_all <- all_result_09_23_clean %>%
  filter((source_sise %in% c("result", "dippriv") & resdip == "O") | !(source_sise %in% c("result", "dippriv"))) |>
  filter(!typ_dipr %in% c("ZH", "01")) |> # ZH = CERTIFICATS DE COMPETENCES, 01 = DIPLOME UNIVERSITE GENERIQUE | ZH = competency certificates related to languages or computer skills, they are not proper degrees; same with 01 which relate to diplomes universitaires (DU) which are not nationally recognised degrees
  pull(student_id) %>%
  unique()
ids_grad_all %>% length

# create dummy identifying students enrolled in SISE Inscrits
cohort_09_14$grad_anytime_all <- NULL
cohort_09_14[, grad_anytime_all := (student_id %in% ids_grad_all)]
cohort_09_14 %>% count(grad_anytime_all) %>% count_to_pct()
cohort_09_14 %>% count(year_bac, grad_anytime_all) |> count_to_pct()

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(grad_anytime_all))
# ----
```

# Degree completion within 5, 7 or 9 years

```{r}
for (i in c(5, 7, 9)) {
  # obtain student IDs who 
  ids_grad_all <- all_result_09_23_clean |> 
    left_join(cohort_09_14 |> select(student_id, year_bac)) |> 
    filter(!is.na(year_bac)) |> 
    filter((source_sise %in% c("result", "dippriv") & resdip == "O") | !(source_sise %in% c("result", "dippriv"))) |>
    filter(!typ_dipr %in% c("ZH", "01")) |> # ZH = CERTIFICATS DE COMPETENCES, 01 = DIPLOME UNIVERSITE GENERIQUE | ZH = competency certificates related to languages or computer skills, they are not proper degrees; same with 01 which relate to diplomes universitaires (DU) which are not nationally recognised degrees
    filter(year <= year_bac + i) |> 
    pull(student_id) %>%
    unique()
  ids_grad_all %>% length
  
  # create dummy identifying students enrolled in SISE Inscrits
  grad_var <- paste0("grad_", i, "_all")
  cohort_09_14[[grad_var]] <- NULL
  cohort_09_14[, (grad_var) := (student_id %in% ids_grad_all)]
  cohort_09_14 %>% count(all_of(grad_var)) %>% count_to_pct()
  cohort_09_14 %>% count(year_bac, all_of(grad_var)) |> count_to_pct()
  
  cohort_09_14 %>%
    group_by(year_bac) %>%
    summarise(mean(get(grad_var)))
  # ---- 
}
```


# Type of degree completed

```{r, eval=FALSE}
all_result_cohort <- all_result_09_23_clean |> 
  filter(student_id %in% ids_cohort_09_14) |> 
  filter((source_sise %in% c("result", "dippriv") & resdip == "O") | !(source_sise %in% c("result", "dippriv"))) |> 
  filter(!typ_dipr %in% c("ZH", "01")) |> # see comment in above code chunk 
  collect()
setDT(all_result_cohort)

all_result_cohort[, .N, by = student_id] |> count(N) |> count_to_pct()

all_result_cohort[, .N, by = student_id]

all_result_cohort <- all_result_cohort |> 
  left_join(cohort_09_14 |>
              select(student_id, year_bac, ins_princip_lab, typ_dipl_lab, diplom_lab, niveau_f_new))

all_result_cohort <- all_result_cohort |>
  mutate(years_to_degree = year - (year_bac + niveau_f_new))

all_result_cohort |> 
  count(years_to_degree)

all_result_cohort |> 
  filter(years_to_degree < 0 & !ins_princip_lab %in% c("medecine", "iep/dauphine")) |> 
  count(year_bac, ins_princip_lab, typ_dipl, typ_dipl_lab, diplom_lab, niveau_f_new, year, typ_dipr, typ_dipr_lab, diplomr_lab, resdip, sort = T) |> view()
```

# Years to first degree

```{r}
# obtain student IDs who 
year_to_first_degree <- all_result_09_23_clean |>
  filter((source_sise %in% c("result", "dippriv") & resdip == "O") | !(source_sise %in% c("result", "dippriv"))) |> 
  filter(!typ_dipr %in% c("ZH", "01")) |>
  left_join(cohort_09_14 |> select(student_id, year_bac)) |> 
  filter(!is.na(year_bac)) |> 
  mutate(years_since_bac = year - year_bac) |> 
  distinct(student_id, years_since_bac) |> 
  summarise(min_years_since_bac = min(years_since_bac), .by = student_id)

year_to_first_degree <- year_to_first_degree |> 
  collect()

cohort_09_14$min_years_since_bac <- NULL
cohort_09_14 <- cohort_09_14 |>
  left_join(year_to_first_degree)

# replace negative values and zeros to missing
cohort_09_14 |> count(min_years_since_bac) |>  count_to_pct()
cohort_09_14 <- cohort_09_14 |> 
  mutate(min_years_since_bac = ifelse(min_years_since_bac <= 0, NA, min_years_since_bac))
cohort_09_14 |> count(min_years_since_bac) |>  count_to_pct()

cohort_09_14 |> 
  group_by(ins_princip_lab) |> 
  summarise(mean_time_to_first_degree = mean(min_years_since_bac, na.rm = T),
            n_obs = n(),
            n_degree = sum(!is.na(min_years_since_bac)),
            pct_observed = n_degree/n_obs*100)
# ----
```

# -----

# Enrollment in graduate degree

I define graduate degree as a degree that has a final level of 4 or 5 years

```{r}
# clean initial level for degree variable ----
# missing for bpbac
all_enrol_cohort %>% count(source_sise, niveau_d) |> collect()
all_enrol_cohort |>
  filter(source_sise == "bpbac") %>% count(typ_dipl, typ_dipl_det, typ_dipl_det_lab, niveau_d, degetu_new, niveau_f_new) |>
  collect()

all_enrol_cohort |> count(niveau_d)
all_enrol_cohort |> count(niveau_f_new)

all_enrol_cohort <- all_enrol_cohort |> 
  mutate(niveau_d = as.numeric(niveau_d),
         niveau_d_new = ifelse(source_sise != "bpbac", niveau_d, NA))
all_enrol_cohort |> count(niveau_d_new)

all_enrol_cohort <- all_enrol_cohort |> 
  mutate(niveau_d_new = case_when(source_sise == "bpbac" & typ_dipl == "311" ~ 0, # CPGE
                                  source_sise == "bpbac" & typ_dipl == "321" ~ 0, # BTS 1 an
                                  source_sise == "bpbac" & typ_dipl == "322" ~ 0, # BTS 2 ans
                                  source_sise == "bpbac" & typ_dipl == "323" ~ 0, # BTS 3 ans
                                  source_sise == "bpbac" & typ_dipl == "324" ~ 0, # mise a niveau BTS
                                  source_sise == "bpbac" & typ_dipl == "325" ~ 0, # DIP.METIERS D'ARTS EN 1 AN
                                  source_sise == "bpbac" & typ_dipl == "326" ~ 0, # DIP.METIERS D'ARTS EN 2 ANS
                                  source_sise == "bpbac" & typ_dipl == "328" ~ 3, # DIP.SUPERIEUR ARTS APPLIQUES
                                  source_sise == "bpbac" & typ_dipl == "329" ~ 2, # DIPLOME NATIONAL DE TECHNO SPECIALISE
                                  source_sise == "bpbac" & typ_dipl == "32A" ~ 0, # DIP DE COMPTA GESTION
                                  source_sise == "bpbac" & typ_dipl == "32B" ~ 3, # DIP SUP COMPTA ET GESTION
                                  source_sise == "bpbac" & typ_dipl == "433" ~ 2, # FORMATION COMPLEMENTAIRE POST BTS
                                  source_sise == "bpbac" & typ_dipl == "521" ~ 0, # PREPA.DIVERSE POST-BAC
                                  TRUE ~ niveau_d_new))

all_enrol_cohort |> count(niveau_d_new)
all_enrol_cohort |> count(niveau_f_new)

# all_enrol_08_23_clean |>
#   filter(student_id %in% ids_cohort_09_14 & source_sise == "bpbac") %>% count(typ_dipl, typ_dipl_det, typ_dipl_det_lab, niveau_d_new, degetu_new, niveau_f_new) |>
#   collect() |> view()


# all_enrol_08_23_clean |>
#   filter(student_id %in% ids_cohort_09_14) %>% count(niveau_d_new, niveau_f_new) %>% collect() |> count_to_pct() %>% print(n = 50)
# ----

# obtain student IDs who have at least one enrollment in a masters degree (proxied by degrees of at least 4 years)
ids_master_all <- all_enrol_cohort %>%
  filter(niveau_f_new %in% 4:5) %>%
  # filter(niveau_f_new >= 4) %>% # doing this basically adds students who did medecine and I wouldn't necessarily count them as pursuing a graduate degree
  pull(student_id) %>%
  unique()
ids_master_all %>% length

# create dummy identifying students enrolled in SISE Inscrits
cohort_09_14$master_anytime_all <- NULL
cohort_09_14[, master_anytime_all := (student_id %in% ids_master_all)]
cohort_09_14 %>% count(master_anytime_all) %>% count_to_pct()
cohort_09_14 %>% count(year_bac, master_anytime_all)

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(master_anytime_all))
# ----
```

# Enrollment in selective graduate degree

I define selective graduate degree as a graduate degree in an engineering, business, IEP/Dauphine, private, ENS or other prestigious schools (EHESS, etc.).

```{r}
# obtain student IDs who have at least one enrollment in a masters degree (proxied by taking degrees of at least 4 years in inge, mana and IEP and Dauphine)
ids_master_select_all <- all_enrol_cohort %>%
  filter(niveau_f_new %in% 4:5 & (source_sise %in% c("mana", "inge", "ens", "priv") | compos %in% c(not_inge_inge_compos, inscrits_busi_compos, iep, ens_compos) | etabli %in% c(ens_etabli, other_etabli) | etabli_lab == "UNIVERSITE PARIS-DAUPHINE")) %>%
  # filter(niveau_f_new %in% 4:5 & source_sise %in% c("mana", "inge", "ens", "priv")) %>%
  pull(student_id) %>%
  unique()
ids_master_select_all %>% length

# create dummy identifying students enrolled in SISE Inscrits
cohort_09_14$master_select_anytime_all <- NULL
cohort_09_14[, master_select_anytime_all := (student_id %in% ids_master_select_all)]
cohort_09_14 %>% count(master_select_anytime_all) %>% count_to_pct()
cohort_09_14 %>% count(year_bac, master_select_anytime_all)

cohort_09_14 %>%
  group_by(year_bac) %>%
  summarise(mean(master_select_anytime_all))
# ----
```

# Quality of graduate degree

Define graduate degree enrollment as first graduate degree in which student enrols

```{r}
first_grad_degree <- all_enrol_cohort |> 
  filter(niveau_f_new %in% 4:5) |>
  left_join(all_enrol_cohort |> 
              filter(niveau_f_new %in% 4:5) |>
              group_by(student_id) |> 
              summarise(year_sise_min = min(year_sise, na.rm = T)) |> 
              ungroup()) |> 
  filter(year_sise == year_sise_min)
setDT(first_grad_degree)
first_grad_degree[, .N, by = student_id] |> count(N) |> count_to_pct()

# obtain degree quality
first_grad_degree <- first_grad_degree |> 
  left_join(degree_quality)
setDT(first_grad_degree)
first_grad_degree[, .N, by = student_id] |> count(N) |> count_to_pct()

# no quality missing
first_grad_degree |> count(is.na(quality)) |> count_to_pct()

# a minority of students have multiple masters enrollments
first_grad_degree[, nb_obs := .N, by = student_id]
first_grad_degree |> count(nb_obs > 1)
# for these students pick graduate degree with greatest "quality"
first_grad_degree <- bind_rows(first_grad_degree[nb_obs == 1],
                               first_grad_degree[nb_obs > 1] |> 
                                 group_by(student_id) |> 
                                 slice_max(order_by = quality) |> 
                                 ungroup())
first_grad_degree[, .N, by = student_id] |> count(N)

# a small fraction still has multiple enrollments, mostly enrollments in degrees with missing quality
# pick one at random
first_grad_degree$nb_obs <- NULL
first_grad_degree[, nb_obs := .N, by = student_id]
first_grad_degree |> filter(nb_obs > 1) |> count(is.na(quality))
first_grad_degree[, id := 1:.N, by = student_id]
first_grad_degree <- first_grad_degree[id == 1]
first_grad_degree[, .N, by = student_id] |> count(N)

# merge with cohort_09_14
cohort_09_14 <- cohort_09_14 |> 
  left_join(first_grad_degree |> select(student_id, quality_first_grad_degree = quality))
# missing for 0%
cohort_09_14 |> filter(master_anytime_all == T) |> count(is.na(quality_first_grad_degree)) |> count_to_pct()
```

# -----

# ECTS credits

```{r}
# obtain variable for ECTS credits of years to degree completion
## graduation 2009-2023
cohorts_ids <- cohort_09_14 |> distinct(student_id) |> pull()
all_degree_ects_cohort <- open_dataset(here("out/data/all_result_parquet")) |>
  filter(source_sise %in% c("result", "priv")) |> # only SISE datasets containing ECTS variable
  filter(year %in% 2009:2023 & student_id %in% cohorts_ids) |>
  select(student_id, year, degetu, etabli, etabli_lab, compos, typ_dipr_lab, diplom, diplomr, diplomr_lab, sectdis_lab, discpli_lab, ects, flag_res, source_sise)

# replace all empty by missing values
all_degree_ects_cohort <- all_degree_ects_cohort %>%
  mutate(across(where(is.character), ~ifelse(. =="", NA, .)))

# put in memory
all_degree_ects_cohort <- all_degree_ects_cohort |> 
  collect()

# the ECTS variable measures the cumulative number of ECTS credits obtained by the student
# therefore, keep the variable's highest value
# all_degree_ects_cohort |>
#   summarise(n_obs = n(), .by = c(student_id, year)) |> count(n_obs)
all_degree_ects_cohort |> count(ects, sort = T)

# convert to numeric
all_degree_ects_cohort <- all_degree_ects_cohort |> 
  mutate(ects_num = as.numeric(ects))

all_degree_ects_cohort |> count(ects_num, sort = T)

# group ects value into coherent bind
all_degree_ects_cohort <- all_degree_ects_cohort |> 
  mutate(ects_credits_bin = case_when(ects_num < 60 ~ "< 1 year (< 60)",
                                      ects_num == 60 ~ "1 year (60)",
                                      ects_num > 60 & ects_num < 120 ~ "between 1 and 2 years (60, 120)",
                                      ects_num == 120 ~ "2 years (120)",
                                      ects_num > 120 & ects_num < 180 ~ "between 2 and 3 years (120, 180)",
                                      ects_num == 180 ~ "3 years (180)",
                                      ects_num > 180 & ects_num < 240 ~ "between 3 and 4 years (180, 240)",
                                      ects_num == 240 ~ "4 years (240)",
                                      ects_num > 240 & ects_num < 300 ~ "between 4 and 5 years (240, 300)",
                                      ects_num == 300 ~ "5 years (300)",
                                      ects_num > 300 ~ "more than 5 years (> 300)"))
all_degree_ects_cohort |> count(ects_credits_bin)

# I need to adjust the number of ECTS credits for students who transfer across degrees
# I make the following adjustment: if a student is enrolled in year X, I add the number of ECTS credits necessary to reach that level for students who have less than the required number of ECTS credits
# for example, masters students' ECTS credits are reset in their master's first year (i.e., degetu = 1), I therefore add 180 credits to their total
all_degree_ects_cohort |> filter(degetu == 4) |> count(ects_num, sort = T)
all_degree_ects_cohort |> filter(degetu == 5) |> count(ects_num, sort = T)
all_degree_ects_cohort <- all_degree_ects_cohort |> 
  mutate(ects_num_adjusted = case_when(degetu == 2 & ects_num < 60 ~ 60 + ects_num,
                                       degetu == 3 & ects_num < 120 ~ 120 + ects_num,
                                       degetu == 4 & ects_num < 180 ~ 180 + ects_num,
                                       degetu == 5 & ects_num < 240 ~ 240 + ects_num,
                                       .default = ects_num),
         ects_credits_bin_adjusted = case_when(ects_num_adjusted < 60 ~ "< 1 year (< 60)",
                                               ects_num_adjusted == 60 ~ "1 year (60)",
                                               ects_num_adjusted > 60 & ects_num_adjusted < 120 ~ "between 1 and 2 years (60, 120)",
                                               ects_num_adjusted == 120 ~ "2 years (120)",
                                               ects_num_adjusted > 120 & ects_num_adjusted < 180 ~ "between 2 and 3 years (120, 180)",
                                               ects_num_adjusted == 180 ~ "3 years (180)",
                                               ects_num_adjusted > 180 & ects_num_adjusted < 240 ~ "between 3 and 4 years (180, 240)",
                                               ects_num_adjusted == 240 ~ "4 years (240)",
                                               ects_num_adjusted > 240 & ects_num_adjusted < 300 ~ "between 4 and 5 years (240, 300)",
                                               ects_num_adjusted == 300 ~ "5 years (300)",
                                               ects_num_adjusted > 300 ~ "more than 5 years (> 300)"))

setDT(all_degree_ects_cohort)
all_degree_ects_cohort_max <- all_degree_ects_cohort[, .(max_ects_credits = max(ects_num_adjusted, na.rm = T)), by = student_id]
all_degree_ects_cohort_max |> count(max_ects_credits)

# merge with cohort data
cohort_09_14 <- cohort_09_14 |> 
  left_join(all_degree_ects_cohort_max)

# number of credits obtained at the end of year 1
cohort_09_14 <- cohort_09_14 |>
  left_join(all_degree_ects_cohort |>
              left_join(cohort_09_14 |> select(student_id, year_bac)) |> 
              filter(year == year_bac + 1 & !is.na(ects_num)) |>
              summarise(ects_num = max(ects_num, na.rm = T), .by = student_id) |> 
              rename(ects_num_end_year_1 = ects_num))

# number of credits obtained by the end of year 2
cohort_09_14 <- cohort_09_14 |>
  left_join(all_degree_ects_cohort |>
              left_join(cohort_09_14 |> select(student_id, year_bac)) |> 
              filter(year == year_bac + 2 & !is.na(ects_num)) |> 
              summarise(ects_num = max(ects_num, na.rm = T), .by = student_id) |> 
              rename(ects_num_end_year_2 = ects_num))

# number of credits obtained by the end of year 3
cohort_09_14 <- cohort_09_14 |>
  left_join(all_degree_ects_cohort |>
              left_join(cohort_09_14 |> select(student_id, year_bac)) |> 
              filter(year == year_bac + 3 & !is.na(ects_num)) |> 
              distinct(student_id, ects_num) |>
              slice_max(ects_num, by = student_id) |> 
              rename(ects_num_end_year_3 = ects_num))
```

# -----

# HEI urban area

```{r}
# keep only institutions for cohort in high school graduation year
ids_students <- cohort_09_14 |> pull(student_id) |> unique()
all_enrol_cohort <- all_enrol_08_23_clean |>
  filter(student_id %in% ids_students) |> 
  left_join(cohort_09_14 |> select(student_id, year_bac)) |> 
  filter(year_bac == year_sise) |> 
  collect()
setDT(all_enrol_cohort)
gc()

# missing HEI municipality in 31.5% of case
all_enrol_cohort |> count(is.na(comins)) |> count_to_pct()
# only missing for BPBAC
all_enrol_cohort |>
  summarise(mean(is.na(comins)), .by = source_sise)

# keep only those missing location
missing_comins <- all_enrol_cohort |> 
  filter(is.na(comins)) |>
  count(etabli)

# 2,290 HEIs
missing_comins |> count()

# secondary establishment
etab_second <- fread(paste0(data_path, "original_data/other/fr-en-adresse-et-geolocalisation-etablissements-premier-et-second-degre.csv")) %>% clean_names() |> 
  select(etabli = code_etablissement,
         etabli_lab = appellation_officielle,
         code_postal, code_commune, commune)

# closed secondary establishment
etab_second_fermes <- fread(paste0(data_path, "original_data/other/fr-en-etablissements-fermes.csv")) %>% clean_names() |> 
  select(etabli = numero_uai,
         etabli_lab = appellation_officielle,
         code_postal = code_postal_uai,
         code_commune, commune = libelle_commune)

# higher education institutions
etab_sup <- fread(paste0(data_path, "original_data/other/fr-esr-principaux-etablissements-enseignement-superieur.csv")) %>% clean_names() |> 
  select(etabli = uai_identifiant,
         etabli_lab = libelle,
         code_postal,
         code_commune, commune)

# higher education institutions in onisep data
etab_onisep <- fread(paste0(data_path, "original_data/other/ideo-structures_denseignement_superieur.csv")) %>% clean_names() |> 
  select(etabli = code_uai,
         etabli_lab = nom,
         code_postal = cp,
         code_commune = commune_cog,
         commune)

# bind all together
etab_all <- bind_rows(etab_second,
                      etab_second_fermes,
                      etab_sup,
                      etab_onisep)
setDT(etab_all)
etab_all[, .N, by = etabli] |> count(N)
etab_all[, id := 1:.N, by = etabli]
etab_all <- etab_all[id == 1]

# merged 2,223 out of 2,290 missing -> 67 (2.93%) remaining
missing_comins <- missing_comins |> 
  left_join(etab_all)
missing_comins |> count(is.na(code_commune)) |> count_to_pct()

# merge in municipality code
# missing for 2,253 (0.1%) students,
all_enrol_cohort <- all_enrol_cohort |> 
  left_join(etab_all |> 
              select(etabli, comins_bpbac = code_commune))
all_enrol_cohort <- all_enrol_cohort |> 
  mutate(comins_clean = coalesce(comins, comins_bpbac))
all_enrol_cohort |> count(is.na(comins_clean)) |> count_to_pct()

# manually impute municipality using https://www.education.gouv.fr/acce_public/search.php
# 0352680Y = not found
# 0212190S = not found
# 9711212R = not found
# 9711021H = not found
# 0932383K = not found
# 0671677J = not found
# 0891261M = not found
all_enrol_cohort <- all_enrol_cohort |> 
  mutate(comins_clean = case_match(etabli,
                                   "0922687W" ~ "92140",
                                   "0333040A" ~ "33300", # https://www.location-etudiant.fr/liste-ecoles-Ecole-d-artdesign-de-Bordeaux-LIM-ART-Ynov-campus--14784.html
                                   "0752887F" ~ "75017", # https://en.location-etudiant.fr/liste-ecoles-IDRAC-Business-School-15552.html
                                   "0755203Y" ~ "75010",
                                   "0693172Y" ~ "69009",
                                   "0061977S" ~ "06300", # https://www.lacl.fr/~msassolas/enseignement/XML_Licence/2016-2017-TPsolo2bis/etablissements.xml
                                   "9711102W" ~ "97110",
                                   "0342073U" ~ "34077",
                                   "0693739P" ~ "69006",
                                   "0371441R" ~ "37058",
                                   "0531002B" ~ "53000",
                                   "0594658T" ~ "59044",
                                   "0383349J" ~ "38400",
                                   "0672689J" ~ "67100",
                                   "0490082Y" ~ "49000", # https://www.location-etudiant.fr/liste-ecoles-Institut-des-metiers-du-notariat-14678.html
                                   "0673043U" ~ "67000",
                                   "0731545H" ~ "73420", # https://www.lacl.fr/~msassolas/enseignement/XML_Licence/2016-2017-TPsolo2bis/etablissements.xml
                                   "0672881T" ~ "67000",
                                   "0682049H" ~ "68100",
                                   "0755081R" ~ "75008",
                                   .default = comins_clean))
# missing for 643 (0.03%) students
all_enrol_cohort |> count(is.na(comins_clean)) |> count_to_pct()

# obtain urban area of HEI municipality
commune_appart <- read_excel(paste0(data_path, "original_data/other/table-appartenance-geo-communes-14.xls"), sheet = "COM", skip = 5) %>% clean_names() |> 
  select(codgeo, libgeo, au2010)

commune_appart_arm <- read_excel(paste0(data_path, "original_data/other/table-appartenance-geo-communes-14.xls"), sheet = "ARM", skip = 5) %>% clean_names() |> 
  select(codgeo, libgeo, au2010)

commune_appart <- bind_rows(commune_appart,
                            commune_appart_arm)
setDT(commune_appart)
commune_appart[, .N, by = codgeo] |> count(N)

au2010 <- read_excel(paste0(data_path, "original_data/other/AU2010_au_01-01-2020.xlsx"), skip = 5) %>% clean_names() |> 
  select(au2010, libau2010)
setDT(au2010)
au2010[, .N, by = au2010] %>% count(N)

commune_appart <- commune_appart %>%
  left_join(au2010 %>% select(au2010, au2010_lab = libau2010))

all_enrol_cohort <- all_enrol_cohort |> 
  left_join(commune_appart |> 
              select(comins_clean = codgeo,
                     comins_clean_lab = libgeo,
                     au2010, au2010_lab))

# missing for 9,625 (0.429%) students
all_enrol_cohort |> count(is.na(au2010)) |> count_to_pct()

all_enrol_cohort |> filter(is.na(au2010)) |> count(substr(comins_clean, 1, 2) == "98", sort = T)

# merge back in cohort_09_14
cohort_09_14 <- cohort_09_14 |> 
  left_join(all_enrol_cohort |> 
              select(student_id, compos, comins_clean, au2010, au2010_lab) |> 
              distinct() |> 
              mutate(id = 1:n(), .by = c(student_id, compos)) |> 
              filter(id == 1))

# missing for 9,547 (0.45%) students
cohort_09_14 |>
  filter(enrol_year_bac_all_0914 == T) |>
  count(is.na(au2010)) |> count_to_pct()
```

# High school urban area

```{r}
# missing high school location for 4.24% students
cohort_09_14 <- cohort_09_14 |>
  left_join(etab_all |> 
              select(etabli,
                     hs_cod_commune = code_commune,
                     hs_commune = commune), by = c("cod_eta" = "etabli"))
cohort_09_14 |> count(is.na(hs_cod_commune)) |> count_to_pct()

cohort_09_14 |> filter(is.na(hs_cod_commune)) |> count(cod_eta, sort = T)

cohort_09_14 <- cohort_09_14 |> 
  mutate(hs_commune = case_when(str_detect(hs_commune, "Paris") & substr(hs_cod_commune, 1, 2) == "75" ~ "Paris",
                                str_detect(hs_commune, "Lyon") & substr(hs_cod_commune, 1, 2) == "69" ~ "Paris",
                                str_detect(hs_commune, "Marseille") & substr(hs_cod_commune, 1, 2) == "13" ~ "Marseille",
                                .default = hs_commune))
# obtain high school urban area
cohort_09_14 <- cohort_09_14 |> 
  left_join(commune_appart %>%
              select(hs_cod_commune = codgeo,
                     hs_au2010 = au2010,
                     hs_au2010_lab = au2010_lab))
# missing for about 5% of students
cohort_09_14 |> count(is.na(hs_au2010)) |> count_to_pct()
```

# -----

# Information proxies

```{r}
# number of recipients of aide au mérite per cohort per high school
n_aidemerite_per_hs <- cohort_09_14 %>% 
  group_by(year_bac, cod_eta1) %>% 
  summarise(n_aidemerite = sum(aidemerite_new == T)) %>% 
  ungroup()
n_aidemerite_per_hs %>% count(year_bac, n_aidemerite > 0) %>% count_to_pct()

n_aidemerite_per_hs %>%
  ggplot(aes(x = n_aidemerite)) +
  geom_histogram(binwidth = 1, center = 0, color = "white", closed = "left") +
  facet_wrap(vars(year_bac))

# how many students came from high schools with at least 1 student who in the current year obtained the aide au mérite
# 57%
cohort_09_14 %>% left_join(n_aidemerite_per_hs) %>% count(n_aidemerite > 1) %>% count_to_pct()

# number of eligible students to aide au mérite per cohort per high school
n_eligible_aidemerite_per_hs <- cohort_09_14 %>% 
  group_by(year_bac, cod_eta1) %>% 
  summarise(n_eligible_aidemerite = sum(mention == "Très Bien" & boursier_esr_all == T)) %>% 
  ungroup()
n_eligible_aidemerite_per_hs %>% count(year_bac, n_eligible_aidemerite > 0) %>% count_to_pct()

n_eligible_aidemerite_per_hs %>%
  ggplot(aes(x = n_eligible_aidemerite)) +
  geom_histogram(binwidth = 1, center = 0, color = "white", closed = "left") +
  facet_wrap(vars(year_bac))

# lag cohort year to obtain number of recipients in previous cohort
# due to this lag the 2009 cohort will have missing values. that's fine, doesn't change much most likely.
setDT(n_aidemerite_per_hs)
n_aidemerite_per_hs[, `:=`(year_bac = year_bac + 1,
                           n_aidemerite_prev_year = n_aidemerite)]

# merge with cohort_09_14
cohort_09_14 <- cohort_09_14 %>% 
  left_join(n_aidemerite_per_hs %>%
              select(cod_eta1, n_aidemerite_prev_year, year_bac)) %>% 
  left_join(n_eligible_aidemerite_per_hs %>% 
              select(cod_eta1, n_eligible_aidemerite, year_bac))
cohort_09_14 %>% count(n_aidemerite_prev_year)
cohort_09_14 %>% count(n_eligible_aidemerite)

# how many students from post-2009 cohorts came from high schools with at least 1 student who in the previous year obtained the aide au mérite
# 67.1%
cohort_09_14[year_bac > 2009] %>% count(n_aidemerite_prev_year >= 1) %>% count_to_pct()

# how many students came from high schools where they were not the only student to be eligible to the aide au mérite
# 59.7%
cohort_09_14 %>% count(n_eligible_aidemerite > 1) %>% count_to_pct()
```

# -----

# Donut

```{r}
# Donut dummy ----
upper = 0.051 # this is so that students scoring exactly at 16.05 are excluded in the donut specification since there is some bunching at this value
lower = .3
cohort_09_14[, donut := !(round(moy1,2) >= (16 - lower) & round(moy1,2) < (16 + upper))]
cohort_09_14 %>% count(donut)
cohort_09_14[moy1 >= 15.5 & moy1 <= 16.1] %>% count(moy1, donut)

cohort_09_14[, donut15 := !(round(moy1,2) >= (15 - lower) & round(moy1,2) < (15 + upper))]
cohort_09_14 %>% count(donut15)
cohort_09_14[moy1 >= 14.5 & moy1 <= 15.1] %>% count(moy1, donut15)

cohort_09_14[, donut14 := !(round(moy1,2) >= (14 - lower) & round(moy1,2) < (14 + upper))]
cohort_09_14 %>% count(donut14)
cohort_09_14[moy1 >= 13.5 & moy1 <= 14.1] %>% count(moy1, donut14)

cohort_09_14[, donut12 := !(round(moy1,2) >= (12 - lower) & round(moy1,2) < (12 + upper))]
cohort_09_14 %>% count(donut12)
cohort_09_14[moy1 >= 11.5 & moy1 <= 12.1] %>% count(moy1, donut12)

# donuts that don't work for appendix
# [15.95, 16.05]
cohort_09_14[, donut_a := !(round(moy1,2) >= (16 - .05) & round(moy1,2) < (16 + upper))]
cohort_09_14 %>% count(donut_a)
cohort_09_14[moy1 >= 15.5 & moy1 <= 16.1] %>% count(moy1, donut_a)

# [15.9, 16.05]
cohort_09_14[, donut_b := !(round(moy1,2) >= (16 - .1) & round(moy1,2) < (16 + upper))]
cohort_09_14 %>% count(donut_b)
cohort_09_14[moy1 >= 15.5 & moy1 <= 16.1] %>% count(moy1, donut_b)

# [15.85, 16.05]
cohort_09_14[, donut_c := !(round(moy1,2) >= (16 - .15) & round(moy1,2) < (16 + upper))]
cohort_09_14 %>% count(donut_c)
cohort_09_14[moy1 >= 15.5 & moy1 <= 16.1] %>% count(moy1, donut_c)

# [15.8, 16.05]
cohort_09_14[, donut_d := !(round(moy1,2) >= (16 - .2) & round(moy1,2) < (16 + upper))]
cohort_09_14 %>% count(donut_d)
cohort_09_14[moy1 >= 15.5 & moy1 <= 16.1] %>% count(moy1, donut_d)

# [15.75, 16.05]
cohort_09_14[, donut_e := !(round(moy1,2) >= (16 - .25) & round(moy1,2) < (16 + upper))]
cohort_09_14 %>% count(donut_e)
cohort_09_14[moy1 >= 15.5 & moy1 <= 16.1] %>% count(moy1, donut_e)

# [15.65, 16.05]
cohort_09_14[, donut_f := !(round(moy1,2) >= (16 - .35) & round(moy1,2) < (16 + upper))]
cohort_09_14 %>% count(donut_f)
cohort_09_14[moy1 >= 15.5 & moy1 <= 16.1] %>% count(moy1, donut_f)

# [15.6, 16.05]
cohort_09_14[, donut_g := !(round(moy1,2) >= (16 - .4) & round(moy1,2) < (16 + upper))]
cohort_09_14 %>% count(donut_g)
cohort_09_14[moy1 >= 15.5 & moy1 <= 16.1] %>% count(moy1, donut_g)
# ----
```

# -----

# Export dataset

```{r}
fwrite(cohort_09_14, here("out/data/cohort_09_14.csv"))
```



