---
title: "Descriptive Statistics"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, cache.lazy = FALSE)
```

# Packages

```{r}
library(data.table)
library(tidyverse)
library(arrow)
library(ggthemr)
library(here)
library(janitor)
library(readxl)
library(kableExtra)
library(ggalluvial)
library(scico)
library(fixest)
library(broom)
library(tidylog)
```

# Useful functions

```{r}
source(here("src","code_lib","useful_functions.R"))
```

# Params

```{r}
# figures
fig_height = 6
fig_width = (16/9)*fig_height
ggthemr("pale")

theme_update(text = element_text(size = 14),
             legend.title = element_text(face = "italic", size = 12),
             # legend.text = element_text(size = 10),
             legend.background = element_rect(fill = alpha("white", .75)),
             plot.caption = element_text(size = 8, face = "italic", color = "#7d7d7d"),
             plot.margin = unit(c(6,10,6,6), "pt"))

# no scientific notation
options(scipen=999)

# data folder
data_path <- "../data/"
```

# Import data

```{r}
bac_09_14 <- fread(paste0(data_path, "/modified_data/anonym/ocean/bac_08_14.csv")) |> 
  filter(year_bac %in% 2009:2014)
# Replace all empty by missing values
bac_09_14 <- bac_09_14 %>%
  mutate_if(is.character, ~ifelse(.=="", NA, .))
setDT(bac_09_14)

bac_09_14_clean <- fread(here("out/data/bac_09_14_clean.csv"))
# Replace all empty by missing values
bac_09_14_clean <- bac_09_14_clean %>%
  mutate_if(is.character, ~ifelse(.=="", NA, .))
setDT(bac_09_14_clean)

cohort_09_14 <- fread(here("out/data/cohort_09_14.csv"))
# Replace all empty by missing values
cohort_09_14 <- cohort_09_14 %>%
  mutate_if(is.character, ~ifelse(.=="", NA, .))
setDT(cohort_09_14)

aglae_09_16_clean_unique <- fread(here("out/data/aglae_09_16_clean_unique.csv"))
# Replace all empty by missing values
aglae_09_16_clean_unique <- aglae_09_16_clean_unique %>%
  mutate_if(is.character, ~ifelse(.=="", NA, .))
setDT(aglae_09_16_clean_unique)

all_enrol_08_23_clean <- open_dataset(here("out/data/all_enrol_parquet"))
# replace all empty by missing values
all_enrol_08_23_clean <- all_enrol_08_23_clean |> 
  mutate(across(where(is.character), ~ ifelse(.=="", NA, .)))

all_result_09_23_clean <- open_dataset(here("out/data/all_result_parquet"))
# replace all empty by missing values
all_result_09_23_clean <- all_result_09_23_clean |> 
  mutate(across(where(is.character), ~ ifelse(.=="", NA, .)))

gc()
```

# Number of observations table

```{r}
num_obs_table <- data.table(restriction = c(2009:2014, "2009-2014"))

# Raw number of obs.
num_obs_table[, "Raw number of obs." := c(bac_09_14 %>% count(year_bac) %>% pull(n),
                                          bac_09_14 %>% count() %>% pull(n))]

# Restriction 1: obtained Bac in June session
bac_09_14_sample <- bac_09_14 %>%
  filter(exam1 == 1 & (dec1 %in% c("A","B","C","D") | (dec1 == "P" & dec2 == "D")))
num_obs_table[, "+ Obtained the Bac in June session" := c(bac_09_14_sample %>% count(year_bac) %>% pull(n),
                                                        bac_09_14_sample %>% count() %>% pull(n))]

# Restriction 2: unique and non-missing student identifier
setDT(bac_09_14_sample)
bac_09_14_sample[, n_unique := .N, by = list(year_bac, student_id)]
bac_09_14_sample %>% count(n_unique)
bac_09_14_sample <- bac_09_14_sample[n_unique == 1]
num_obs_table[, "+ Unique and non-missing student identifier" := c(bac_09_14_sample %>% count(year_bac) %>% pull(n),
                                                                 bac_09_14_sample %>% count() %>% pull(n))]

# Restriction 3: obtained Bac only once over the period 2006-2014
bac_06_08 <- open_dataset(paste0(data_path, "modified_data/anonym/ocean/parquet")) |> 
  filter(year_bac %in% 2006:2008) |> collect()
bac_06_08 <- bac_06_08 %>% mutate_if(is.character, ~ifelse(.=="", NA, .))
setDT(bac_06_08)
bac_06_08 <- bac_06_08[exam1 == 1 & (dec1 %in% c("A","B","C","D") | (dec1 == "P" & dec2 == "D")) & !is.na(student_id)]
bac_09_14_sample <- rbindlist(list(bac_09_14_sample, bac_06_08), fill = T)
bac_09_14_sample[, n_times := .N, by = student_id]
bac_09_14_sample %>% count(n_times)
bac_09_14_sample <- bac_09_14_sample[n_times == 1 & year_bac %in% 2009:2014]
num_obs_table[, "+ Obtained the Bac only once over the period" := c(bac_09_14_sample %>% count(year_bac) %>% pull(n),
                                                                    bac_09_14_sample %>% count() %>% pull(n))]

# Restriction 4: Bac grade not missing
bac_09_14_sample <- bac_09_14_sample[!is.na(moy1)]
num_obs_table[, "+ Bac grade not missing" := c(bac_09_14_sample %>% count(year_bac) %>% pull(n),
                                             bac_09_14_sample %>% count() %>% pull(n))]

# Restriction 5: Eligible to a need-based grant
num_obs_table[, "+ Eligible to need-based grants" := c(cohort_09_14[boursier_esr_all == T] %>%
                                                       count(year_bac) %>%
                                                       pull(n),
                                                     cohort_09_14[boursier_esr_all == T] %>%
                                                       count() %>%
                                                       pull(n))]

# format numbers
num_obs_table <- num_obs_table %>% 
  mutate(across(-restriction, ~ formatC(., big.mark = ",")))

# transpose
t(num_obs_table)

# export
fwrite(t(num_obs_table), here("out/tables/num_obs_table.csv"))
```

# Descriptive Stats Tables

4 samples:
(i) Full sample of high school graduates
(i) Full sample of need-based grant eligibles
(ii) Aide au merite eligibles in Bac year
(iii) RD sample ([15, 17])

```{r}
cohort_09_14 <- cohort_09_14 %>% 
  mutate(sample_full = T,
         sample_boursier = (boursier_esr_all == T),
         sample_aide_merite = (moy1 >= 16 & boursier_esr_all == T),
         sample_rd = (sample_boursier & moy1 > 15 & moy1 < 17))

cohort_09_14 %>% count(sample_full) |> count_to_pct()
cohort_09_14 %>% count(sample_boursier)
cohort_09_14 %>% count(sample_aide_merite)
cohort_09_14 %>% count(sample_rd)

sample <- c("sample_full", "sample_boursier", "sample_aide_merite", "sample_rd")
num_digits <- 1

stat_desc_table = 1:length(sample) %>% 
  map_dfr(~ cohort_09_14 %>%
            filter(get(sample[.x]) == T) %>% 
            summarise(sample = sample[.x],
                      "Female (%)" = round(mean(gender == "Female")*100, num_digits),
                      "Age at Bac (mean)" = round(mean(age), num_digits),
                      # mean(natio == 1),
                      "Parents' taxable income (median; euros)" = formatC(median(ress), format = "d", big.mark = ","),
                      "Very high SES (%)" = round(mean(pcs_depp == "Very High SES")*100, num_digits),
                      "High or middle SES (%)" = round(mean(pcs_depp %in% c("High SES", "Middle SES"))*100, num_digits),
                      "Low SES (%)" = round(mean(pcs_depp == "Low SES")*100, num_digits),
                      "Missing SES (%)" = round(mean(pcs_depp == "Missing")*100, num_digits),
                      ">= 16/20 at Bac (%)" = round(mean(moy1 >= 16)*100, num_digits),
                      "Bac grade (mean)" = round(mean(moy1), num_digits),
                      "General high school track (%)" = round(mean(exagt == 1)*100, num_digits),
                      "Technologic high school track (%)" = round(mean(exagt == 2)*100, num_digits),
                      "Professional high school track (%)" = round(mean(exagt == 3)*100, num_digits),
                      "Private high school (%)" = round(mean(origine %in% 2:3)*100, num_digits),
                      "Eligible for merit aid in HS grad. year" = formatC(round(sum(boursier_esr_all == T & moy1 >= 16), 2), format = "d", big.mark = ","),
                      "Eligible for merit aid in HS grad. year + 1" = formatC(round(sum(boursier_esr_all_plus1 == T & moy1 >= 16), 2), format = "d", big.mark = ","),
                      "Eligible for merit aid in HS grad. year + 2" = formatC(round(sum(boursier_esr_all_plus2 == T & moy1 >= 16), 2), format = "d", big.mark = ","),
                      "Echelon 0-0 bis (%)" = round(mean(echelon %in% c("0", "0bis"))*100, num_digits),
                      "Echelon 1 (%)" = round(mean(echelon %in% c("1"))*100, num_digits),
                      "Echelon 2-4 (%)" = round(mean(echelon %in% c("2", "3", "4"))*100, num_digits),
                      "Echelon 5-7 (%)" = round(mean(echelon %in% c("5", "6", "7"))*100, num_digits),
                      "Enrolled in HS grad. year (%)" = round(mean(enrol_year_bac_all_0914 == T)*100, num_digits),
                      "Public university (%)" = round(sum(ins_princip_lab %in% c("licence/master", "medecine"), na.rm = T)/sum(enrol_year_bac_all_0914 == T)*100, num_digits),
                      "Vocational degree (BTS) (%)" = round(sum(ins_princip_lab == "bts", na.rm = T)/sum(enrol_year_bac_all_0914 == T)*100, num_digits),
                      "Technical degree (DUT) (%)" = round(sum(ins_princip_lab == "dut", na.rm = T)/sum(enrol_year_bac_all_0914 == T)*100, num_digits),
                      "Academic preparatory classes (CPGE) (%)" = round(sum(ins_princip_lab == "cpge", na.rm = T)/sum(enrol_year_bac_all_0914 == T)*100, num_digits),
                      "Other institutions (%)" = round(sum(ins_princip_lab %in% c("iep/dauphine", "inge", "mana", "priv", "other"), na.rm = T)/sum(enrol_year_bac_all_0914 == T)*100, num_digits),
                      "Enrolled in 2nd year in HS grad. year + 1 (%)" = round(mean(enrol_2_ontime_all_0914 == T)*100, num_digits),
                      "Enrolled in 3rd year in HS grad. year + 2 (%)" = round(mean(enrol_3_ontime_all_0914 == T)*100, num_digits),
                      "Obtained a degree (2009-2023) (%)" = round(mean(grad_anytime_all == T)*100, num_digits),
                      "Observations" = formatC(n(), format = "d", big.mark = ",")))

fwrite(stat_desc_table, here("out/tables/raw_data/stat_desc_table.csv"))
```

# Figure: Distribution of Bac grades, 2009-2014, need-based grant eligibles

## Panel (a) Grades 8-20

```{r}
graph <- cohort_09_14[boursier_esr_all == T] %>% 
  mutate(moy1 = round(moy1, 2),
         mention_en = case_when(mention == "Pas de mention" ~ "No\nhonors",
                                mention == "Passe second groupe" ~ "Obtained at\nretake session",
                                mention == "Assez Bien" ~ "Honors",
                                mention == "Bien" ~ "High\nhonors",
                                mention == "Très Bien" ~ "Highest\nhonors",
                                TRUE ~ mention),
         mention_en = fct_relevel(mention_en, "Highest\nhonors","High\nhonors", "Honors", "No\nhonors", "Obtained at\nretake session")) |> 
  ggplot(aes(x = moy1, fill = mention_en)) +
  geom_histogram(binwidth = .1, boundary = 10, closed = "left", color = "white", linewidth = 0.1) +
  scale_fill_viridis_d() +
  scale_x_continuous(lim = c(8,20), breaks = seq(0,20,2), expand = c(0,0)) +
  scale_y_continuous(lim = c(0,65000), breaks = seq(0,60000,10000),labels = scales::comma, expand = c(0,0)) +
  labs(x = "Bac grade",
       y = "Frequency",
       fill = NULL) +
  theme(text = element_text(size = 12),
        legend.position = c(0.01,1),
        legend.justification = c(0,1),
        legend.text = element_text(size = 9),
        plot.margin = unit(c(6,10,6,6), "pt")) +
  guides(fill = guide_legend(nrow = 1, reverse = T))
graph

ggsave(here("out","figures","distrib_bac_0914_moy1_clean.pdf"),
       height = fig_height*0.495, width = fig_width*0.495)
```

## Panel (b) Grades 15-17 with 16.05 included in [16, 16.05)

```{r}
cohort_09_14[boursier_esr_all == T] %>%
  mutate(moy1 = ifelse(round(moy1, 2) == 16.05, 16.049999, moy1)) |> 
  filter(moy1 >= 15 & moy1 <= 17) %>% 
  ggplot(aes(x = moy1)) +
  geom_histogram(binwidth = .05, boundary = 10, closed = "left", color = "white", size = 0.1) +
  scale_fill_viridis_d() +
  scale_x_continuous(lim = c(15,17), breaks = seq(0,20,.2), minor_breaks = seq(0,20,.1), expand = c(0,0)) +
  scale_y_continuous(lim = c(0,11000), breaks = seq(0,11000,2000),labels = scales::comma, expand = c(0,0)) +
  labs(x = "Bac grade",
       y = "Frequency") +
  theme(panel.grid.minor.x = element_line(color = alpha("#eaeaea", .5), linetype = 2))

ggsave(here("out","figures","distrib_bac_0914_moy1_clean_1517_slight_adjust_inarticle.pdf"),
       height = fig_height*0.495, width = fig_width*0.495)
```

# Appendix Figure: Distribution of Bac grades, 2009-2014, all

## Panel (a) Grades 8-20

```{r}
cohort_09_14 %>% 
  mutate(mention = case_when(mention == "Pas de mention" ~ "No\ndistinction",
                             mention == "Passe second groupe" ~ "Obtained at\nsecond round",
                             mention == "Assez Bien" ~ "Assez\nBien",
                             mention == "Très Bien" ~ "Très\nBien",
                             TRUE ~ mention),
         mention = fct_relevel(mention, "Très\nBien","Bien","Assez\nBien","No\ndistinction", "Obtained at\nsecond round")) %>% 
  ggplot(aes(x = moy1, fill = mention)) +
  geom_histogram(binwidth = .1, boundary = 10, closed = "left", color = "white", size = 0.1) +
  scale_fill_viridis_d() +
  scale_x_continuous(lim = c(8,20), breaks = seq(0,20,2), expand = c(0,0)) +
  scale_y_continuous(lim = c(0,180000), breaks = seq(0,200000,20000),labels = scales::comma, expand = c(0,0)) +
  labs(x = "Bac grade",
       y = "Frequency",
       fill = "Distinction:") +
  theme(legend.position = c(0.01,1),
        legend.justification = c(0,1),
        plot.margin = unit(c(6,10,6,6), "pt")) +
  guides(fill = guide_legend(nrow = 1, reverse = T))
ggsave(here("out","figures","distrib_bac_0914_moy1_all_clean.pdf"),
       height = fig_height*0.495, width = fig_width*0.495)
```

## Panel (b) Grades 15-17 with 16.05 included in [16, 16.05)

```{r}
cohort_09_14 %>%
  mutate(moy1 = ifelse(round(moy1, 2) == 16.05, 16.049999, moy1)) |> 
  filter(moy1 >= 15 & moy1 <= 17) %>% 
  ggplot(aes(x = moy1)) +
  geom_histogram(binwidth = .05, boundary = 10, closed = "left", color = "white", size = 0.1) +
  scale_fill_viridis_d() +
  scale_x_continuous(lim = c(15,17), breaks = seq(0,20,.2), minor_breaks = seq(0,20,.1), expand = c(0,0)) +
  scale_y_continuous(lim = c(0,32000), breaks = seq(0,32000,5000),labels = scales::comma, expand = c(0,0)) +
  labs(x = "Bac grade",
       y = "Frequency") +
  theme(panel.grid.minor.x = element_line(color = alpha("#eaeaea", .5), linetype = 2))

ggsave(here("out","figures","distrib_bac_0914_moy1_clean_all_1517_slight_adjust.pdf"),
       height = fig_height, width = fig_width)
ggsave(here("out","figures","distrib_bac_0914_moy1_clean_all_1517_slight_adjust_inarticle.pdf"),
       height = fig_height*0.495, width = fig_width*0.495)
```

# Alluvial chart of need-based grant status

```{r}
ids_enrolled_byyear <- all_enrol_08_23_clean %>% distinct(year_sise, student_id)
ids_enrolled_byyear <- ids_enrolled_byyear %>% 
  mutate(enrolled = T) |> 
  collect()

nbg_status_overtime <- aglae_09_16_clean_unique[student_id %in% cohort_09_14[boursier_esr_all == T]$student_id] %>%
  select(student_id, year_aglae, year_bac, dec_aid1_new, echelon) %>% 
  left_join(ids_enrolled_byyear, by = c("student_id", "year_aglae" = "year_sise")) %>% 
  mutate(enrolled = ifelse(is.na(enrolled), F, enrolled),
         year_postbac = (year_aglae - year_bac + 1),
         echelon = case_when(!is.na(echelon) ~ echelon,
                             is.na(echelon) & !is.na(dec_aid1_new) & enrolled == T ~ "enrolled + FA app.\nbut not eligible",
                             is.na(echelon) & !is.na(dec_aid1_new) & enrolled == F ~ "not enrolled + FA app.\nbut not eligible",
                             is.na(echelon) & is.na(dec_aid1_new) & enrolled == T ~ "enrolled + no FA app.",
                             is.na(echelon) & is.na(dec_aid1_new) & enrolled == F ~ "not enrolled + no FA app.")) %>% 
  filter(year_postbac %in% 1:3)
nbg_status_overtime %>% count(echelon) %>% count_to_pct()

nbg_status_overtime_agg <- nbg_status_overtime %>% 
  pivot_wider(id_cols = student_id,
              names_from = year_postbac, 
              values_from = echelon) %>% 
  mutate(across(matches("[[:digit:]]"), ~ ., .names = "year_bac_plus{.col}")) %>% 
  select(student_id, contains("year_bac")) 
grouping_cols = nbg_status_overtime_agg %>% select(contains("year_bac")) %>% names  
nbg_status_overtime_agg <- nbg_status_overtime_agg %>% 
  group_by(across(all_of(grouping_cols))) %>% 
  summarise(freq = n()) %>% 
  ungroup() %>% 
  mutate(id = 1:n()) %>% 
  pivot_longer(cols = contains("year_bac"),
               names_to = "year_bac_plus",
               values_to = "echelon") %>% 
  mutate(year_bac_plus = str_remove(year_bac_plus, "year_bac_plus"))

fwrite(nbg_status_overtime_agg, here("out/figures/raw_data/flow_chart_need_based_status_cohort_09_14.csv"))
```

# Alluvial chart of aide au merite status

```{r}
ids_enrolled_byyear <- all_enrol_08_23_clean %>% distinct(year_sise, student_id)
ids_enrolled_byyear <- ids_enrolled_byyear %>% 
  mutate(enrolled = T) |> 
  collect()

merite_status_overtime <- aglae_09_16_clean_unique[student_id %in% cohort_09_14[boursier_esr_all == T]$student_id] %>%
  select(student_id, year_aglae, year_bac, rangveur, echelon, dec_aid1_new, masqaid1, boursier_esr_all, mention, aidemerite_new) %>% 
  left_join(ids_enrolled_byyear, by = c("student_id", "year_aglae" = "year_sise")) %>% 
  mutate(enrolled = ifelse(is.na(enrolled), F, enrolled),
         mention_tb = (mention == "Très Bien"),
         nbg_eligible = (echelon %in% c("0bis", as.character(0:7))),
         year_postbac = (year_aglae - year_bac + 1)) %>% 
  filter(year_postbac %in% 1:3)

merite_status_overtime[, n_aidemerite := sum(aidemerite_new), by = student_id]
merite_status_overtime %>% count(n_aidemerite)
merite_status_overtime <- merite_status_overtime %>% filter(mention_tb == T)

merite_status_overtime <- merite_status_overtime %>% 
  mutate(aidemerite_status = case_when(aidemerite_new == T ~ "YES: received",
                                       aidemerite_new == F & boursier_esr_all == T & enrolled == T & rangveur == 0 ~ "NO: should have",
                                       aidemerite_new == F & boursier_esr_all == T & enrolled == T & rangveur == 1 ~ "NO: eligible to need-based grant\nbut application not finalised\nenrolled",
                                       aidemerite_new == F & boursier_esr_all == T & enrolled == F & rangveur == 0 ~ "NO: eligible to need-based grant\nnot enrolled",
                                       aidemerite_new == F & boursier_esr_all == T & enrolled == F & rangveur == 1 ~ "NO: eligible to need-based grant\nbut application not finalised\nnot enrolled",
                                       aidemerite_new == F & boursier_esr_all == F & enrolled == T ~ "NO: not eligible to\nneed-based grant\nbut enrolled",
                                       aidemerite_new == F & boursier_esr_all == F & enrolled == F ~ "NO: not eligible to need-based grant\nand not enrolled"))
merite_status_overtime %>% count(aidemerite_status) %>% count_to_pct()

merite_status_overtime[, n_aidemerite_yes_should := sum(aidemerite_status %in% c("YES: received", "NO: should have")), by = student_id]
merite_status_overtime <- merite_status_overtime[n_aidemerite_yes_should > 0]

merite_status_overtime_agg <- merite_status_overtime %>% 
  pivot_wider(id_cols = student_id,
              names_from = year_postbac, 
              values_from = aidemerite_status) %>% 
  mutate(across(matches("[[:digit:]]"), ~ ., .names = "year_bac_plus{.col}")) %>% 
  select(student_id, contains("year_bac")) 
grouping_cols = merite_status_overtime_agg %>% select(contains("year_bac")) %>% names
merite_status_overtime_agg <- merite_status_overtime_agg %>% 
  group_by(across(all_of(grouping_cols))) %>% 
  summarise(freq = n()) %>% 
  ungroup() %>% 
  mutate(id = 1:n()) %>% 
  pivot_longer(cols = contains("year_bac"),
               names_to = "year_bac_plus",
               values_to = "aidemerite_status") %>% 
  mutate(year_bac_plus = str_remove(year_bac_plus, "year_bac_plus"))

fwrite(merite_status_overtime_agg, here("out/figures/raw_data/flow_chart_aide_merite_status_cohort_09_14.csv"))
```

# Regressions of differences in persistence/graduation merit aid vs not

The idea of these controlled differences is to better understand the extent to which merit aid eligible students are underperforming relative to equally-academic more priviledged students.

I conduct the following comparison:
- merit aid vs engineers/managers

```{r}
cohort_09_14_temp <- cohort_09_14 |> 
  filter(moy1 >= 16) |> 
  mutate(inge_aid = case_when(boursier_esr_all == T ~ "Merit aid eligible",
                              boursier_esr_all == F & pcs == 38 ~ "Very High SES"),
         year_bac_diplom = paste0(year_bac, diplom),
         year_bac_compos_diplom = paste0(year_bac, compos, diplom))

out.vars <- c("enrol_2_ontime_all_0914", "enrol_3_ontime_all_0914",
              "grad_anytime_all_excl_bpbac", "master_anytime_all")

cohort_09_14_temp <- cohort_09_14_temp |>
  mutate(across(c(grad_anytime_all), ~ ifelse(source_sise == "bpbac" & ins_princip_lab != "cpge", NA, .x), .names = "{.col}_excl_bpbac"))

# main enrollment in bac year
comparison_fct <- function(dt,
                           pcs_var) {
  dt <- dt |> 
    filter(!is.na(get(pcs_var)))
  
  dt_comp <- dt |>
    filter(enrol_year_bac_all_0914 == T) |> 
    summarise(across(all_of(out.vars), list(n_obs = ~ n(),
                                            avg = ~ mean(.x, na.rm = T),
                                            std_dev = ~ sd(.x, na.rm = T))),
              .by = !!pcs_var) |> 
    pivot_longer(cols = -!!pcs_var,
                 names_to = c("outcome_var", "stat"),
                 names_pattern = "(.+)_(n_obs|avg|std_dev)$",
                 values_to = "value") |> 
    pivot_wider(names_from = stat,
                values_from = value)
  
  dt_coef <- out.vars |> 
    map(function(x) {
      
      # no controls
      uncontrolled_reg <- tidy(summary(feols(.[x] ~ .[pcs_var],
                                             data = dt |>
                                               filter(enrol_year_bac_all_0914 == T))))
      
      # controls
      controlled_reg <- tidy(summary(feols(.[x] ~ .[pcs_var] + poly(moy1, 2, raw = T) |
                                             ins_princip_lab,
                                           data = dt |>
                                             filter(enrol_year_bac_all_0914 == T))))
      
      return(data.frame(outcome_var = x,
                        uncontrolled_diff = uncontrolled_reg[2,]$estimate,
                        uncontrolled_se = uncontrolled_reg[2,]$std.error,
                        uncontrolled_p_value = uncontrolled_reg[2,]$p.value,
                        controlled_diff = controlled_reg[1,]$estimate,
                        controlled_se = controlled_reg[1,]$std.error,
                        controlled_p_value = controlled_reg[1,]$p.value))
    }) |> 
    rbindlist()
  
  return(list(dt_comp, dt_coef))
  }
comparison_table_fct <- function(dt, pcs_var) {
  
  dt_comp_clean <- dt[[1]] |>
    pivot_wider(names_from = !!pcs_var,
                values_from = c(n_obs, avg, std_dev)) |> 
    clean_names() |> 
    left_join(dt[[2]]) |> 
    mutate(controlled_pct = scales::percent(controlled_diff/avg_merit_aid_eligible, accuracy = .01),
           uncontrolled_pct = scales::percent(uncontrolled_diff/avg_merit_aid_eligible, accuracy = .01))
  
  dt_comp_clean <- dt_comp_clean |> 
    mutate(across(contains("p_value"), ~ case_when(.x <= 0.01 ~ "***",
                                                   .x > 0.01 & .x <= 0.05 ~ "**",
                                                   .x > 0.05 & .x <= 0.1 ~ "*",
                                                   .x > 0.1 ~ ""),
                  .names = "{.col}_sig"),
           uncontrolled_diff = paste0(round(uncontrolled_diff, 3), uncontrolled_p_value_sig),
           controlled_diff = paste0(round(controlled_diff, 3), controlled_p_value_sig)) |> 
    select(outcome_var, n_obs_merit_aid_eligible, avg_merit_aid_eligible, n_obs_very_high_ses, avg_very_high_ses, uncontrolled_diff, uncontrolled_se, uncontrolled_pct, controlled_diff, controlled_se, controlled_pct) |> 
    mutate(across(where(is.numeric), ~ as.character(.x))) |>  
    mutate(across(contains(c("avg", "_se")), ~ as.character(round(as.numeric(.x), 3)))) |> 
    pivot_longer(cols = contains(c("controlled_diff", "controlled_se")),
                 names_to = c("group", "stat"),
                 names_pattern = "(.+)_(diff|se)$",
                 values_to = "value") |> 
    pivot_wider(names_from = group,
                values_from = value) |> 
    mutate(across(-c(controlled, uncontrolled), ~ ifelse(stat == "se", "", .x))) |> 
    mutate(across(contains("n_obs"), ~ scales::comma(as.numeric(.x)))) |> 
    left_join(fread(here("out/data/out_vars_labs.csv")) |> rename(outcome_var = outcome)) |>
    mutate(outcome_lab = ifelse(is.na(outcome_lab), outcome_var, outcome_lab)) |> 
    select(outcome_lab, n_obs_merit_aid_eligible, avg_merit_aid_eligible, n_obs_very_high_ses, avg_very_high_ses, uncontrolled, uncontrolled_pct, controlled, controlled_pct)
  
  return(dt_comp_clean)
}

comp_38_09_14 <- comparison_fct(dt = cohort_09_14_temp,
                                pcs_var = "inge_aid")
write_rds(comp_38_09_14, here("out/tables/raw_data/comp_moy1_above_16_38_09_14.rds"))

comp_38_09_14[[1]] |> 
  # left_join(fread(here("out/data/out_vars_labs.csv")) |>
  #             rename(outcome_var = outcome)) |>
  ggplot(aes(x = outcome_var, y = avg, fill = inge_aid)) +
  geom_col(position = position_dodge(1)) +
  geom_text(aes(label = round(avg, 2)), position = position_dodge(1), vjust = 0) +
  facet_wrap(~ outcome_var, scales = "free")

fwrite(comparison_table_fct(comp_38_09_14, pcs_var = "inge_aid"), here("out/tables/raw_data/comp_table_moy1_above_16_38_09_14.csv"))
```

# Income by SES and echelon

## by SES

```{r}
library(glue)

pct_pcs_depp <- cohort_09_14 |> 
  filter(!is.na(year_bac) & boursier_esr_all == T) |>
  summarise(n_obs = n(), .by = pcs_depp) |> 
  mutate(pct = n_obs/sum(n_obs),
         pcs_depp = fct_relevel(pcs_depp, "Missing", "Low SES", "Middle SES", "High SES", "Very High SES"),
         order = as.integer(pcs_depp))

plot <- cohort_09_14 |>
  filter(!is.na(year_bac) & boursier_esr_all == T) |>
  select(echelon, ress, pcs_depp) |> 
  left_join(pct_pcs_depp) |> 
  mutate(pcs_depp = fct_relevel(pcs_depp, "Missing", "Low SES", "Middle SES", "High SES", "Very High SES"),
         pcs_depp_pct = glue("{pcs_depp} ({scales::percent(pct, accuracy = 1)})"),
         pcs_depp_pct = fct_reorder(pcs_depp_pct, as.integer(pcs_depp))) |> 
  filter(ress < quantile(ress, .995, na.rm = T) & ress > quantile(ress, .005, na.rm = T)) |>
  # filter(abs(ress) < 100000) |> 
  ggplot(aes(x = pcs_depp_pct, y = ress)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::comma) +
  labs(x = NULL,
       y = "Parents' taxable income (euros)")
plot
ggsave(here("out/figures/boxplot_parent_income_by_ses.pdf"), 
       height = fig_height, width = fig_width)

plot_dt <- ggplot_build(plot)$data[[1]]
plot_dt <- plot_dt |> 
  left_join(pct_pcs_depp |> 
              rename(x = order)) |> 
  mutate(pcs_depp_pct = glue("{pcs_depp} ({scales::percent(pct, accuracy = 1)})"),
         pcs_depp_pct = fct_reorder(pcs_depp_pct, as.integer(pcs_depp)))
fwrite(plot_dt, here("out/figures/raw_data/boxplot_parent_income_by_ses.csv"))
  
plot_dt |> 
  ggplot() +
  geom_boxplot(aes(x = pcs_depp_pct,
                   group = pcs_depp_pct,
                   ymin = ymin,
                   lower = lower,
                   middle = middle,
                   upper = upper,
                   ymax = ymax),
               stat = "identity") +
  geom_point(data = plot_dt |> 
               select(pcs_depp_pct, outliers) |> 
               unnest(outliers),
             aes(x = pcs_depp_pct, y = outliers))
```

## by echelon

```{r}
library(glue)

pct_echelon <- cohort_09_14 |> 
  filter(!is.na(year_bac) & boursier_esr_all == T) |>
  summarise(n_obs = n(), .by = echelon) |> 
  mutate(pct = n_obs/sum(n_obs),
         echelon = fct_relevel(echelon, "0", "0bis", as.character(1:7)),
         order = as.integer(echelon))

plot <- cohort_09_14 |>
  filter(!is.na(year_bac) & boursier_esr_all == T) |>
  select(echelon, ress) |> 
  left_join(pct_echelon) |> 
  mutate(echelon = fct_relevel(echelon, "0", "0bis", as.character(1:7)),
         echelon_pct = glue("Echelon {echelon}\n({scales::percent(pct, accuracy = 1)})"),
         echelon_pct = fct_reorder(echelon_pct, as.integer(echelon))) |> 
  filter(ress < quantile(ress, .995, na.rm = T) & ress > quantile(ress, .005, na.rm = T)) |> 
  ggplot(aes(x = echelon_pct, y = ress)) +
  geom_boxplot() +
  scale_y_continuous(breaks = seq(0, 100000, 10000), labels = scales::comma) +
  labs(x = NULL,
       y = "Parents' taxable income (euros)")
plot
ggsave(here("out/figures/boxplot_parent_income_by_echelon.pdf"), 
       height = fig_height, width = fig_width)

plot_dt <- ggplot_build(plot)$data[[1]]
plot_dt <- plot_dt |> 
  left_join(pct_echelon |> 
              rename(x = order)) |> 
  mutate(echelon_pct = glue("Echelon {echelon}\n({scales::percent(pct, accuracy = 1)})"),
         echelon_pct = fct_reorder(echelon_pct, as.integer(echelon)))
fwrite(plot_dt, here("out/figures/raw_data/boxplot_parent_income_by_echelon.csv"))
  
plot_dt |> 
  ggplot() +
  geom_boxplot(aes(x = echelon_pct,
                   group = echelon_pct,
                   ymin = ymin,
                   lower = lower,
                   middle = middle,
                   upper = upper,
                   ymax = ymax),
               stat = "identity") +
  geom_point(data = plot_dt |> 
               select(echelon_pct, outliers) |> 
               unnest(outliers),
             aes(x = echelon_pct, y = outliers))
```

# SES composition

```{r}
library(glue)

pct_pcs_depp <- cohort_09_14 |> 
  filter(!is.na(year_bac) & boursier_esr_all == T) |>
  summarise(n_obs = n(), .by = pcs_depp) |> 
  mutate(pct = n_obs/sum(n_obs),
         pcs_depp = fct_relevel(pcs_depp, "Missing", "Low SES", "Middle SES", "High SES", "Very High SES"),
         order = as.integer(pcs_depp))

plot_dt <- cohort_09_14 |>
  filter(!is.na(year_bac) & boursier_esr_all == T) |>
  select(pcs, pcs_depp) |> 
  left_join(pct_pcs_depp) |> 
  mutate(pcs_depp = fct_relevel(pcs_depp, "Missing", "Low SES", "Middle SES", "High SES", "Very High SES"),
         pcs_depp_pct = glue("{pcs_depp} ({scales::percent(pct, accuracy = 1)})"),
         pcs_depp_pct = fct_reorder(pcs_depp_pct, as.integer(pcs_depp))) |> 
  count(pcs_depp_pct, pcs)
fwrite(plot_dt, here("out/figures/raw_data/share_pcs_by_pcs_depp.csv"))

plot_dt |> 
  ggplot(aes(x = pcs_depp_pct, y = n, fill = factor(pcs))) +
  geom_col(position = "fill") +
  scale_fill_viridis_d()
ggsave(here("out/figures/share_pcs_by_pcs_depp.pdf"),
       height = fig_height, width = fig_width)
```


# Composition of echelon by SES and vice versa

## by SES

```{r}
pct_pcs_depp <- cohort_09_14 |> 
  filter(!is.na(year_bac) & boursier_esr_all == T) |>
  summarise(n_obs = n(), .by = pcs_depp) |> 
  mutate(pct = n_obs/sum(n_obs),
         pcs_depp = fct_relevel(pcs_depp, "Missing", "Low SES", "Middle SES", "High SES", "Very High SES"),
         order = as.integer(pcs_depp))


plot_dt <- cohort_09_14 |> 
  filter(boursier_esr_all == T) |> 
  select(pcs_depp, echelon) |> 
  count(pcs_depp, echelon) |>
  left_join(pct_pcs_depp) |> 
  mutate(pct_echelon = n/sum(n), .by = pcs_depp) |>
  mutate(pcs_depp = fct_relevel(pcs_depp, "Missing", "Low SES", "Middle SES", "High SES", "Very High SES"),
         pcs_depp_pct = glue("{pcs_depp} ({scales::percent(pct, accuracy = 1)})"),
         pcs_depp_pct = fct_reorder(pcs_depp_pct, as.integer(pcs_depp)))
fwrite(plot_dt, here("out/figures/raw_data/share_echelon_by_pcs_depp.csv"))

plot_dt |> 
  ggplot(aes(x = pcs_depp_pct, y = pct_echelon, fill = fct_rev(echelon))) +
  geom_col() +
  geom_text(aes(label = scales::percent(pct_echelon, accuracy = 1)),
            position = position_fill(.5), color = "black") +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = scales::percent, expand = c(0,0)) +
  labs(x = NULL,
       y = "Share of need-based grant eligible students",
       fill = "Echelon:")
ggsave(here("out/figures/share_echelon_by_pcs_depp.pdf"),
       height = fig_height, width = fig_width)
```

## by echelon

```{r}
pct_echelon <- cohort_09_14 |> 
  filter(!is.na(year_bac) & boursier_esr_all == T) |>
  summarise(n_obs = n(), .by = echelon) |> 
  mutate(pct = n_obs/sum(n_obs),
         echelon = fct_relevel(echelon, "0", "0bis", as.character(1:7)),
         order = as.integer(echelon))

plot_dt <- cohort_09_14 |> 
  filter(boursier_esr_all == T) |> 
  select(pcs_depp, echelon) |> 
  count(pcs_depp, echelon) |>
  left_join(pct_echelon) |> 
  mutate(pct_pcs_depp = n/sum(n), .by = echelon) |>
  mutate(echelon_pct = glue("Echelon {echelon}\n({scales::percent(pct, accuracy = 1)})"),
         echelon_pct = fct_reorder(echelon_pct, order),
         pcs_depp = fct_relevel(pcs_depp, "Missing", "Low SES", "Middle SES", "High SES", "Very High SES"))
fwrite(plot_dt, here("out/figures/raw_data/share_pcs_depp_by_echelon.csv"))

plot_dt |> 
  ggplot(aes(x = echelon_pct, y = pct_pcs_depp, fill = fct_rev(pcs_depp))) +
  geom_col() +
  geom_text(aes(label = scales::percent(pct_pcs_depp, accuracy = 1)),
            position = position_fill(.5), color = "black") +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = scales::percent, expand = c(0,0)) +
  labs(x = NULL,
       y = "Share of need-based grant eligible students",
       fill = NULL)
ggsave(here("out/figures/share_pcs_depp_by_echelon.pdf"),
       height = fig_height, width = fig_width)
```


