---
title: "Observatoire de la Vie Étudiante (OVE) Data"
subtitle: "Financial difficulties: merit-aid eligible vs. high-income high-achievers"
author: "Gustave"
date: today
format:
  html:
    toc: true
    embed-resources: true
    code-fold: true
    code-summary: "Show the code"
    fig-cap-location: top
    number-sections: true
    lightbox: true
editor: source
editor_options:
  chunk_output_type: console
execute:
  warning: false
  cache: true
---

## Objective

Produce `merit_aid_v_high_income_financial_diff.csv`, the raw data underlying the figure that compares self-reported financial outcomes between two groups of high-achieving (Bac mention "Très bien") undergraduate students from the 2013 OVE *Conditions de vie des étudiants* survey:

- **Merit-aid eligible students**: need-based grant recipients (`bourse == 1`).
- **High-income high-achievers**: non-recipients whose father AND mother both fall into the top income bands (`revenu_pere %in% 6:9` and `revenu_mere %in% 6:9`).

For each group, we compute the share answering "yes" to four survey items (financial distress, not enough money, work indispensable to live, work as a source of stress), along with weighted/unweighted counts and a 95% CI.

## Setup

### Packages

```{r}
#| cache: false

# Packages required to load the data, build the analysis sample, and write the
# output CSV. (Plotting packages are not needed since this script only produces
# the raw data file.)
packages <- c("tidyverse", "data.table", "janitor", "here")

# Install any package that isn't already installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Load the packages
invisible(lapply(packages, library, character.only = TRUE))
```

## Data

The OVE 2013 *Conditions de vie des étudiants* microdata cannot be redistributed
with these replication files. It can be requested directly from the Progedo
data portal at <https://data.progedo.fr/studies/doi/10.13144/lil-1086>. Once
obtained, point `ove_2013_data_path` below to the local folder containing the
extracted CSVs.

```{r}
# Load OVE 2013 (Conditions de vie des étudiants) survey data.
# The data ships as several CSV files (one per survey "partie"); we read each
# one, harmonize the `id` column to numeric, drop rows without a valid id, and
# left-join everything together on `id`.
ove_2013_data_path <- "~/Dropbox/3resources/data/ove_cdv/2013/lil-1086.csv/Csv/"
ove_2013_files <- list.files(ove_2013_data_path)

ove_2013_data <- ove_2013_files |>
  map(~fread(paste0(ove_2013_data_path, .x), fill = T) |>
        clean_names() |>
        mutate(id = as.numeric(id)) |>
        filter(!is.na(id)))

ove_2013 <- ove_2013_data |>
  reduce(left_join)
```

## Sample selection

Restrict the analysis to undergraduate students (Bac+1 to Bac+3) who obtained their Bac in 2009 or later — the cohorts potentially exposed to the merit-aid policy.

```{r}
ove_2013_sample <- ove_2013 |>
  filter(niveau %in% 2:4 & annee_bac >= 2009)
```

## Variable creation

We build the analysis variables in two steps:

1. **Group labels** — `bourse_lab` (need-based grant recipient vs. not), `mention` (Bac honors), and `boursier_income` (the comparison groups used in the figure: need-based grant recipients vs. non-recipients whose parents both fall in the top income bands).
2. **Outcome flags** — Boolean indicators for the four survey items, plus the helper `work_activity_since_year_start` (used to gate the work-related outcomes to students who actually had paid work since the start of the academic year).

```{r}
# --- Step 1: group labels --------------------------------------------------
ove_2013_sample <- ove_2013_sample |>
  mutate(
    # Need-based grant recipient label
    bourse_lab = case_match(bourse,
                            1 ~ "Need-based grant recipient",
                            2 ~ "Not a recipient",
                            .default = "Missing"),
    # Bac mention (honors)
    mention = case_match(q1200,
                         1 ~ "Passable ou pas de mention",
                         2 ~ "Assez Bien",
                         3 ~ "Bien",
                         4 ~ "Très bien"),
    mention = fct_relevel(mention,
                          "Passable ou pas de mention",
                          "Assez Bien", "Bien", "Très bien"),
    # Comparison groups for this figure: need-based grant recipients vs.
    # non-recipients whose father AND mother are both in the top income bands
    # (revenu_pere/revenu_mere bands 6 through 9). Anyone else is set to NA
    # and will be dropped from the figure.
    boursier_income = case_when(
      bourse == 1 ~ bourse_lab,
      bourse == 2 & revenu_pere %in% 6:9 & revenu_mere %in% 6:9 ~ "High-income"
    )
  )

# Drop respondents missing the bourse status — we cannot classify them.
ove_2013_sample_temp <- ove_2013_sample |>
  filter(!is.na(bourse))

# --- Step 2: outcome flags -------------------------------------------------
# All four outcomes are coded so that TRUE = "experiencing the difficulty"
# (financial difficulties, not enough money, work indispensable, work stressful).
# The two work-related outcomes are NA for students who did not work since the
# start of the academic year.
ove_2013_sample_temp <- ove_2013_sample_temp |>
  mutate(
    # Q7900_1: 1 = very significant financial difficulties, 5 = none.
    # We flag answers 1-3 as "experiencing financial difficulties".
    financial_distress = (q7900_1 %in% 1:3),
    # Q7700_1: 1 = completely disagree, 5 = completely agree with
    # "I have enough money to cover my monthly needs". We flag 4-5 as
    # "has enough money"; the figure ultimately reports the inverse share
    # (those answering 1-3, i.e. NOT enough money).
    enough_money = (q7700_1 %in% 4:5),
    # Helper: any paid work activity since the start of the academic year.
    work_activity_since_year_start = (q8700 %in% 1:2),
    # Q8706_r1: paid work is "indispensable to live" (3-5 on a 1-5 scale).
    indispensable_to_live = ifelse(work_activity_since_year_start == TRUE,
                                   q8706_r1 %in% 3:5, NA),
    # Q8707_2: paid work is a source of stress / nervous tension (yes = 1).
    impact_on_stress = ifelse(work_activity_since_year_start == TRUE,
                              q8707_2 == 1, NA)
  )
```

## Build and export `merit_aid_v_high_income_financial_diff.csv`

For students with mention "Très bien" and a non-missing `boursier_income` group, reshape the four outcome flags into long format and compute, by group and by question:

- `n_unweighted` / `n_weighted` — unweighted and weighted counts of non-missing responses in each (group, question, value) cell.
- `pct_unweighted` / `pct_weighted` — share of each value within the (group, question) total.
- `se`, `ci_lower`, `ci_upper` — Wald 95% CI on the weighted share, using the unweighted n in the standard-error formula.

We then keep only the `value == TRUE` rows (i.e. the share *experiencing* each difficulty) and write the result to disk.

```{r}
dt_graph <- ove_2013_sample_temp |>
  # Keep only high-achievers (mention "Très bien") who fall into one of the
  # two comparison groups defined by boursier_income.
  filter(mention == "Très bien" & !is.na(boursier_income)) |>
  select(id, poids_fin3, mention, boursier_income,
         financial_distress, enough_money,
         indispensable_to_live, impact_on_stress) |>
  # Reshape: one row per (student, outcome) pair.
  pivot_longer(cols = c(financial_distress, enough_money,
                        indispensable_to_live, impact_on_stress),
               names_to  = "question",
               values_to = "value") |>
  # Human-readable labels for each survey item, in display order.
  mutate(
    question_lab = case_match(
      question,
      "financial_distress"   ~ "To what extent would you say you are currently experiencing financial difficulties?",
      "enough_money"         ~ "Generally speaking, to what extent would you agree with the following statement? 'I have enough money to meet my monthly needs.'",
      "indispensable_to_live" ~ "Regarding your paid work, to what extent do the following statements apply to your situation? It is essential for my livelihood",
      "impact_on_stress"     ~ "Regarding your paid work, would you say it is a source of stress or nervous tension?"
    ),
    question_lab = factor(
      question_lab,
      levels = c(
        "To what extent would you say you are currently experiencing financial difficulties?",
        "Generally speaking, to what extent would you agree with the following statement? 'I have enough money to meet my monthly needs.'",
        "Regarding your paid work, to what extent do the following statements apply to your situation? It is essential for my livelihood",
        "Regarding your paid work, would you say it is a source of stress or nervous tension?"
      )
    )
  ) |>
  # Counts of non-missing answers in each (group, question, value) cell —
  # both unweighted (sample size) and weighted (using OVE sampling weight
  # poids_fin3).
  summarise(
    n_unweighted = sum(!is.na(value)),
    n_weighted   = sum(poids_fin3[!is.na(value)], na.rm = TRUE),
    .by = c(boursier_income, question_lab, value)
  ) |>
  # Within each (group, question) pair, turn counts into shares and compute
  # the standard error / 95% CI for the weighted share. The SE uses the
  # unweighted n on purpose (to reflect actual sample size precision).
  mutate(
    pct_unweighted = n_unweighted / sum(n_unweighted),
    pct_weighted   = n_weighted   / sum(n_weighted),
    se             = sqrt(pct_unweighted * (1 - pct_unweighted) / n_unweighted),
    .by = c(boursier_income, question_lab)
  ) |>
  mutate(
    ci_lower = pct_weighted - 1.96 * se,
    ci_upper = pct_weighted + 1.96 * se
  ) |>
  # Keep only the share *experiencing* the difficulty (value == TRUE);
  # the FALSE rows are the complement and aren't plotted.
  filter(value == TRUE)
dt_graph

# Write the raw data to disk for the figure.
fwrite(dt_graph, here("out/figures/raw_data/merit_aid_v_high_income_financial_diff.csv"))
```
