---
title: "Methodology Robustness"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages, useful functions and parameters

```{r}
source("src/code_lib/common_initial_loading.R")

source("src/code_lib/out_tab_observables.R")
source("src/code_lib/rd_graph_observables.R")
source("src/code_lib/placebos_coefs.R")
source("src/code_lib/placebos_fct.R")
source("src/code_lib/placebos_table.R")
source(here("src/code_lib/out_coef_ci_simple.R"))
source(here("src/code_lib/out_tab_prediction.R"))
source(here("src/code_lib/out_tab_latex_clean.R"))
source(here("src/code_lib/out_coef_ci.R"))
source(here("src/code_lib/export_table.R"))

library(modelr)
```

# ---------- LOAD DATA ----------

# Load datasets

```{r}
cohort_09_14 <- fread(here("out/data/cohort_09_14.csv"))
gc()

aca_labels <- fread(paste0(data_path, "original_data/other/n_academie_et_assimile_.csv")) %>% 
  select(ACADEMIE_ET_ASSIMILE, LIBELLE_LONG) %>% 
  mutate(ACADEMIE_ET_ASSIMILE = as.numeric(ACADEMIE_ET_ASSIMILE)) %>% 
  arrange(ACADEMIE_ET_ASSIMILE)
```

# ---------- DESIGN VALIDITY TEST 1: RDD ON OBSERVABLE CHARACTERISTICS ----------

# Observable characteristics

Run RDD on pre-treatment observables:
(i) Demographic characteristics
- gender
- age
- French nationality -> no longer possible
- parent SES
- parent income

(ii) Need-based grants
- echelon 0-0bis
- echelon 1
- echelon 2-4
- echelon 5-7

(iii) Geographic location
- high school location: Paris academie, 5 largest academies

(iv) High-school
- HS bac track
- HS general specific track
- private HS

2 bandwidths:
- MSE-optimal bandwidth
- +/- 1 bandwidth

2 specifications:
- no donut
- donut [15.7, 16.05]

## Setup

```{r}
data <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

X = data$moy1
donut = data$donut == TRUE
poly = 1
band = rep(list(NULL, 1), 2)
sub = c(rep(list(NULL, donut), each = 2))
cutoff_16 = 16

# replace extreme parent income values
# 9 observations with values 999999999 or 99999999 or 999999
# max value excluding them: 105,642
# 11 values of income strictly above 100,000
# min value: -1,503,821
# there are 191 values below -100,000
# I drop parent income values strictly superior in absolute value to 100,000 -> 202 observations
data %>% count(abs(ress) > 100000)
data <- data %>% 
  mutate(parent_inc = ress,
         parent_inc = ifelse(abs(parent_inc) > 100000, NA, parent_inc))

# create variables
data[, `:=`(female = (gender == "Female"),
            # french nationality
            # french_natio = (natio == 1),
            # first_time_bac = !(nbr_djc > 1 & nbr_djc != 99),
            # parent SES
            ses_very_high = (pcs_depp == "Very High SES"),
            ses_high = (pcs_depp == "High SES"),
            ses_middle = (pcs_depp == "Middle SES"),
            ses_low = (pcs_depp == "Low SES"),
            ses_missing = (pcs_depp == "Missing"),
            # echelon
            echelon_0_0bis = (echelon %in% c("0", "0bis")),
            echelon_1 = (echelon %in% c("1")),
            echelon_2_4 = (echelon %in% c("2","3","4")),
            echelon_5_7 = (echelon %in% c("5", "6","7")),
            # geographic origin
            paris_academie = (acam == 1),
            top5_academie = (acam %in% c(9,24,17,25,14)), # Lille, Créteil, Nantes, Versailles, Rennes
            # paris_resid = (depres == 75),
            # idf_resid = (depres %in% c(75, 77, 78, 91, 92, 93, 94, 95)),
            # paris_born = (depnais == 75),
            idf_born = (depnais %in% c(75, 77, 78, 91, 92, 93, 94, 95)),
            # HS track
            general_track = (exagt_name == "Générale"),
            technological_track = (exagt_name == "Technologique"),
            professional_track = (exagt_name == "Professionnelle"),
            # sciences_track = (cod_spe == "S"),
            # social_sciences_track = (cod_spe == "ES"),
            # humanities_track = (cod_spe == "L"),
            # HS private (sous contrat + hors contrat)
            private_hs = (origine %in% 2:3))]

obs_vars <- c("female", "age", "year_bac", #"french_natio", #"first_time_bac",
              "ses_very_high", "ses_high", "ses_middle", "ses_low", "ses_missing", "parent_inc",
              "echelon_0_0bis", "echelon_1", "echelon_2_4", "echelon_5_7",
              "paris_academie", "top5_academie",
              # "paris_resid", "idf_resid", "paris_born",
              "idf_born",
              "general_track", "technological_track", "professional_track",
              # "sciences_track", "social_sciences_track", "humanities_track",
              "private_hs")
```

## Estimate regressions and export

```{r}
# estimate RDDs for all observables
plan(multisession, workers = n_cores)
options(future.globals.maxSize = 2e9)

coef_observables = 1:length(obs_vars) %>% 
  future_map_dfr(function(x) {
    print(obs_vars[x])
    outcome = obs_vars[x]
    
    dt <- data |>
      filter(!is.na(outcome))
    Y = dt[[outcome]]
    
    reg <- 1:length(band) %>%
      future_map(possibly(function(x) rdrobust(y = Y, x = X, c = cutoff_16, all = T, p = poly, subset = sub[[x]], h = band[[x]]), NA, quiet = T))
    
    coef_ci <- out_coef_ci_simple(reg) %>%
      mutate(variable = obs_vars[x],
             donut = c(rep(c("No Donut", "Donut [15.7, 16.05]"), each = 2)),
             bandwidth = rep(c("MSE-Optimal", "(15, 17)"), n()/2),
             mean_y = mean(Y[X >= 15.5 & X < 15.7], na.rm = T))
    
    return(coef_ci)
  })

# generate category labels
coef_observables <- coef_observables %>% 
  mutate(category = case_when(variable %in% c("female", "age", "french_natio", "year_bac") ~ "Demographic",
                              variable %in% c("ses_missing", "ses_low", "ses_middle", "ses_high", "ses_very_high", "parent_inc") ~ "Parent SES",
                              variable %in% c("echelon_0_0bis", "echelon_1", "echelon_2_4", "echelon_5_7") ~ "Need-Based Grant",
                              variable %in% c("paris_academie", "top5_academie", "idf_born") ~ "Geographic",
                              variable %in% c("general_track", "technological_track", "professional_track", "private_hs") ~ "High-School"),
         category = factor(category, levels = c("Demographic", "Parent SES", "Need-Based Grant", "Geographic", "High-School")))

# generate characteristic labels
coef_observables <- coef_observables %>% 
  mutate(variable_lab = case_when(variable == "female" ~ "Female",
                                  variable == "age" ~ "Age",
                                  variable == "year_bac" ~ "HS Grad. Year",
                                  # variable == "french_natio" ~ "French Nationality",
                                  variable == "ses_missing" ~ "Missing SES",
                                  variable == "ses_low" ~ "Low SES",
                                  variable == "ses_middle" ~ "Middle SES",
                                  variable == "ses_high" ~ "High SES",
                                  variable == "ses_very_high" ~ "Very High SES",
                                  variable == "parent_inc" ~ "Parent Income",
                                  variable == "echelon_0_0bis" ~ "Echelon 0-0bis",
                                  variable == "echelon_1" ~ "Echelon 1",
                                  variable == "echelon_2_4" ~ "Echelon 2-4",
                                  variable == "echelon_5_7" ~ "Echelon 5-7",
                                  variable == "paris_academie" ~ "Paris Academie",
                                  variable == "top5_academie" ~ "5 Largest Academies",
                                  variable == "idf_born" ~ "Born in Paris Region",
                                  variable == "general_track" ~ "General Track",
                                  variable == "technological_track" ~ "Technologic Track",
                                  variable == "professional_track" ~ "Professional Track",
                                  variable == "private_hs" ~ "Private"),
         variable_lab = factor(variable_lab, levels = c("Female", "Age", "HS Grad. Year", "Missing SES", "Low SES", "Middle SES", "High SES", "Very High SES", "Parent Income", "Echelon 0-0bis", "Echelon 1", "Echelon 2-4", "Echelon 5-7", "Paris Academie", "5 Largest Academies", "Born in Paris Region", "General Track", "Technologic Track", "Professional Track", "Private")))

# export underlying data
fwrite(coef_observables, here("out", "tables", "raw_data", "rd_observables_method_robustness.csv"))
```

## Joint significance test

```{r}
library(systemfit)

# temp data to conduct joint significance test
rdd_temp <- data |> 
  filter(moy1 > 14.5 & moy1 < 17.5) |>
  select(moy1, donut, all_of(obs_vars[-9])) |> 
  drop_na(all_of(obs_vars[-9]))

# function for joint test
joint_test_systemfit <- function(dt = rdd_temp,
                                 running_var = "moy1",
                                 # covariates = obs_vars[c(1:7, 9:12, 14:17, 19)],
                                 covariates = obs_vars[c(1:6, 8, 9:11, 13:20)],
                                 cutoff = 16,
                                 donut_spec = T,
                                 bw = 1) {
  
  if (donut_spec == T) {
    # donut
    dt <- dt |>
      filter(donut == T)
  }
  
  # create treatment indicator
  dt$D <- as.numeric(dt[[running_var]] >= cutoff)
  
  # center running variable at cutoff
  dt$X_centered <- dt[[running_var]] - cutoff
  
  # filter data to bandwidth
  dt_subset <- dt |> 
    filter(abs(X_centered) < bw)
  
  # create triangular kernel weights
  # triangular kernel: K(u) = (1 - |u|) for |u| <= 1, 0 otherwise
  # dt_subset$weight <- 1 - abs(dt_subset$X_centered) / bw
  
  # create system of equations (one for each covariate)
  formulas <- lapply(covariates, function(cov) {
    as.formula(paste0(cov, "~ D + X_centered + I(D * X_centered)"))
  })
  
  # estimate SUR model
  # I have to drop the outcomes that are "collinear"
  sur_model <- systemfit(formulas, method = "SUR", data = dt_subset)
  
  # extract coefficient on D (the discontinuity)
  coef_names <- paste0("eq", 1:length(covariates), "_D")
  
  # extract coefficients on D (the discontinuity)
  # R <- matrix(0, nrow = length(covariates), ncol = length(coef(sur_model)))
  # for (i in 1:length(covariates)) {
  #   R[i, which(names(coef(sur_model)) == coef_names[i])] <- 1
  # }
  
  # Wald test
  tests <- paste0("eq", 1:length(covariates), "_D = 0")
  
  wald_test <- linearHypothesis(sur_model, tests)
  wald_test
  
  return(wald_test)
}


covs <- obs_vars[c(1:7, 10:12, 14:18, 20)]

# bandwith: (15, 17)
joint_test_donut_15_17 <- joint_test_systemfit(covariates = covs,
                                               donut_spec = T,
                                               bw = 1)
write_rds(joint_test_donut_15_17, here("out/tables/joint_test_donut_15_17.rds"))

joint_test_nodonut_15_17 <- joint_test_systemfit(covariates = covs,
                                                 donut_spec = F,
                                                 bw = 1)
write_rds(joint_test_nodonut_15_17, here("out/tables/joint_test_nodonut_15_17.rds"))

# bandwidth: median MSE optimal
coef_observables <- fread(here("out", "tables", "raw_data", "rd_observables_method_robustness.csv"))
median_mse_band <- coef_observables |> 
  filter(h_bandwidth != 1) |> 
  summarise(med_band = median(h_bandwidth), .by = donut)

joint_test_donut_mse <- joint_test_systemfit(covariates = covs,
                                         donut_spec = T,
                                         bw = median_mse_band[2, 2])
write_rds(joint_test_donut_mse, here("out/tables/joint_test_donut_mse.rds"))

joint_test_nodonut_mse <- joint_test_systemfit(covariates = covs,
                                           donut_spec = F,
                                           bw = median_mse_band[1, 2])
write_rds(joint_test_nodonut_mse, here("out/tables/joint_test_nodonut_mse.rds"))
```

## Data for raw graphs

```{r}
# save rd estimate in .rds files
system.time({
  grappe <- makeCluster(n_cores)
  registerDoParallel(grappe)
  foreach(i = 1:length(obs_vars), .packages = c("rdrobust", "here")) %dopar% {
    outcome = obs_vars[i]
    Y = data[[outcome]]
    reg = rdrobust(y = Y, x = X, c = cutoff_16, all = T, p = poly, subset = donut, h = 1)
    saveRDS(reg, here("out", "regressions", paste0(obs_vars[i], "_bandwidth_1.rds")))
  }
  stopCluster(grappe)
})

# save raw data for graphs so I can do them outside DEPP
for (i in 1:length(obs_vars)) {
  print(obs_vars[i])
  Y = data[[obs_vars[i]]]
  cov_graph_dt = rd_graph_observables(data, 0.05,
                                      var = obs_vars[i],
                                      16,
                                      outcome = obs_vars[i],
                                      donut_min = 15.7, donut_max = 16.05,
                                      reg_file = "_bandwidth_1.rds")
  write_rds(cov_graph_dt[2:4], here(paste0("out/figures/raw_data/", obs_vars[i], "_observables_graph_dt.rds")))
}
```

## Appendix: discontinuity in observable characteristics for different donuts

### Setup

```{r}
data <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

X = data$moy1
donut = data$donut == TRUE
donut_a = data$donut_a == TRUE
donut_b = data$donut_b == TRUE
donut_c = data$donut_c == TRUE
donut_d = data$donut_d == TRUE
donut_e = data$donut_e == TRUE
donut_f = data$donut_f == TRUE
donut_g = data$donut_g == TRUE
poly = 1
band = rep(list(NULL, 1), 9)
sub = c(rep(list(NULL, donut_a, donut_b, donut_c, donut_d, donut_e, donut, donut_f, donut_g), each = 2))
cutoff_16 = 16

# replace extreme parent income values
# 9 observations with values 999999999 or 99999999 or 999999
# max value excluding them: 105,642
# 11 values of income strictly above 100,000
# min value: -1,503,821
# there are 191 values below -100,000
# I drop parent income values strictly superior in absolute value to 100,000 -> 202 observations
data %>% count(abs(ress) > 100000)
data <- data %>% 
  mutate(parent_inc = ress,
         parent_inc = ifelse(abs(parent_inc) > 100000, NA, parent_inc))

# create variables
data[, `:=`(female = (gender == "Female"),
            # french nationality
            # french_natio = (natio == 1),
            # parent SES
            ses_very_high = (pcs_depp == "Very High SES"),
            ses_high = (pcs_depp == "High SES"),
            ses_middle = (pcs_depp == "Middle SES"),
            ses_low = (pcs_depp == "Low SES"),
            ses_missing = (pcs_depp == "Missing"),
            # echelon
            echelon_0_0bis = (echelon %in% c("0", "0bis")),
            echelon_1 = (echelon %in% c("1")),
            echelon_2_4 = (echelon %in% c("2","3","4")),
            echelon_5_7 = (echelon %in% c("5", "6","7")),
            # geographic origin
            paris_academie = (acam == 1),
            top5_academie = (acam %in% c(9,24,17,25,14)), # Lille, Créteil, Nantes, Versailles, Rennes
            idf_born = (depnais %in% c(75, 77, 78, 91, 92, 93, 94, 95)),
            # HS track
            general_track = (exagt_name == "Générale"),
            technological_track = (exagt_name == "Technologique"),
            professional_track = (exagt_name == "Professionnelle"),
            # HS private (sous contrat + hors contrat)
            private_hs = (origine %in% 2:3))]

obs_vars <- c("female", "age", "year_bac", #"french_natio",
              "ses_very_high", "ses_high", "ses_middle", "ses_low", "ses_missing", "parent_inc",
              "echelon_0_0bis", "echelon_1", "echelon_2_4", "echelon_5_7",
              "paris_academie", "top5_academie", "idf_born",
              "general_track", "technological_track", "professional_track", "private_hs")
```

### Estimate regressions and export

```{r}
# estimate RDDs for all observables
plan(multisession, workers = n_cores)
options(future.globals.maxSize = 2e9)

coef_observables = 1:length(obs_vars) %>% 
  future_map_dfr(function(x) {
    print(obs_vars[x])
    outcome = obs_vars[x]
    
    Y = data[[outcome]]
    
    reg <- 1:length(band) %>%
      future_map(possibly(function(x) rdrobust(y = Y, x = X, c = cutoff_16, all = T, p = poly, subset = sub[[x]], h = band[[x]]), NA, quiet = T))
    
    coef_ci <- out_coef_ci_simple(reg) %>%
      mutate(variable = obs_vars[x],
             donut = c(rep(c("No Donut", "Donut [15.95, 16.05]", "Donut [15.9, 16.05]", "Donut [15.85, 16.05]", "Donut [15.8, 16.05]", "Donut [15.75, 16.05]", "Donut [15.7, 16.05]", "Donut [15.65, 16.05]", "Donut [15.6, 16.05]"), each = 2)),
             bandwidth = rep(c("MSE-Optimal", "(15, 17)"), n()/2),
             mean_y = mean(Y[X >= 15.5 & X < 15.7], na.rm = T))
    
    return(coef_ci)
  })

# generate category labels
coef_observables <- coef_observables %>% 
  mutate(category = case_when(variable %in% c("female", "age", "french_natio", "year_bac") ~ "Demographic",
                              variable %in% c("ses_missing", "ses_low", "ses_middle", "ses_high", "ses_very_high", "parent_inc") ~ "Parent SES",
                              variable %in% c("echelon_0_0bis", "echelon_1", "echelon_2_4", "echelon_5_7") ~ "Need-Based Grant",
                              variable %in% c("paris_academie", "top5_academie", "idf_born") ~ "Geographic",
                              variable %in% c("general_track", "technological_track", "professional_track", "private_hs") ~ "High-School"),
         category = factor(category, levels = c("Demographic", "Parent SES", "Need-Based Grant", "Geographic", "High-School")))

# generate characteristic labels
coef_observables <- coef_observables %>% 
  mutate(variable_lab = case_when(variable == "female" ~ "Female",
                                  variable == "age" ~ "Age",
                                  variable == "year_bac" ~ "HS Grad. Year",
                                  variable == "french_natio" ~ "French Nationality",
                                  variable == "ses_missing" ~ "Missing SES",
                                  variable == "ses_low" ~ "Low SES",
                                  variable == "ses_middle" ~ "Middle SES",
                                  variable == "ses_high" ~ "High SES",
                                  variable == "ses_very_high" ~ "Very High SES",
                                  variable == "parent_inc" ~ "Parent Income",
                                  variable == "echelon_0_0bis" ~ "Echelon 0-0bis",
                                  variable == "echelon_1" ~ "Echelon 1",
                                  variable == "echelon_2_4" ~ "Echelon 2-4",
                                  variable == "echelon_5_7" ~ "Echelon 5-7",
                                  variable == "paris_academie" ~ "Paris Academie",
                                  variable == "top5_academie" ~ "5 Largest Academies",
                                  variable == "idf_born" ~ "Born in Paris Region",
                                  variable == "general_track" ~ "General Track",
                                  variable == "technological_track" ~ "Technologic Track",
                                  variable == "professional_track" ~ "Professional Track",
                                  variable == "private_hs" ~ "Private"),
         variable_lab = factor(variable_lab, levels = c("Female", "Age", "HS Grad. Year", "French Nationality", "Missing SES", "Low SES", "Middle SES", "High SES", "Very High SES", "Parent Income", "Echelon 0-0bis", "Echelon 1", "Echelon 2-4", "Echelon 5-7", "Paris Academie", "5 Largest Academies", "Born in Paris Region", "General Track", "Technologic Track", "Professional Track", "Private")))

# export underlying data
fwrite(coef_observables, here("out", "figures", "raw_data", "rd_observables_method_robustness_all_donuts.csv"))
```

# ---------- DESIGN VALIDITY TEST 2: RDD ON PREDICTED OUTCOMES ----------

# Predicted outcomes

Predict outcomes using all observable characteristics:
age, gender, hs graduation year, parent SES, parent income, high school location (Paris, top 5), born in Paris region, bac track, private 

2 bandwidths:
- MSE-optimal bandwidth
- +/- 1 bandwidth

2 specifications:
- no donut
- donut

## Setup

```{r}
outcome_vars <- c("enrol_year_bac_all_0914", "enrol_anytime_all_0914",
              "enrol_2_ontime_all_0914", "enrol_2_anytime_all_0914",
              "enrol_3_ontime_all_0914", "enrol_3_anytime_all_0914",
              "quality", "quality_bacyear_plus1", "quality_bacyear_plus2",
              "tot_enrol_yrs", "max_enrol_degetu",
              # "grad_anytime_all", "min_years_since_bac",
              "grad_5_all", "grad_7_all", "grad_9_all",
              "max_ects_credits",
              "master_anytime_all", "master_select_anytime_all", "quality_first_grad_degree")

rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

# replace extreme parent income values
# rdd <- rdd %>%
#   mutate(parent_inc = ress,
#          parent_inc = ifelse(abs(parent_inc) > 100000, NA, parent_inc))

# replace degree completion to missing students whose initial enrollment is BPBAC but not CPGE because I cannot track these students
rdd <- rdd |> 
  mutate(across(c(grad_5_all, grad_7_all, grad_9_all), ~ ifelse(source_sise == "bpbac" & ins_princip_lab != "cpge", NA, .x)))

# create variables
rdd[, `:=`(female = (gender == "Female"),
           # french nationality
           # french_natio = (natio == 1),
           # parent SES
           ses_very_high = (pcs_depp == "Very High SES"),
           ses_high = (pcs_depp == "High SES"),
           ses_middle = (pcs_depp == "Middle SES"),
           ses_low = (pcs_depp == "Low SES"),
           ses_missing = (pcs_depp == "Missing"),
           parent_inc = ress,
           # echelon
           echelon_0_0bis = (echelon %in% c("0", "0bis")),
           echelon_1 = (echelon %in% c("1")),
           echelon_2_4 = (echelon %in% c("2","3","4")),
           echelon_5_7 = (echelon %in% c("5", "6","7")),
           # geographic origin
           paris_academie = (acam == 1),
           top5_academie = (acam %in% c(9,24,17,25,14)), # Lille, Créteil, Nantes, Versailles, Rennes
           idf_born = (depnais %in% c(75, 77, 78, 91, 92, 93, 94, 95)),
           # HS track
           general_track = (exagt_name == "Générale"),
           technological_track = (exagt_name == "Technologique"),
           professional_track = (exagt_name == "Professionnelle"),
           # HS private (sous contrat + hors contrat)
           private_hs = (origine %in% 2:3))]

obs_vars <- c("female", "age", "year_bac", #"french_natio",
              "ses_very_high", "ses_high", "ses_middle", "ses_low", "ses_missing", "parent_inc",
              "echelon_0_0bis", "echelon_1", "echelon_2_4", "echelon_5_7",
              "paris_academie", "top5_academie", "idf_born",
              "general_track", "technological_track", "private_hs") # professional_track is not included because perfectly collinear. Also note that excluded category for parent SES is "Unknown".

rdd_long <- rdd %>%
  select(student_id, moy1, all_of(obs_vars), all_of(outcome_vars), donut) %>%
  pivot_longer(cols = all_of(outcome_vars),
               names_to = "outcomes",
               values_to = "outcome_values")

model_fct <- function(df) {
  lm(paste("outcome_values ~", paste(obs_vars, collapse = " + ")), data = df)
}

by_outcome <- rdd_long %>%
  group_by(outcomes) %>% 
  nest() %>% 
  mutate(model = map(data, model_fct))

by_outcome %>% summarise(tidy = map(model, tidy)) %>% unnest(cols = c(tidy))
by_outcome %>% summarise(glance = map(model, glance)) %>% unnest(cols = c(glance)) %>% select(outcomes, adj.r.squared, nobs)

predictions <- by_outcome %>%
  mutate(.fitted = map2(data, model, add_predictions)) %>% 
  select(-c(data, model)) %>% 
  unnest(.fitted) %>% 
  ungroup()


# rdd on predictions function
rdd_fct <- function(df) {
  Y = df$pred
  X = rdd$moy1
  donut = rdd$donut == TRUE
  poly = 1
  band = rep(list(NULL, 1), 2)
  sub = c(rep(list(NULL, donut), each = 2))
  cutoff_16 = 16
  
  reg_mse <- 1:length(band) %>%
    future_map(possibly(function(x) rdrobust(y = Y, x = X, c = cutoff_16, all = T, p = poly, subset = sub[[x]], h = band[[x]]), NA, quiet = T))
  
  coef_ci <- out_coef_ci_simple(reg_mse)
  
  coef_ci <- coef_ci %>%
    mutate(donut = c(rep(c(F, "[15.7, 16.05]"), each = 2)),
           bandwidth = rep(c("MSE optimal", "[15, 17]"), nrow(coef_ci)/2),
           mean_y = mean(Y[X >= 15.5 & X < 15.7], na.rm = T))
  
  return(coef_ci)
}

# estimate rdd on predicted outcomes based on observables
plan(multisession, workers = 8)
options(future.globals.maxSize = 2e9)

reg_pred_rd = predictions %>% 
  group_by(outcomes) %>% 
  nest() %>% 
  mutate(model = future_map(data, rdd_fct))

coef_ci <- reg_pred_rd %>%
  select(-data) %>% 
  unnest(model) %>% 
  ungroup()

adj_r2 <- by_outcome %>% summarise(glance = map(model, glance)) %>% unnest(cols = c(glance)) %>% select(outcomes, adj.r.squared, nobs)

out_vars_labs <- fread(here("out/data/out_vars_labs.csv"))

coef_ci_clean <- coef_ci %>%
  left_join(adj_r2) %>% 
  left_join(out_vars_labs |> rename(outcomes = outcome)) |> 
  mutate(outcomes_lab_clean = glue("Predicted {outcome_lab_short} (adj. R2 = {round(adj.r.squared, 2)})"),
         outcomes_lab_clean = fct_reorder(outcomes_lab_clean, order))

fwrite(coef_ci_clean, here("out/tables/raw_data/rd_predictions_method_robustness.csv"))
```

# ---------- DESIGN VALIDITY TEST 3: PLACEBOS ----------

## Setup

```{r}
rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

# replace degree completion to missing students whose initial enrollment is BPBAC but not CPGE because I cannot track these students
rdd <- rdd |> 
  mutate(grad_anytime_all = ifelse(source_sise == "bpbac" & ins_princip_lab != "cpge", NA, grad_anytime_all))
```

## MSE-optimal and (15, 17) bandwidth

```{r}
out.vars <- c("enrol_year_bac_all_0914", "enrol_anytime_all_0914",
              "enrol_2_ontime_all_0914", "enrol_2_anytime_all_0914",
              "enrol_3_ontime_all_0914", "enrol_3_anytime_all_0914",
              "quality", "quality_bacyear_plus1", "quality_bacyear_plus2",
              "tot_enrol_yrs", "max_enrol_degetu",
              # "grad_anytime_all", "min_years_since_bac",
              "grad_5_all", "grad_7_all", "grad_9_all",
              "max_ects_credits",
              "master_anytime_all", "master_select_anytime_all", "quality_first_grad_degree")

out.vars.captions <- paste0("Effect of Eligibility for the Merit Aid in the High School Graduation Year on ",
                            c("Enrollment in the High School Graduation Year",
                              "Enrollment at Least Once",
                              "Enrollment in 2nd Year in High School Graduation Year + 1",
                              "Enrollment in 2nd Year at Least Once",
                              "Enrollment in 3rd Year in High School Graduation Year + 2",
                              "Enrollment in 3rd Year at Least Once",
                              "Degree Quality in High School Graduation Year",
                              "Degree Quality in High School Graduation Year + 1",
                              "Degree Quality in High School Graduation Year + 2",
                              "Number of Years Enrolled in Higher Education",
                              "Highest Level of Study Attained (in Years)",
                              # "Degree Completion",
                              # "Years to First Degree Completion",
                              "Degree Completion within 5 Years",
                              "Degree Completion within 7 Years",
                              "Degree Completion within 9 Years",
                              "Total Number of Credits Obtained",
                              "Enrolling in a Masters Degree",
                              "Enrolling in a Selective Masters Degree",
                              "First Graduate Degree Quality"),
                              collapse = NULL)


out.vars.par <- rep(out.vars, each = 2)
out.vars.captions.par <- rep(out.vars.captions, each = 2)
band.par <- rep(list(NULL, 1), length(out.vars))

# lightweight datasets
rdd <- rdd |> 
  select(moy1, donut, donut15, donut14, all_of(out.vars))

cohort_09_14_light = cohort_09_14 |> 
  select(moy1, boursier_esr_all, donut, all_of(out.vars))

# MSE-optimal + (15, 17) bandwidths
# plan(multisession, workers = 10)
# options(future.globals.maxSize = 2e12)
1:length(out.vars.par) %>% 
  map(~ placebos_fct(cohort_dt = cohort_09_14_light,
                     rdd_dt = rdd,
                     outcome = out.vars.par[.x],
                     tab.cap = out.vars.captions.par[.x],
                     band = band.par[[.x]]))


# merge all together
band = "mse"

coefs_placebo_mse <- outcomes |> 
  map(function(x) {
    
    placebo_15 <- readRDS(here(glue("out/regressions/{x}_bandwidth_{band}_placebo15.rds")))
    placebo_14 <- readRDS(here(glue("out/regressions/{x}_bandwidth_{band}_placebo14.rds")))
    placebo_notbcs <- readRDS(here(glue("out/regressions/{x}_bandwidth_{band}_notbcs.rds")))
    
    coefs <- bind_rows(out_coef_ci(placebo_15[[1]],
                                   donut_vec = c(F, T),
                                   controls = c(F, F)) |> 
                         mutate(outcome = x,
                                placebo = "Grade 15",
                                mean_y = placebo_15[[2]]),
                       out_coef_ci(placebo_14[[1]],
                                   donut_vec = c(F, T),
                                   controls = c(F, F)) |> 
                         mutate(outcome = x,
                                placebo = "Grade 14",
                                mean_y = placebo_14[[2]]),
                       out_coef_ci(placebo_notbcs[[1]],
                                   donut_vec = c(F, T),
                                   controls = c(F, F)) |> 
                         mutate(outcome = x,
                                placebo = "Grade 16 Not Eligible to Need-Based Grant",
                                mean_y = placebo_notbcs[[2]]))
                       
  }) |> 
  rbindlist() |> 
  mutate(#ci_lower = ifelse(h_bandwidth == 1, ci_lower, robust_ci_lower),
         #ci_upper = ifelse(h_bandwidth == 1, ci_upper, robust_ci_upper),
         #mean_y = round(mean_y, 2),
         bandwidth = "MSE-optimal")

band = "1"

coefs_placebo_1 <- outcomes |> 
  map(function(x) {
    
    placebo_15 <- readRDS(here(glue("out/regressions/{x}_bandwidth_{band}_placebo15.rds")))
    placebo_14 <- readRDS(here(glue("out/regressions/{x}_bandwidth_{band}_placebo14.rds")))
    placebo_notbcs <- readRDS(here(glue("out/regressions/{x}_bandwidth_{band}_notbcs.rds")))
    
    coefs <- bind_rows(out_coef_ci(placebo_15[[1]],
                                   donut_vec = c(F, T),
                                   controls = c(F, F)) |> 
                         mutate(outcome = x,
                                placebo = "Grade 15",
                                mean_y = placebo_15[[2]]),
                       out_coef_ci(placebo_14[[1]],
                                   donut_vec = c(F, T),
                                   controls = c(F, F)) |> 
                         mutate(outcome = x,
                                placebo = "Grade 14",
                                mean_y = placebo_14[[2]]),
                       out_coef_ci(placebo_notbcs[[1]],
                                   donut_vec = c(F, T),
                                   controls = c(F, F)) |> 
                         mutate(outcome = x,
                                placebo = "Grade 16 Not Eligible to Need-Based Grant",
                                mean_y = placebo_notbcs[[2]]))
                       
  }) |> 
  rbindlist() |> 
  mutate(#ci_lower = ifelse(h_bandwidth == 1, ci_lower, robust_ci_lower),
         #ci_upper = ifelse(h_bandwidth == 1, ci_upper, robust_ci_upper),
         #mean_y = round(mean_y, 2),
         bandwidth = "(15, 17)")

coefs_placebo <- bind_rows(coefs_placebo_mse,
                           coefs_placebo_1)
fwrite(coefs_placebo, here("out/regressions/all_outcomes_placebos.csv"))
```