---
title: "Extensive Margin Analysis 2009-2014"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages, useful functions and parameters

```{r}
source("src/code_lib/common_initial_loading.R")

source(here("src/code_lib/export_fct.R"))

source(here("src/code_lib/out_coef_ci.R"))
source(here("src/code_lib/out_coef_ci_simple.R"))
source(here("src/code_lib/rdd_reg_bygroup.R"))

source(here("src/code_lib/rd_reg_by_type.R"))

library(fixest)
library(rdhte)
library(tictoc)
library(arrow)
library(glue)
library(furrr)
```


# ---------- LOAD DATA ----------

## Load datasets

```{r}
cohort_09_14 <- fread(paste0(data_modified_path, "cohort_09_14.csv"))
gc()
```

# ---------- MAIN RESULTS ----------

## Setup

```{r}
rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

rdd <- rdd[, `:=`(gender = factor(gender),
                  exagt_name = factor(exagt_name),
                  year_bac = factor(year_bac),
                  parent_inc = ress,
                  private_hs = (origine %in% 2:3),
                  acam = factor(acam),
                  depnais = factor(depnais),
                  echelon = factor(echelon),
                  paris_academie = factor(acam == 1),
                  top5_academie = factor(acam %in% c(9,24,17,25,14)),
                  idf_born = factor(depnais %in% c(75, 77, 78, 91, 92, 93, 94, 95)))]

control_vars <- c("gender", "age", "pcs_depp", "parent_inc", "echelon", "paris_academie", "top5_academie", "idf_born", "exagt_name", "private_hs", "year_bac") # "natio"
```

## Outcomes

```{r}
# outcome variables and associated table captions
out.vars <- c("enrol_year_bac_all_0914", "enrol_anytime_all_0914", "quality")

out.vars.captions <- paste0("Effect of Eligibility for the Merit Aid in the High School Graduation Year on ",
                            c("Enrollment in the High School Graduation Year",
                              "Enrollment at Least Once",
                              "Degree Quality in High School Graduation Year"),
                              collapse = NULL)
```

## Estimation

```{r}
rdd <- rdd |>
  select(all_of(c(out.vars, control_vars)), moy1, donut)

out.vars.par <- rep(out.vars, each = 2)
out.vars.captions.par <- rep(out.vars.captions, each = 2)
band.par <- rep(list(NULL, 1), length(out.vars))

# MSE-optimal + (15, 17) bandwidths
plan(multisession, workers = 10)
options(future.globals.maxSize = 2e9)
system.time(1:length(out.vars.par) %>% 
              future_map(~ export_fct(outcome = out.vars.par[.],
                                      bandwidth = band.par[[.]],
                                      tab.cap = out.vars.captions.par[.]),
                         .progress = T))
```

## RD plots

```{r}
out.vars <- c("enrol_year_bac_all_0914",
              "enrol_anytime_all_0914",
              "quality")

rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

plan(multisession, workers = 10)
options(future.globals.maxSize = 2e9)
graphs_out <- 1:length(out.vars) %>% 
  future_map(function(x) {
    # print(out.vars[x])
    graph = rd_graph(rdd,
                     cut = 0.05,
                     out = out.vars[x],
                     reg_file = "_bandwidth_1.rds",
                     xmin = 14, xmax = 18)
    
    saveRDS(graph, here("out", "figures", "raw_data", paste0("graph_", out.vars[x], "_bandwidth_1_donut_nocovs.rds")))
  }, .progress = T)
```

# ---------- EFFECT ON INITIAL ENROLMMENT DEGREE ----------

## Setup

```{r}
rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

rdd[enrol_year_bac_all_0914 == T] %>% count(ins_princip_lab, sort = T) |> count_to_pct()

rdd[, enrol_year_bac_all_0914_licence := (ins_princip_lab == "licence/master")]
rdd[, enrol_year_bac_all_0914_medecine := (ins_princip_lab == "medecine")]
rdd[, enrol_year_bac_all_0914_bts := (ins_princip_lab == "bts")]
rdd[, enrol_year_bac_all_0914_dut := (ins_princip_lab == "dut")]
rdd[, enrol_year_bac_all_0914_cpge := (ins_princip_lab == "cpge")]
rdd[, enrol_year_bac_all_0914_other := (ins_princip_lab %in% c("iep/dauphine", "inge", "priv", "mana"))]

rdd <- rdd[, `:=`(gender = factor(gender),
                  exagt_name = factor(exagt_name),
                  year_bac = factor(year_bac),
                  parent_inc = ress,
                  private_hs = (origine %in% 2:3),
                  acam = factor(acam))]

X = rdd$moy1
donut = rdd$donut == TRUE
covs = cbind(model.matrix(~rdd$gender+0),
             model.matrix(~rdd$age+0),
             # model.matrix(~rdd$natio+0),
             model.matrix(~rdd$pcs_depp+0),
             # model.matrix(~rdd$parent_inc+0),
             # model.matrix(~rdd$acam+0),
             model.matrix(~rdd$exagt_name+0),
             # model.matrix(~rdd$private_hs+0),
             model.matrix(~rdd$year_bac+0)
             )
cutoff_16 = 16
```

# Estimation

```{r}
outcomes_lab = c("enrol_year_bac_all_0914_licence",
                 "enrol_year_bac_all_0914_medecine",
                 "enrol_year_bac_all_0914_bts",
                 "enrol_year_bac_all_0914_dut",
                 "enrol_year_bac_all_0914_cpge",
                 "enrol_year_bac_all_0914_other")

outcomes = list(rdd$enrol_year_bac_all_0914_licence,
                rdd$enrol_year_bac_all_0914_medecine,
                rdd$enrol_year_bac_all_0914_bts,
                rdd$enrol_year_bac_all_0914_dut,
                rdd$enrol_year_bac_all_0914_cpge,
                rdd$enrol_year_bac_all_0914_other)

poly = list(1,1,1,1)
Y = rep(outcomes, each = length(poly))
outcomes_lab_par = rep(outcomes_lab, each = length(poly))
poly_par = rep(poly, length(outcomes))
nb_tot = length(unique(unlist(poly))) * length(outcomes)
controls = rep(list(NULL, covs, NULL, covs), nb_tot)
sub = donut
band = rep(list(NULL, 1), each = 2, nb_tot)
  
system.time({
  grappe <- makeCluster(n_cores)
  registerDoParallel(grappe)
  
  coef_ci <- foreach(i=1:length(poly_par), .packages=c("rdrobust", "here", "tidyverse"), .combine = rbind) %dopar% {
    reg = rdrobust(y = Y[[i]], x = X, c = cutoff_16, all = T, p = poly_par[[i]], h = band[[i]], covs = controls[[i]], subset = sub)
    source(here("src", "code_lib", "rdplot_output_latex.R"))
    data = out_coef_ci(list(reg),
                       donut_vec = ifelse(is.null(sub[[i]]), F, T),
                       controls_vec = ifelse(is.null(controls[[i]]), F, T)) %>% 
      mutate(outcome = outcomes_lab_par[[i]])}
  stopCluster(grappe)
})

fwrite(coef_ci, here("out", "tables", "raw_data", paste0("enrol_year_bac_all_0914_by_ins_princip_lab.csv")))
# ----
```

# ---------- AWARENESS ANALYSIS ----------

Perhaps the lack of effect on enrollment can be explained by a lack of awareness about the policy. To investigate this channel, I examine whether the effects on enrollment differ by:

(i) bac cohort
(ii) number of recipient students in same high schools in previous cohort
(iii) number of other students in same high school in same cohort

## Setup

```{r}
outcome = "enrol_year_bac_all_0914"

rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

rdd <- rdd[, `:=`(gender = factor(gender),
                  exagt_name = factor(exagt_name),
                  year_bac = factor(year_bac),
                  parent_inc = ress,
                  private_hs = (origine %in% 2:3),
                  acam = factor(acam))]

X = rdd$moy1
donut = rdd$donut == TRUE
covs = cbind(model.matrix(~rdd$gender+0),
             model.matrix(~rdd$age+0),
             # model.matrix(~rdd$natio+0),
             model.matrix(~rdd$pcs_depp+0),
             # model.matrix(~rdd$parent_inc+0),
             # model.matrix(~rdd$acam+0),
             model.matrix(~rdd$exagt_name+0),
             # model.matrix(~rdd$private_hs+0),
             model.matrix(~rdd$year_bac+0)
             )

cov_vars <- c("gender", "age", "pcs_depp", "exagt_name", "year_bac")
```

## By Bac cohort

### Estimation

```{r}
band = 1
coef_ci <- rdd_reg_bygroup(group_var = "year_bac",
                           bandwidth = band,
                           with_controls = F)
fwrite(coef_ci, here("out", "tables", "raw_data", paste0(outcome, "_bandwidth_", ifelse(is.null(band), "mse", band), "_cohort_coefs.csv")))

band = NULL
coef_ci <- rdd_reg_bygroup(group_var = "year_bac", bandwidth = band, with_controls = F)
fwrite(coef_ci, here("out", "tables", "raw_data", paste0(outcome, "_bandwidth_", ifelse(is.null(band), "mse", band), "_cohort_coefs.csv")))
```

## By number of students treated in previous year

### Setup

```{r}
rdd <- rdd %>% 
  mutate(n_aidemerite_prev_year_group = case_when(n_aidemerite_prev_year %in% 0:2 ~ "0-2",
                                                  n_aidemerite_prev_year %in% 3:5 ~ "3-5",
                                                  n_aidemerite_prev_year %in% 6:9 ~ "6-9",
                                                  n_aidemerite_prev_year >= 10 ~ "10+"))
rdd %>% count(n_aidemerite_prev_year_group) |> count_to_pct()

pct <- rdd %>%
  filter(year_bac != "2009" & !is.na(n_aidemerite_prev_year_group)) %>% 
  filter(moy1 > 15 & moy1 < 17) %>%
  count(n_aidemerite_prev_year_group) %>% count_to_pct()

rdd$n <- NULL
rdd$pct <- NULL
rdd <- rdd %>% 
  left_join(pct) %>% 
  mutate(n_aidemerite_prev_year_group_lab = paste0(n_aidemerite_prev_year_group, " (", round(pct,1), "%)"))
rdd %>% count(n_aidemerite_prev_year_group_lab)
```

### Estimation

```{r}
band = 1
coef_ci <- rdd_reg_bygroup(dt = rdd[!is.na(n_aidemerite_prev_year_group)],
                           group_var = "n_aidemerite_prev_year_group_lab", bandwidth = band, with_controls = F)
fwrite(coef_ci, here("out", "tables", "raw_data", paste0(outcome, "_bandwidth_", ifelse(is.null(band), "mse", band), "_n_aidemerite_prev_year_group_coefs.csv")))

band = NULL
coef_ci <- rdd_reg_bygroup(dt = rdd[!is.na(n_aidemerite_prev_year_group)],
                           group_var = "n_aidemerite_prev_year_group_lab", bandwidth = band, with_controls = T)
fwrite(coef_ci, here("out", "tables", "raw_data", paste0(outcome, "_bandwidth_", ifelse(is.null(band), "mse", band), "_n_aidemerite_prev_year_group_coefs.csv")))
```

## By number of students treated in current year

### Setup

```{r}
rdd <- rdd %>% 
  mutate(n_eligible_aidemerite = n_eligible_aidemerite - 1,
         n_eligible_aidemerite_group = case_when(n_eligible_aidemerite == -1 ~ NA_character_,
                                                 n_eligible_aidemerite %in% 0:2 ~ "0-2",
                                                 n_eligible_aidemerite %in% 3:5 ~ "3-5",
                                                 n_eligible_aidemerite %in% 6:9 ~ "6-9",
                                                 n_eligible_aidemerite >= 10 ~ "10+"))

pct <- rdd %>%
  filter(!is.na(n_eligible_aidemerite_group)) %>% 
  filter(moy1 > 15 & moy1 < 17) %>%
  count(n_eligible_aidemerite_group) %>% count_to_pct()

rdd$n <- NULL
rdd$pct <- NULL
rdd <- rdd %>% 
  left_join(pct) %>% 
  mutate(n_eligible_aidemerite_group_lab = paste0(n_eligible_aidemerite_group, " (", round(pct,1), "%)"))
rdd %>% count(n_eligible_aidemerite_group_lab)
```

### Estimation

```{r}
band = 1
coef_ci <- rdd_reg_bygroup(dt = rdd[!is.na(n_eligible_aidemerite_group)],
                           group_var = "n_eligible_aidemerite_group_lab", bandwidth = band, with_controls = T)
fwrite(coef_ci, here("out", "tables", "raw_data", paste0(outcome, "_bandwidth_", ifelse(is.null(band), "mse", band), "_n_eligible_aidemerite_group_coefs.csv")))

band = NULL
coef_ci <- rdd_reg_bygroup(dt = rdd[!is.na(n_eligible_aidemerite_group)],
                           group_var = "n_eligible_aidemerite_group_lab", bandwidth = band, with_controls = T)
fwrite(coef_ci, here("out", "tables", "raw_data", paste0(outcome, "_bandwidth_", ifelse(is.null(band), "mse", band), "_n_eligible_aidemerite_group_coefs.csv")))
```