---
title: "Robustness Check 1: Bandwidth; 2009-2014"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r}
library(data.table)
library(tidyverse)
library(here)
library(kableExtra)
library(doParallel)
library(ggthemr)
library(rdrobust)
library(furrr)
```

# Useful functions

```{r}
source(here("src","code_lib","useful_functions.R"))
source(here("src", "code_lib", "bandwidth_coef_ci.R"))
source(here("src", "code_lib", "bandwidth_graph.R"))
source(here("src", "code_lib", "out_coef_ci.R"))

source(here("src/code_lib/bandwidth_fct.R"))
source(here("src/code_lib/bandwidth_graph_fct.R"))
```

# Params

```{r}
# figures
fig_height = 6
fig_width = (16/9)*fig_height
ggthemr("pale")

theme_update(text = element_text(size = 12),
             legend.title = element_text(face = "italic", size = 10),
             legend.text = element_text(size = 10),
             legend.background = element_rect(fill = alpha("white", .75)),
             plot.caption = element_text(size = 10, face = "italic", color = "#7d7d7d"))

# no scientific notation
options(scipen=999)

# number of cores for parallelisation
n_cores = 10

# data folder
data_path <- "../data/"
data_modified_path <- here("out", "data/")
```

# ---------- LOAD DATA ----------

# Load datasets

```{r}
cohort_09_14 <- fread(paste0(data_modified_path, "cohort_09_14.csv"))
gc()

# replace by NA students in BTS and other BPBAC that I do not observe in graduation data
cohort_09_14 <- cohort_09_14 |> 
  mutate(across(c(grad_5_all, grad_7_all, grad_9_all), ~ ifelse(source_sise == "bpbac" & ins_princip_lab != "cpge", NA, .x)))
```

# Outcomes

```{r}
# outcomes
outcomes <- c("enrol_year_bac_all_0914",
              "enrol_anytime_all_0914",
              "enrol_2_ontime_all_0914",
              "enrol_2_anytime_all_0914",
              "enrol_3_ontime_all_0914",
              "enrol_3_anytime_all_0914",
              "quality",
              "quality_bacyear_plus1",
              "quality_bacyear_plus2",
              "tot_enrol_yrs",
              "max_enrol_degetu",
              "grad_5_all",
              "grad_7_all",
              "grad_9_all",
              "max_ects_credits",
              "master_anytime_all",
              "master_select_anytime_all",
              "quality_first_grad_degree")
```


# ---------- BANDWIDTH ROBUSTNESS ----------

## Setup

```{r}
rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

# lightweight rdd
rdd <- rdd |>  
  select(all_of(outcomes), moy1, donut)

X = rdd$moy1
donut = rdd$donut == TRUE
cutoff_16 = 16
```

## Estimation for different bandwidths

```{r}
# MSE-optimal bandwidth estimates
plan(multisession, workers = 10)
options(future.globals.maxSize = 2e9)
system.time(1:length(outcomes) %>% 
              future_map(function(z) {
                coef_ci <- bandwidth_fct(outcomes[z], band = NULL)}))


1:length(outcomes) %>%
  map(function(z) {
    if (outcomes[z] %in% c("tot_enrol_yrs", "max_enrol_degetu")) {
      graph <- bandwidth_graph_fct(outcomes[z],
                                   band = NULL,
                                   mse_t = T,
                                   mse_t_y = 0.375)  +
        # scale_y_continuous(breaks = seq(-1, 1, .25)) +
        coord_cartesian(ylim = c(-.5,.5))
      ggsave(here("out","figures", paste0("bandwidth_", outcomes[z], "_mse_bandwidth_nocovs.pdf")),
             height = fig_height/2, width = fig_width/2)
    } else {
      graph <- bandwidth_graph_fct(outcomes[z], band = NULL, mse_t = T)
    }
  })
```

# ---------- DONUT ROBUSTNESS ----------

Only 3 donuts: [15.7, 16.05], [15.75, 16.05], [15.65, 16.05]

MSE-optimal bandwidth + (15, 17)

## Setup

```{r}
rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

# lightweight dataset for faster estimation
rdd_reg <- rdd |> 
  select(all_of(outcomes), moy1, donut, donut_e, donut_f, source_sise, ins_princip_lab)

# parameters
cutoff_16 = 16
poly = 1

# outcome vector
Y = rep(outcomes, each = 3*2)

# running variable
X = rdd_reg$moy1

# donut
donut_baseline = rdd_reg$donut == TRUE
donut_15_75 <- rdd_reg$donut_e == TRUE
donut_15_65 <- rdd_reg$donut_f == TRUE

# parallelised verion
donut_par <- list(donut_baseline = donut_baseline,
                  donut_15_75 = donut_15_75,
                  donut_15_65 = donut_15_65)
donut_par_lab <- rep(names(donut_par), each = 2, length(outcomes))

# bandwidths vector
band = rep(list(NULL, 1), 3*length(outcomes))
```

## Estimation for different donuts

```{r}
# parralellise RD estimations
plan(multisession, workers = 10)
options(future.globals.maxSize = 2e9)
tic()
coef_ci_donut <- 1:length(Y) |>
  future_map(function(x) {
    reg = rdrobust(y = rdd_reg[[Y[x]]],
                   x = X,
                   subset = donut_par[[donut_par_lab[x]]],
                   c = cutoff_16,
                   p = poly,
                   h = band[[x]],
                   all = T)
    
    # extract coefficients, confidence intervals and other information
    data = out_coef_ci(list(reg),
                       donut_vec = donut_par_lab[x],
                       controls_vec = F) %>% 
      mutate(outcome = Y[x])
  }) |> 
  rbindlist()
toc()

# export
fwrite(coef_ci_donut, here("out/figures/raw_data/all_outcomes_different_donuts.csv"))
```

# ---------- DIFFERENT SETS OF CONTROLS ----------

## Setup

```{r}
rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

rdd <- rdd[, `:=`(gender = factor(gender),
                  exagt_name = factor(exagt_name),
                  year_bac = factor(year_bac),
                  parent_inc = ress,
                  private_hs = (origine %in% 2:3),
                  acam = factor(acam),
                  depnais = factor(depnais),
                  echelon = factor(echelon),
                  paris_academie = factor(acam == 1),
                  top5_academie = factor(acam %in% c(9,24,17,25,14)),
                  idf_born = factor(depnais %in% c(75, 77, 78, 91, 92, 93, 94, 95)))]

# control variables
control_vars <- c("gender", "age", "pcs_depp", "parent_inc", "echelon", "paris_academie", "top5_academie", "idf_born", "exagt_name", "private_hs", "year_bac")

# lightweight dataset for faster estimation
rdd_reg <- rdd |> 
  select(all_of(c(outcomes, control_vars)), moy1, donut)

rdd_reg_grad <- rdd |> 
  filter(!(source_sise == "bpbac" & ins_princip_lab != "cpge")) |> 
  select(all_of(c(outcomes, control_vars)), moy1, donut)

# parameters
cutoff_16 = 16
poly = 1

# outcome vector
Y = rep(outcomes, each = 3*2)

# running variable
X = rdd_reg$moy1
X_grad = rdd_reg_grad$moy1

# donut
donut = rdd_reg$donut == TRUE
donut_grad = rdd_reg_grad$donut == TRUE

# gender control
covs_gender = cbind(model.matrix(~rdd_reg$gender+0))
covs_gender_grad = cbind(model.matrix(~rdd_reg_grad$gender+0))

# all controls
covs_all = cbind(model.matrix(~rdd_reg$gender+0),
                 model.matrix(~rdd_reg$age+0),
                 # model.matrix(~rdd_reg$natio+0),
                 model.matrix(~rdd_reg$pcs_depp+0),
                 model.matrix(~rdd_reg$parent_inc+0),
                 model.matrix(~rdd_reg$echelon+0),
                 model.matrix(~rdd_reg$paris_academie+0),
                 model.matrix(~rdd_reg$top5_academie+0),
                 model.matrix(~rdd_reg$idf_born+0),
                 model.matrix(~rdd_reg$exagt_name+0),
                 model.matrix(~rdd_reg$private_hs+0),
                 model.matrix(~rdd_reg$year_bac+0))
covs_all_grad = cbind(model.matrix(~rdd_reg_grad$gender+0),
                      model.matrix(~rdd_reg_grad$age+0),
                      # model.matrix(~rdd_reg_grad$natio+0),
                      model.matrix(~rdd_reg_grad$pcs_depp+0),
                      model.matrix(~rdd_reg_grad$parent_inc+0),
                      model.matrix(~rdd_reg_grad$echelon+0),
                      model.matrix(~rdd_reg_grad$paris_academie+0),
                      model.matrix(~rdd_reg_grad$top5_academie+0),
                      model.matrix(~rdd_reg_grad$idf_born+0),
                      model.matrix(~rdd_reg_grad$exagt_name+0),
                      model.matrix(~rdd_reg_grad$private_hs+0),
                      model.matrix(~rdd_reg_grad$year_bac+0))

# control lsts
controls = list(no_controls = NULL,
                gender_only = covs_gender,
                all = covs_all)
controls_grad = list(no_controls = NULL,
                gender_only = covs_gender_grad,
                all = covs_all_grad)

# parallelised verion
controls_par <- rep(names(controls), length(outcomes)*2)
controls_par_grad <- rep(names(controls_grad), length(outcomes)*2)

# bandwidths vector
band = rep(list(NULL, 1), each = 3, length(outcomes))

# mean outcomes
mean_y <- bind_rows(rdd_reg |> 
                      select(-c(grad_5_all, grad_7_all, grad_9_all)) |> 
                      filter(moy1 >= 15.5 & moy1 < 15.7) |> 
                      summarise(across(any_of(outcomes), ~ mean(.x, na.rm = T))) |> 
                      pivot_longer(cols = everything(),
                                   names_to = "outcome",
                                   values_to = "mean_y"),
                    rdd_reg_grad |>  
                      filter(moy1 >= 15.5 & moy1 < 15.7) |> 
                      summarise(across(c(grad_5_all, grad_7_all, grad_9_all), ~ mean(.x, na.rm = T))) |> 
                      pivot_longer(cols = everything(),
                                   names_to = "outcome",
                                   values_to = "mean_y"))
```

## Estimation

```{r}
# parralellise RD estimations
plan(multisession, workers = 10)
options(future.globals.maxSize = 2e9)
tic()
coef_ci <- 1:length(Y) |>
  future_map(function(x) {
    # estimate RD
    if (Y[x] %in% c("grad_5_all", "grad_7_all", "grad_9_all")) {
      
      reg = rdrobust(y = rdd_reg_grad[[Y[x]]],
                     x = X_grad,
                     covs = controls_grad[[controls_par_grad[x]]],
                     subset = donut_grad,
                     c = cutoff_16,
                     p = poly,
                     h = band[[x]],
                     all = T)
      
    } else {
      reg = rdrobust(y = rdd_reg[[Y[x]]],
                     x = X,
                     covs = controls[[controls_par[x]]],
                     subset = donut,
                     c = cutoff_16,
                     p = poly,
                     h = band[[x]],
                     all = T)
    }
    
    # extract coefficients, confidence intervals and other information
    data = out_coef_ci(list(reg),
                       donut_vec = T,
                       controls_vec = controls_par[x]) %>% 
      mutate(outcome = Y[x])
  }) |> 
  rbindlist()
toc()
plan(sequential)

# export
fwrite(coef_ci, here("out/regressions/all_outcomes_nocovs_gender_all_covs.csv"))
```

# ---------- RD POWER ----------

### Setup

```{r}
# binary outcomes
outcome_binary = c("enrol_year_bac_all_0914", "enrol_anytime_all_0914",
                   "enrol_2_ontime_all_0914", "enrol_2_anytime_all_0914",
                   "enrol_3_ontime_all_0914", "enrol_3_anytime_all_0914",
                   "grad_5_all", "grad_7_all", "grad_9_all",
                   "master_anytime_all", "master_select_anytime_all")

# binary outcome labels
outcome_binary_labels <- c("Enrollment in HS Graduation Year",
                           "Enrollment at Any Point",
                           "Enrollment in 2nd Year in HS Graduation Year + 1",
                           "Enrollment in 2nd Year at Any Point",
                           "Enrollment in 3rd Year in HS Graduation Year + 2",
                           "Enrollment in 3rd Year at Any Point",
                           "Degree Completion within 5 Years",
                           "Degree Completion within 7 Years",
                           "Degree Completion within 9 Years",
                           "Enrollment in a Masters Degree",
                           "Enrollment in a Selective Masters Degree")

# continuous outcomes
outcome_continuous = c("quality", "quality_bacyear_plus1", "quality_bacyear_plus2",
                       "tot_enrol_yrs", "max_enrol_degetu",
                       "quality_first_grad_degree", "max_ects_credits")

# continuous outcome labels
outcome_continuous_labels <- c("Degree Quality in HS Graduation Year",
                               "Degree Quality in HS Graduation Year + 1",
                               "Degree Quality in HS Graduation Year + 2",
                               "Number of Years in Higher Education",
                               "Highest Level of Study Attained",
                               "Median Bac Grade of Masters Degree",
                               "Total Number of Credits Obtained")
```

## Power analysis

```{r}
## binary outcomes
# rdd sample - select only useful variables to speed up computation
rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)][donut == T] |> 
  select(moy1, all_of(outcome_binary))

# run RD power over all binary outcomes
tic()
plan(multisession, workers = 6)
power_rdpower <- outcome_binary |> 
  future_map(~ rdpower_fct(dt = rdd,
                           out = .x)) |> 
  rbindlist()
plan(sequential)
toc()
fwrite(power_rdpower, here(paste0("out/data/rdpower_all_binary_outcomes.csv")))

## continuous outcomes
# rdd sample - select only useful variables to speed up computation
rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)][donut == T] |> 
  select(moy1, all_of(outcome_continuous))

# run RD power over all continuous outcomes
tic()
plan(multisession, workers = 6)
power_rdpower<- outcome_continuous |> 
  future_map(~ rdpower_fct(dt = rdd,
                           out = .x,
                           max_tau = ifelse(.x == "max_ects_credits", 20, 1),
                           interval_tau = ifelse(.x == "max_ects_credits", .1, .001))) |> 
  rbindlist()
plan(sequential)
toc()
fwrite(power_rdpower, here(paste0("out/data/rdpower_all_continuous_outcomes.csv")))
```

# ---------- BASELINE VS COND. ENROLL IN HS GRAD. YEAR ----------

## Setup

```{r}
rdd <- cohort_09_14[boursier_esr_all == T][!(mention != "Très Bien" & aidemerite_new == T)]

# outcome variables
outcomes <- c(#"enrol_year_bac_all_0914",
  # "enrol_anytime_all_0914",
  "enrol_2_ontime_all_0914", "enrol_2_anytime_all_0914",
  "enrol_3_ontime_all_0914", "enrol_3_anytime_all_0914",
  "quality", "quality_bacyear_plus1", "quality_bacyear_plus2",
  "tot_enrol_yrs", "max_enrol_degetu",
  "grad_5_all", "grad_7_all", "grad_9_all",
  "master_anytime_all", "master_select_anytime_all", "quality_first_grad_degree",
  "max_ects_credits")

# lightweight dataset for faster estimation
rdd_reg <- rdd |> 
  select(enrol_year_bac_all_0914, all_of(outcomes), moy1, donut, source_sise, ins_princip_lab)

# parameters
cutoff_16 = 16
poly = 1

# outcome vector
Y = rep(outcomes, each = 2)

# bandwidths vector
band = rep(list(NULL, 1), length(outcomes))

# mean outcomes
mean_y <- bind_rows(rdd_reg |> 
                      filter(moy1 >= 15.5 & moy1 < 15.7) |> 
                      summarise(across(any_of(outcomes), ~ mean(.x, na.rm = T))) |> 
                      pivot_longer(cols = everything(),
                                   names_to = "outcome",
                                   values_to = "mean_y"))
```

## Estimation

```{r}
# parralellise RD estimations
plan(multisession, workers = 10)
options(future.globals.maxSize = 2e9)
tic()
coef_ci <- 1:length(Y) |>
  future_map(function(x) {
    
    ## baseline estimates ----
    rdd_temp <- rdd_reg
    X = rdd_temp$moy1
    donut = rdd_temp$donut == TRUE
    
    # RD
    reg_baseline = rdrobust(y = rdd_temp[[Y[x]]],
                   x = X,
                   covs = NULL,
                   subset = donut,
                   c = cutoff_16,
                   p = poly,
                   h = band[[x]],
                   all = T)
    
    # extract coefficients
    coef_ci_baseline <- out_coef_ci(list(reg_baseline),
                                    donut_vec = T,
                                    controls_vec = F) |> 
      mutate(sample = "baseline")
    # ----
    
    ## conditional on enrolling in high school graduation year ----
    rdd_temp <- rdd_reg |> 
      filter(enrol_year_bac_all_0914 == T)
    X = rdd_temp$moy1
    donut = rdd_temp$donut == TRUE
    
    # RD
    reg_cond_enroll = rdrobust(y = rdd_temp[[Y[x]]],
                               x = X,
                               covs = NULL,
                               subset = donut,
                               c = cutoff_16,
                               p = poly,
                               h = band[[x]],
                               all = T)
    
    # extract coefficients
    coef_ci_cond_enroll <- out_coef_ci(list(reg_cond_enroll),
                                       donut_vec = T,
                                       controls_vec = F) |> 
      mutate(sample = "conditional on enrollment")
    
    
    # extract coefficients, confidence intervals and other information
    data = bind_rows(coef_ci_baseline,
                     coef_ci_cond_enroll) %>% 
      mutate(outcome = Y[x])
  }) |> 
  rbindlist()
toc()
plan(sequential)

# export
fwrite(coef_ci, here("out/regressions/all_outcomes_baseline_condenrollment.csv"))
```