---
title: "Observatoire de la Vie Étudiante (OVE) Data"
subtitle: "Impact of paid work on studies, by Bac mention"
author: "Gustave"
date: today
format:
  html:
    toc: true
    embed-resources: true
    code-fold: true
    code-summary: "Show the code"
    fig-cap-location: top
    number-sections: true
    lightbox: true
editor: source
editor_options:
  chunk_output_type: console
execute:
  warning: false
  cache: true
---

## Objective

Produce `impcat_on_sudies_by_mention.pdf` — a single bar chart showing, by
high school graduation honors (Bac mention), the share of working
undergraduate students who report that their paid work has a negative impact
on their study results, using the 2013 OVE *Conditions de vie des étudiants*
survey.

The OVE 2013 microdata cannot be redistributed with these replication files.
It can be requested directly from the Progedo data portal at
<https://data.progedo.fr/studies/doi/10.13144/lil-1086>. Once obtained, point
`ove_2013_data_path` below to the local folder containing the extracted CSVs.

## Setup

### Packages

```{r}
#| cache: false

# Packages required to load the data, build the analysis sample, and produce
# the figure. `ggthemr` is used purely for the "pale" theme applied below.
packages <- c("tidyverse", "data.table", "janitor", "here", "ggthemr")

# Install any package that isn't already installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Load the packages
invisible(lapply(packages, library, character.only = TRUE))
```

### Graph parameters

```{r}
#| cache: false

# Disable scientific notation globally
options(scipen = 999)

# Apply the "pale" ggthemr theme, then override a handful of text/legend
# settings used by the figure.
ggthemr("pale")
theme_update(text             = element_text(size = 12),
             legend.title     = element_text(size = 11, face = "italic"),
             legend.background = element_rect(fill = alpha("white", .75)),
             plot.caption     = element_text(size = 8, face = "italic", color = "#7d7d7d"))

# Output figure dimensions
fig_height <- 6
figh_width <- 6 * 9 / 6
```

## Data

```{r}
# Load OVE 2013 (Conditions de vie des étudiants) survey data.
# The data ships as several CSV files (one per survey "partie"); we read each
# one, harmonize the `id` column to numeric, drop rows without a valid id, and
# left-join everything together on `id`.
ove_2013_data_path <- "~/Dropbox/3resources/data/ove_cdv/2013/lil-1086.csv/Csv/"
ove_2013_files <- list.files(ove_2013_data_path)

ove_2013_data <- ove_2013_files |>
  map(~fread(paste0(ove_2013_data_path, .x), fill = T) |>
        clean_names() |>
        mutate(id = as.numeric(id)) |>
        filter(!is.na(id)))

ove_2013 <- ove_2013_data |>
  reduce(left_join)
```

## Sample selection

Restrict the analysis to undergraduate students (Bac+1 to Bac+3) who obtained
their Bac in 2009 or later — the cohorts potentially exposed to the merit-aid
policy. Then drop respondents missing the bourse status (we keep the same
analysis sample as the rest of the survey-based figures in this project).

```{r}
ove_2013_sample <- ove_2013 |>
  filter(niveau %in% 2:4 & annee_bac >= 2009) |>
  filter(!is.na(bourse))
```

## Build and export `impcat_on_sudies_by_mention.pdf`

The figure plots, separately for each Bac mention group, the weighted share
of working students who answer **yes** to question Q8707_1 (paid work has a
negative impact on study results). Bac mention is collapsed into three groups
for the x-axis:

- **No honors** — Q1200 == 1 (Passable / pas de mention)
- **Honors** — Q1200 == 2 (Assez bien)
- **High and highest honors** — Q1200 == 3 or 4 (Bien / Très bien)

Within each group we compute the unweighted and weighted counts of (yes / no)
responses, turn them into shares, build a Wald 95% CI on the weighted share
using the unweighted n, and then plot only the `yes` (== 1) share.

```{r}
dt_graph <- ove_2013_sample |>
  # keep respondents with a valid Bac mention and a valid (non-999, non-NA)
  # answer to the impact-on-studies question
  filter(!is.na(q1200)) |>
  filter(q8707_1 != 999 & !is.na(q8707_1)) |>
  # collapse the four Bac mention levels into three display groups,
  # ordered from no honors to high/highest honors via the underlying numeric
  mutate(mention = case_match(q1200,
                              1   ~ "No honors",
                              2   ~ "Honors",
                              3:4 ~ "High and highest honors"),
         mention = fct_reorder(mention, q1200)) |>
  # weighted/unweighted counts of (yes/no) within each mention group
  summarise(n_unweighted = n(),
            n_weighted   = sum(poids_fin3),
            .by = c(mention, q8707_1)) |>
  # convert counts to shares within each mention group, and compute the
  # 95% CI on the weighted share (SE uses the unweighted n)
  mutate(pct_unweighted = n_unweighted / sum(n_unweighted),
         pct_weighted   = n_weighted   / sum(n_weighted),
         se             = sqrt(pct_unweighted * (1 - pct_unweighted) / n_unweighted),
         .by = mention) |>
  mutate(ci_lower = pct_weighted - 1.96 * se,
         ci_upper = pct_weighted + 1.96 * se) |>
  # keep only the "yes — work has a negative impact" share
  filter(q8707_1 == 1)

# Write the raw data to disk for the figure.
fwrite(dt_graph, here("out/figures/raw_data/impact_on_sudies_by_mention.csv"))
```
